---
title: "Analysis"
output:
  pdf_document:
    keep_tex:  true
    latex_engine: xelatex
  html_document: default
---

# This script calculates how to complete the market with the interim applications of the RCT using many stratas

```{r echo=FALSE, message=FALSE, results='hide'}
rm(list=ls())
library(plyr)
library(dplyr)
library(tidyr)
library(fastDummies)
library(reshape2)
library(corrplot)
library(stargazer)
library(stringr)
library(ggplot2)
library(rddtools)
library(parallel)
library(evd)  # \342\200\230~/R/x86_64-redhat-linux-gnu-library/3.5\342\200\231 (personal library in Hawk)
library(magic)
library(mvtnorm)
library(LaplacesDemon)
library(truncnorm)
library(compiler)
library(feather)
library(magrittr)
library(geosphere)
library(Hmisc)
library(plyr)
library(dplyr)
library(tidyr)
library(fastDummies)
library(reshape2)
library(corrplot)
library(stargazer)
library(stringr)
library(ggplot2)
library(knitr)
library(kableExtra)
library(anytime)
```

# Load information from previous years to set targets
```{r}
#dropbox_dir = "~/Dropbox/"
students19 <- read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2019/A_INSCRITOS_PUNTAJES_PSU_2019_PUB_MRUN.csv", sep=';', header=TRUE)
applications19 <- read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2019/C_POSTULANTES_SELECCION_PSU_2019_PUB_MRUN.csv", sep=';', header=TRUE)
students20 <- read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2020/A_INSCRITOS_PUNTAJES_PSU_2020_PUB_MRUN.csv", sep=';', header=TRUE)
applications20 <- read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2020/C_POSTULANTES_SELECCION_PSU_2020_PUB_MRUN.csv", sep=';', header=TRUE)
students21 <- read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/A_INSCRITOS_PUNTAJES_PDT_2021_PUB_MRUN.csv", sep=';', header=TRUE)
applications21 <- read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/C_POSTULANTES_SELECCION_PDT_2021_PUB_MRUN.csv", sep=';', header=TRUE)
apps_all_21 <- read.csv('~/Dropbox/Mistakes_in_college_admissions/mistakes_and_warnings/data/2021/210217 Reporte Postulaciones MRUN v2 CB.csv', sep=',', header=TRUE)
```


# Analyze distribution of applications per time of the day and day for previous year (2021)
#NOTE: this is only for the group of students whi took PDT on 2021

```{r}
#TODO: Check the timezone of the output of Chris!
#TODO: use regular expression for this to be more pro
apps_all_21 %<>% mutate(fecha_modified = gsub(" 9\\:"," 09:",FECHA_POSTULACION))
apps_all_21 %<>% mutate(fecha_modified = gsub(" 8\\:"," 08:",fecha_modified))
apps_all_21 %<>% mutate(fecha_modified = gsub(" 7\\:"," 07:",fecha_modified))
apps_all_21 %<>% mutate(fecha_modified = gsub(" 6\\:"," 06:",fecha_modified))
apps_all_21 %<>% mutate(fecha_modified = gsub(" 5\\:"," 05:",fecha_modified))
apps_all_21 %<>% mutate(fecha_modified = gsub(" 4\\:"," 04:",fecha_modified))
apps_all_21 %<>% mutate(fecha_modified = gsub(" 3\\:"," 03:",fecha_modified))
apps_all_21 %<>% mutate(fecha_modified = gsub(" 2\\:"," 02:",fecha_modified))
apps_all_21 %<>% mutate(fecha_modified = gsub(" 1\\:"," 01:",fecha_modified))
apps_all_21 %<>% mutate(fecha_modified = gsub(" 0\\:"," 00:",fecha_modified))
apps_all_21 %<>% mutate(fecha_modified = anytime(fecha_modified))
hist(as.Date(apps_all_21$FECHA_POSTULACION, tryFormats = c("%Y-%m-%d %H:%M")), breaks = "days")
ggplot(apps_all_21, aes(fecha_modified)) +
  geom_histogram(bins = 100) +
  geom_vline(xintercept = anytime("2021-02-13 23:00")) +
  geom_vline(xintercept = anytime("2021-02-14 11:49"))
#TODO: check that these times are in Chilean time

# Check the distribution of applications
p = ggplot(apps_all_21 %>% mutate(application_initial = ifelse(NRO_POSTULACION == 1, 1, 0)),
                               aes(fecha_modified, fill = as.factor(application_initial))) +
  geom_histogram(bins = 50, position = "dodge") +
  geom_vline(xintercept = anytime("2021-02-13 23:00"), linetype = "longdash") +
  geom_text(x = anytime("2021-02-13 23:00"), y = 5000, label = "Sample \n intervention") +
  geom_vline(xintercept = anytime("2021-02-14 11:49"), linetype = "longdash" ) +
  geom_text(x = anytime("2021-02-14 11:49"), y = 5000, label = "Email") +
  xlab("date") +
  scale_fill_brewer(palette="Pastel1",
                    name="Application",
                    breaks = c(1,
                               0),
                    labels = c("Initial",
                               "Modified")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank())
p
```


#Compute fraction of initial applications submited until 23:00 of the second day
```{r}
nrow(apps_all_21)
apps_first_21 = apps_all_21 %>% subset(NRO_POSTULACION == 1)
apps_tot = nrow(apps_first_21)
#TODO: MODIFY THIS!
apps_first_before_21 = apps_first_21 %>% filter(anytime(FECHA_POSTULACION) < "2021-02-12 23:00")
apps_partial = nrow(apps_first_before_21)
K = apps_partial/apps_tot
K  
#Plot
ggplot(apps_first_before_21 %>% mutate(application_initial = ifelse(NRO_POSTULACION == 1, 1, 0)),
                               aes(fecha_modified, fill = as.factor(application_initial))) +
  geom_histogram(bins = 50, position = "dodge") +
  xlab("date") +
  scale_fill_brewer(palette="Pastel1",
                    name="Application",
                    breaks = c(1,
                               0),
                    labels = c("Initial",
                               "Modified")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank())

```






```{r}
applications19 %>% nrow()
applications20 %>% nrow()
applications21 %>% nrow()
#According to the pdf   Reporte 11-02 23.01 hrs.pdf, there were 75,349 active applications at the end of first day 
#K = 75349/nrow(applications21)
#According to the pdf   Reporte 12-02 23.01 hrs.pdf, there were 95.199 active applications at the end of second day 
#TODO: USE THIS K FOR THE FINAL RUN AT THE END OF THE SECOND DAY
K = 95199/nrow(applications21)
K
top_growth = 0.1*nrow(applications21)
```



```{r}
applications19$applied = 1
applications20$applied = 1
applications21$applied = 1
applications19 %<>% mutate(assigned = (ESTADO_PREF_01 == 24) + (ESTADO_PREF_02 == 24) + (ESTADO_PREF_03 == 24) + (ESTADO_PREF_04 == 24) + (ESTADO_PREF_05 == 24) +
                                      (ESTADO_PREF_06 == 24) + (ESTADO_PREF_07 == 24) + (ESTADO_PREF_08 == 24) + (ESTADO_PREF_09 == 24) + (ESTADO_PREF_10 == 24) )
applications20 %<>% mutate(assigned = (ESTADO_PREF_01 == 24) + (ESTADO_PREF_02 == 24) + (ESTADO_PREF_03 == 24) + (ESTADO_PREF_04 == 24) + (ESTADO_PREF_05 == 24) +
                                      (ESTADO_PREF_06 == 24) + (ESTADO_PREF_07 == 24) + (ESTADO_PREF_08 == 24) + (ESTADO_PREF_09 == 24) + (ESTADO_PREF_10 == 24) )
applications21 %<>% mutate(assigned = (ESTADO_PREF_01 == 24) + (ESTADO_PREF_02 == 24) + (ESTADO_PREF_03 == 24) + (ESTADO_PREF_04 == 24) + (ESTADO_PREF_05 == 24) +
                                      (ESTADO_PREF_06 == 24) + (ESTADO_PREF_07 == 24) + (ESTADO_PREF_08 == 24) + (ESTADO_PREF_09 == 24) + (ESTADO_PREF_10 == 24) )
```


```{r}
students19 <- merge(students19, applications19[,c("MRUN", "applied", "assigned")], by='MRUN', all.x=TRUE)
students19$applied[is.na(students19$applied)] <- 0
students19$assigned[is.na(students19$assigned)] <- 0
students20 <- merge(students20, applications20[,c("MRUN", "applied", "assigned")], by='MRUN', all.x=TRUE)
students20$applied[is.na(students20$applied)] <- 0
students20$assigned[is.na(students20$assigned)] <- 0
students21 <- merge(students21, applications21[,c("MRUN", "applied", "assigned")], by='MRUN', all.x=TRUE)
students21$applied[is.na(students21$applied)] <- 0
students21$assigned[is.na(students21$assigned)] <- 0
```

```{r}
#students19 %>% group_by(assigned) %>% tally()
#students20 %>% group_by(assigned) %>% tally()
students19 %>% group_by(assigned) %>% summarise(n = n()) %>% mutate(share = n/sum(n))
students20 %>% group_by(assigned) %>% summarise(n = n()) %>% mutate(share = n/sum(n))
students21 %>% group_by(assigned) %>% summarise(n = n()) %>% mutate(share = n/sum(n))

#124451/(124451+181601)
#116047/(116047+192488)
```


```{r}
#Checking vars
describe(students19$PROMLM_ACTUAL)
describe(students19$PROMLM_ANTERIOR)
describe(students20$PROMLM_ACTUAL)
describe(students20$PROMLM_ANTERIOR)
describe(students21$PROM_CM_ACTUAL)
describe(students21$PROMLM_ANTERIOR)
is.factor(students19$PROMLM_ACTUAL)
is.factor(students19$PROMLM_ANTERIOR)
is.factor(students20$PROMLM_ACTUAL)
is.factor(students20$PROMLM_ANTERIOR)
is.factor(students21$PROM_CM_ACTUAL)
is.factor(students21$PROMLM_ANTERIOR)
sum(is.na(students19$PROMLM_ACTUAL))
sum(is.na(students19$PROMLM_ANTERIOR))
sum(is.na(students20$PROMLM_ACTUAL))
sum(is.na(students20$PROMLM_ANTERIOR))
sum(is.na(students21$PROM_CM_ACTUAL))
sum(is.na(students21$PROMLM_ANTERIOR))
```

```{r}
#Parssing factor strings to numerics
students19 %<>% mutate(PROMLM_ACTUAL = as.numeric(as.character(str_replace_all(PROMLM_ACTUAL, ",", "."))))
students19 %<>% mutate(PROMLM_ANTERIOR = as.numeric(as.character(str_replace_all(PROMLM_ANTERIOR, ",", "."))))
students20 %<>% mutate(PROMLM_ACTUAL = as.numeric(as.character(str_replace_all(PROMLM_ACTUAL, ",", "."))))
students20 %<>% mutate(PROMLM_ANTERIOR = as.numeric(as.character(str_replace_all(PROMLM_ANTERIOR, ",", "."))))
students21 %<>% mutate(PROM_CM_ACTUAL = as.numeric(as.character(str_replace_all(PROM_CM_ACTUAL, ",", "."))))
students21 %<>% mutate(PROMLM_ANTERIOR = as.numeric(as.character(str_replace_all(PROMLM_ANTERIOR, ",", "."))))
#Checks
sum(is.na(students19$PROMLM_ACTUAL))
sum(is.na(students19$PROMLM_ANTERIOR))
sum(is.na(students20$PROMLM_ACTUAL))
sum(is.na(students20$PROMLM_ANTERIOR))
sum(is.na(students21$PROM_CM_ACTUAL))
sum(is.na(students21$PROMLM_ANTERIOR))
summary(students19$PROMLM_ACTUAL)
summary(students19$PROMLM_ANTERIOR)
summary(students20$PROMLM_ACTUAL)
summary(students20$PROMLM_ANTERIOR)
summary(students21$PROM_CM_ACTUAL)
summary(students21$PROMLM_ANTERIOR)
hist(students19$PROMLM_ACTUAL)
hist(students19$PROMLM_ANTERIOR)
hist(students20$PROMLM_ACTUAL)
hist(students20$PROMLM_ANTERIOR)
hist(students21$PROM_CM_ACTUAL)
hist(students21$PROMLM_ANTERIOR)
```

# Create Stratas

```{r}
 students19 %<>% mutate(
   strata_score = ifelse(pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) < 450 , 1,
        ifelse(pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) >= 450 & pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) < 600 , 2,
        ifelse( pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) >= 600, 3, NA))),
   strata_sexo = COD_SEXO,
   strata_region = ifelse(CODIGO_REGION_EGRESO %in% c(1,2,3,4,15), 1,
   ifelse(CODIGO_REGION_EGRESO %in% c(5,6,7,13), 2,
   ifelse(CODIGO_REGION_EGRESO %in% c(8,9,10,11,12,14,16), 3, 4))))
 students19 %>% select(PROMLM_ACTUAL, PROMLM_ANTERIOR, strata_score, COD_SEXO, strata_sexo, CODIGO_REGION_EGRESO, strata_region)
 sum(is.na(students19$strata_score))
 sum(is.na(students19$strata_sexo))
 sum(is.na(students19$strata_region))
 sum(students19$strata_region == 4)
```

```{r}
 students20 %<>% mutate(
   strata_score = ifelse(pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) < 450 , 1,
        ifelse(pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) >= 450 & pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) < 600 , 2,
        ifelse( pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) >= 600, 3, NA))),
   strata_sexo = COD_SEXO,
   strata_region = ifelse(CODIGO_REGION_EGRESO %in% c(1,2,3,4,15), 1,
   ifelse(CODIGO_REGION_EGRESO %in% c(5,6,7,13), 2,
   ifelse(CODIGO_REGION_EGRESO %in% c(8,9,10,11,12,14,16), 3, 4))))
 students20 %>% select(PROMLM_ACTUAL, PROMLM_ANTERIOR, strata_score, COD_SEXO, strata_sexo, CODIGO_REGION_EGRESO, strata_region)
 sum(is.na(students20$strata_score))
 sum(is.na(students20$strata_sexo))
 sum(is.na(students20$strata_region))
 sum(students20$strata_region == 4)
```

```{r}
 students21 %<>% mutate(
   strata_score = ifelse(pmax(PROM_CM_ACTUAL, PROMLM_ANTERIOR) < 450 , 1,
        ifelse(pmax(PROM_CM_ACTUAL, PROMLM_ANTERIOR) >= 450 & pmax(PROM_CM_ACTUAL, PROMLM_ANTERIOR) < 600 , 2,
        ifelse( pmax(PROM_CM_ACTUAL, PROMLM_ANTERIOR) >= 600, 3, NA))),
   strata_sexo = COD_SEXO,
   strata_region = ifelse(CODIGO_REGION_EGRESO %in% c(1,2,3,4,15), 1,
   ifelse(CODIGO_REGION_EGRESO %in% c(5,6,7,13), 2,
   ifelse(CODIGO_REGION_EGRESO %in% c(8,9,10,11,12,14,16), 3, 4))))
 students21 %>% select(PROM_CM_ACTUAL, PROMLM_ANTERIOR, strata_score, COD_SEXO, strata_sexo, CODIGO_REGION_EGRESO, strata_region)
 sum(is.na(students21$strata_score))
 sum(is.na(students21$strata_sexo))
 sum(is.na(students21$strata_region))
 sum(students21$strata_region == 4)
```

```{r}
targets_2019 = students19 %>% group_by(strata_score,  strata_region, strata_sexo) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() )
  kable(targets_2019, digits=3)
```

```{r}
targets_2020 = students20 %>% group_by(strata_score,  strata_region, strata_sexo) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() )
kable(targets_2020, digits=3)
```

```{r}
targets_2021 = students21 %>% group_by(strata_score,  strata_region, strata_sexo) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() )
kable(targets_2021, digits=3)
```



# Load information interim for this year
```{r}
# students22 <- read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/official/adm2021_archivo_C_demre_2021feb08_MRUN_Compartir.csv", sep=';', header=TRUE)
# bea <- read.csv('~/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/15-01-21_Preseleccionados_BEA_DEMRE_MRUN.csv', sep=';', header=TRUE)
# inscritos22 <- read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/official/Inscritos_final_febrero_MRUN_Compartir.csv", sep=';', header=TRUE)
# applications22 <- read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/Reporte_diario_postulaciones_final_mrun.csv", sep=',', header=TRUE)
# students21_aux = read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/A_INSCRITOS_PUNTAJES_PDT_2021_PUB_MRUN.csv", sep=';', header=TRUE)
#applications21_aux = read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/C_POSTULANTES_SELECCION_PDT_2021_PUB_MRUN.csv", sep=';', header=TRUE)
#applications21_aux = read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/Reporte_diario_postulaciones_2_mrun.csv", sep=',', header=TRUE)
students22     = read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2022/puntajes_consolidado_v2.csv", sep=',', header=TRUE)
inscritos22     = read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2022/inscritos_consolidado_v2.csv", sep=',', header=TRUE)
applications22 = read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2022/raw/postulaciones_actual_12_01_22.csv", sep=',', header=TRUE)
#NOTE: K = 0.67 in the DEMRE files
nrow(applications22)/K
# Considering an upper bound of growth in 
top_growth + nrow(applications21) 
#Some stats to compare
#NOTE: THIS NUMBER IS SMALLER THAN 2020 and 2019 BECAUSE WE DON"T HAVE THE recupera puntaje students
nrow(students22 %>% subset(mate_actual > 0))
nrow(students21 %>% subset(MATE_ACTUAL > 0))
nrow(students20 %>% subset(MATE_ACTUAL > 0))
nrow(students19 %>% subset(MATE_ACTUAL > 0))

```


```{r}
#applications22 %<>% dplyr::rename(mrun = MRUN)
#students22 %<>% dplyr::rename(mrun = MRUN)
applications22$applied = 1
students22 <- merge(students22, applications22[,c("mrun", "applied")], by='mrun', all.x=TRUE)
```


```{r}
students22$applied[is.na(students22$applied)] <- 0
#Parssing
#TODO: CHANGE THE NAME OF THESE VARIABLES ACCORDING TO THE NEW FILES
#students22 %<>% dplyr::rename(promedio_cm_actual = PROM_CM_ACTUAL, promedio_clec_anterior = PROMLM_ANTERIOR)
students22 %<>% mutate(promedio_cm_actual = as.numeric(as.character(str_replace_all(promedio_cm_actual, ",", "."))))
students22 %<>% mutate(promedio_cm_anterior = as.numeric(as.character(str_replace_all(promedio_cm_anterior, ",", "."))))
#students22$promedio_cm_actual <- as.numeric(as.character(students22$promedio_cm_actual))
##students22$promedio_cm_anterior <- as.numeric(as.character(students22$promedio_cm_anterior))
sum(is.na(students22$promedio_cm_actual))
sum(is.na(students22$promedio_cm_anterior))
hist(students22$promedio_cm_actual)
hist(students22$promedio_cm_anterior)
```
# Create the same Stratas for interim

```{r}
 colnames(students22)
 colnames(inscritos22)
 #Merge student with inscritos 
 students22 = merge(students22, inscritos22 %>% select(sexo, mrun), by = "mrun", all.x = TRUE)
 students22 %<>% mutate(code_sexo = ifelse(sexo == "M", 1, 2))
 # Compute stratas
 students22 %<>% mutate(
   strata_score = ifelse(pmax(promedio_cm_actual, promedio_cm_anterior) < 450 , 1,
        ifelse(pmax(promedio_cm_actual, promedio_cm_anterior) >= 450 & pmax(promedio_cm_actual, promedio_cm_anterior) < 600 , 2,
        ifelse( pmax(promedio_cm_actual, promedio_cm_anterior) >= 600, 3, NA))),
   strata_sexo = code_sexo,
   strata_region = ifelse(codigo_region %in% c(1,2,3,4,15), 1,
   ifelse(codigo_region %in% c(5,6,7,13), 2,
   ifelse(codigo_region %in% c(8,9,10,11,12,14,16), 3, 4))))
 students22 %>% select(promedio_cm_actual, promedio_cm_anterior, strata_score, code_sexo, strata_sexo, codigo_region, strata_region)
 sum(is.na(students22$strata_score))
 sum(is.na(students22$strata_sexo))
 sum(is.na(students22$strata_region))
 sum(students22$strata_region == 4)
```


```{r}
interim_2022 = students22 %>% group_by(strata_score,  strata_region, strata_sexo) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() )
interim_2022 %<>% rename(pct_interim = pct)
kable(interim_2022, digits=3)
```

# Targets

```{r}
targets_2019 %<>% select(strata_score, strata_region, strata_sexo, pct) %>% rename(pct_2019 = pct)
targets_2020 %<>% select(strata_score, strata_region, strata_sexo, pct) %>% rename(pct_2020 = pct)
targets_2021 %<>% select(strata_score, strata_region, strata_sexo, pct) %>% rename(pct_2021 = pct)
targets = merge(targets_2019, targets_2020, by = c("strata_score", "strata_region", "strata_sexo"), all = TRUE)
targets = merge(targets, targets_2021, by = c("strata_score", "strata_region", "strata_sexo"), all = TRUE)

#TODO: modify this line
targets %<>% mutate(pct_average = pct_2021)
# targets %<>% mutate(pct_average = (pct_2019 + pct_2020 + pct_2021)/3)
```


```{r}
#NOTE: NEW ANALYSIS
apps_tot = nrow(apps_first_21)
#TODO: MODIFY THIS!
apps_first_before_21 = apps_first_21 %>% filter(anytime(FECHA_POSTULACION) < "2021-02-12 23:00")
apps_first_before_21$applied = 1
apps_partial = nrow(apps_first_before_21)
#Create stratas 
apps_first_21$applied = 1
apps_first_21 = merge(students21 %>% select(!applied), apps_first_21, by.x = "MRUN", by.y = "MRUN", all.x = TRUE)
apps_first_21 %<>% mutate(applied = ifelse(is.na(applied), 0, applied))
mean(apps_first_21$applied)
apps_first_before_21 = merge(students21 %>% select(!applied), apps_first_before_21, by.x = "MRUN", by.y = "MRUN", all.x = TRUE)
apps_first_before_21$applied
apps_first_before_21 %<>% mutate(applied = ifelse(is.na(applied), 0, applied))
mean(apps_first_before_21$applied)
#Collapse by stratas
stats_partial_21 = apps_first_before_21 %>% group_by(strata_score,  strata_region, strata_sexo) %>% summarise(n_partial=n(), na_partial=sum(applied), pct_partial=sum(applied)/n() )
stats_end_21 = apps_first_21 %>% group_by(strata_score,  strata_region, strata_sexo) %>% summarise(n_end=n(), na_end=sum(applied), pct_end=sum(applied)/n() )
#Merge by stratas and keep na column 
table_growth_stratas = merge(stats_partial_21, stats_end_21, by = c("strata_score",  "strata_region", "strata_sexo"))
table_growth_stratas %<>% mutate(growth_rate_strata = na_end/na_partial)
table_growth_stratas$growth_rate_strata
View(table_growth_stratas)
#K = apps_partial/apps_tot
#K  

#K
#applications22_projected = merge(applications22, students22, by = "mrun", all.x = TRUE)
#applications22_projected = applications22_projected[sample(1:nrow(applications22_projected), nrow(applications22_projected)/K, replace=TRUE), ]
#applications22_projected_stats = applications22_projected %>% group_by(strata_score,  strata_region, strata_sexo) %>% summarise(n=n()) %<>% mutate(share = n/sum(n))
#targets_interim = students22_projected %>% group_by(strata_score,  strata_region, strata_sexo) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() )
#targets_interim %<>% rename(pct_target_interim = pct)
```


```{r}
#NOTE: Notice that here we are using all.x=TRUE because the interim might have less combinations but we cant sample not from interim
interim_2022 = merge(interim_2022, targets, by = c("strata_score", "strata_region", "strata_sexo"), all.x = TRUE)
interim_2022 %<>% mutate(N_to_sample = pmax(round(n*pmax(pct_average, pct_interim)), 0))
#Multiply by factor related to fraction of applications at day X from the total of applicants
sum(interim_2022$N_to_sample)
#mult_factor =  sum(interim_2022$na/K)/ sum(interim_2022$N_to_sample)
#mult_factor = min(mult_factor, 1.1)
#NEW!
interim_aux = merge(interim_2022, table_growth_stratas %>% select(strata_score,  strata_region, strata_sexo, growth_rate_strata), by = c("strata_score",  "strata_region", "strata_sexo"))
interim_aux %<>% mutate(N_to_sample = round(na * growth_rate_strata))
sum(interim_aux$N_to_sample)
interim_aux
View(interim_aux)
```

```{r}
sum(interim_aux$N_to_sample)
```

```{r}
write.csv(students22[,c("mrun","strata_score", "strata_region", "strata_sexo")], "~/Dropbox/Mistakes/Code/Python/Cartillas/data/2022/students_stratas_to_complete_market.csv",  row.names = FALSE)
write.csv(interim_aux[,c("strata_score", "strata_region", "strata_sexo", "N_to_sample")], "~/Dropbox/Mistakes/Code/Python/Cartillas/data/2022/N_to_sample_stratas_to_complete_market.csv",  row.names = FALSE)
```



# OUTPUTS:
- Number of cases to complete by strata (region, gender, level mat-verbal)
- Clasification of students according to stratas (to know what students to sample)
    - MRUN
    - Strata (region, gender, level)
