---
title: "Analysis"
output:
  pdf_document:
    keep_tex:  true
    latex_engine: xelatex
  html_document: default
---


# This script calculates how to complete the market with the interim applications of the RCT using only average score strata

```{r echo=FALSE, message=FALSE, results='hide'}
library(plyr)
library(dplyr)
library(tidyr)
library(fastDummies)
library(reshape2)
library(corrplot)
library(stargazer)
library(stringr)
library(ggplot2)
library(rddtools)
library(parallel)
library(evd)  # \342\200\230~/R/x86_64-redhat-linux-gnu-library/3.5\342\200\231 (personal library in Hawk)
library(magic)
library(mvtnorm)
library(LaplacesDemon)
library(truncnorm)
library(compiler)
library(feather)
library(magrittr)
library(geosphere)
library(Hmisc)
library(plyr)
library(dplyr)
library(tidyr)
library(fastDummies)
library(reshape2)
library(corrplot)
library(stargazer)
library(stringr)
library(ggplot2)
library(knitr)
library(kableExtra)
```

# Load information from previous years to set targets
```{r}
#dropbox_dir = "~/Dropbox/"
students19 <- read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2019/A_INSCRITOS_PUNTAJES_PSU_2019_PUB_MRUN.csv", sep=';', header=TRUE)
applications19 <- read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2019/C_POSTULANTES_SELECCION_PSU_2019_PUB_MRUN.csv", sep=';', header=TRUE)
students20 <- read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2020/A_INSCRITOS_PUNTAJES_PSU_2020_PUB_MRUN.csv", sep=';', header=TRUE)
applications20 <- read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2020/C_POSTULANTES_SELECCION_PSU_2020_PUB_MRUN.csv", sep=';', header=TRUE)
students21 <- read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/A_INSCRITOS_PUNTAJES_PDT_2021_PUB_MRUN.csv", sep=';', header=TRUE)
applications21 <- read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/C_POSTULANTES_SELECCION_PDT_2021_PUB_MRUN.csv", sep=';', header=TRUE)
```


```{r}
applications19$applied = 1
applications20$applied = 1
applications21$applied = 1
applications19 %<>% mutate(assigned = (ESTADO_PREF_01 == 24) + (ESTADO_PREF_02 == 24) + (ESTADO_PREF_03 == 24) + (ESTADO_PREF_04 == 24) + (ESTADO_PREF_05 == 24) +
                                      (ESTADO_PREF_06 == 24) + (ESTADO_PREF_07 == 24) + (ESTADO_PREF_08 == 24) + (ESTADO_PREF_09 == 24) + (ESTADO_PREF_10 == 24) )
applications20 %<>% mutate(assigned = (ESTADO_PREF_01 == 24) + (ESTADO_PREF_02 == 24) + (ESTADO_PREF_03 == 24) + (ESTADO_PREF_04 == 24) + (ESTADO_PREF_05 == 24) +
                                      (ESTADO_PREF_06 == 24) + (ESTADO_PREF_07 == 24) + (ESTADO_PREF_08 == 24) + (ESTADO_PREF_09 == 24) + (ESTADO_PREF_10 == 24) )
applications21 %<>% mutate(assigned = (ESTADO_PREF_01 == 24) + (ESTADO_PREF_02 == 24) + (ESTADO_PREF_03 == 24) + (ESTADO_PREF_04 == 24) + (ESTADO_PREF_05 == 24) +
                                      (ESTADO_PREF_06 == 24) + (ESTADO_PREF_07 == 24) + (ESTADO_PREF_08 == 24) + (ESTADO_PREF_09 == 24) + (ESTADO_PREF_10 == 24) )
```


```{r}
students19 <- merge(students19, applications19[,c("MRUN", "applied", "assigned")], by='MRUN', all.x=TRUE)
students19$applied[is.na(students19$applied)] <- 0
students19$assigned[is.na(students19$assigned)] <- 0
students20 <- merge(students20, applications20[,c("MRUN", "applied", "assigned")], by='MRUN', all.x=TRUE)
students20$applied[is.na(students20$applied)] <- 0
students20$assigned[is.na(students20$assigned)] <- 0
students21 <- merge(students21, applications21[,c("MRUN", "applied", "assigned")], by='MRUN', all.x=TRUE)
students21$applied[is.na(students21$applied)] <- 0
students21$assigned[is.na(students21$assigned)] <- 0
```

```{r}
#students19 %>% group_by(assigned) %>% tally()
#students20 %>% group_by(assigned) %>% tally()
students19 %>% group_by(assigned) %>% summarise(n = n()) %>% mutate(share = n/sum(n))
students20 %>% group_by(assigned) %>% summarise(n = n()) %>% mutate(share = n/sum(n))
students21 %>% group_by(assigned) %>% summarise(n = n()) %>% mutate(share = n/sum(n))

#124451/(124451+181601)
#116047/(116047+192488)
```


```{r}
#Checking vars
describe(students19$PROMLM_ACTUAL)
describe(students19$PROMLM_ANTERIOR)
describe(students20$PROMLM_ACTUAL)
describe(students20$PROMLM_ANTERIOR)
describe(students21$PROM_CM_ACTUAL)
describe(students21$PROMLM_ANTERIOR)
is.factor(students19$PROMLM_ACTUAL)
is.factor(students19$PROMLM_ANTERIOR)
is.factor(students20$PROMLM_ACTUAL)
is.factor(students20$PROMLM_ANTERIOR)
is.factor(students21$PROM_CM_ACTUAL)
is.factor(students21$PROMLM_ANTERIOR)
sum(is.na(students19$PROMLM_ACTUAL))
sum(is.na(students19$PROMLM_ANTERIOR))
sum(is.na(students20$PROMLM_ACTUAL))
sum(is.na(students20$PROMLM_ANTERIOR))
sum(is.na(students21$PROM_CM_ACTUAL))
sum(is.na(students21$PROMLM_ANTERIOR))
```

```{r}
#Parssing factor strings to numerics
students19 %<>% mutate(PROMLM_ACTUAL = as.numeric(as.character(str_replace_all(PROMLM_ACTUAL, ",", "."))))
students19 %<>% mutate(PROMLM_ANTERIOR = as.numeric(as.character(str_replace_all(PROMLM_ANTERIOR, ",", "."))))
students20 %<>% mutate(PROMLM_ACTUAL = as.numeric(as.character(str_replace_all(PROMLM_ACTUAL, ",", "."))))
students20 %<>% mutate(PROMLM_ANTERIOR = as.numeric(as.character(str_replace_all(PROMLM_ANTERIOR, ",", "."))))
students21 %<>% mutate(PROM_CM_ACTUAL = as.numeric(as.character(str_replace_all(PROM_CM_ACTUAL, ",", "."))))
students21 %<>% mutate(PROMLM_ANTERIOR = as.numeric(as.character(str_replace_all(PROMLM_ANTERIOR, ",", "."))))
#Checks
sum(is.na(students19$PROMLM_ACTUAL))
sum(is.na(students19$PROMLM_ANTERIOR))
sum(is.na(students20$PROMLM_ACTUAL))
sum(is.na(students20$PROMLM_ANTERIOR))
sum(is.na(students21$PROM_CM_ACTUAL))
sum(is.na(students21$PROMLM_ANTERIOR))
summary(students19$PROMLM_ACTUAL)
summary(students19$PROMLM_ANTERIOR)
summary(students20$PROMLM_ACTUAL)
summary(students20$PROMLM_ANTERIOR)
summary(students21$PROM_CM_ACTUAL)
summary(students21$PROMLM_ANTERIOR)
hist(students19$PROMLM_ACTUAL)
hist(students19$PROMLM_ANTERIOR)
hist(students20$PROMLM_ACTUAL)
hist(students20$PROMLM_ANTERIOR)
hist(students21$PROM_CM_ACTUAL)
hist(students21$PROMLM_ANTERIOR)
```

```{r}
  targets_2019 =  rbind(
        students19 %>% filter(  pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) < 450 ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() ),
        students19 %>% filter(  pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) >= 450 & pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) < 600 ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() ),
        students19 %>% filter(  pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) >= 600  ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() )
    )
kable(targets_2019, digits=3)
```

```{r}
targets_2020 = rbind(
        students20 %>% filter(  pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) < 450 ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() ),
        students20 %>% filter(  pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) >= 450 & pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) < 600 ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() ),
        students20 %>% filter(  pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) >= 600  ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() )
    )
kable(targets_2020, digits=3)
```

```{r}
targets_2021 = rbind(
        students21 %>% filter(  pmax(PROM_CM_ACTUAL, PROMLM_ANTERIOR) < 450 ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() ),
        students21 %>% filter(  pmax(PROM_CM_ACTUAL, PROMLM_ANTERIOR) >= 450 & pmax(PROM_CM_ACTUAL, PROMLM_ANTERIOR) < 600 ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() ),
        students21 %>% filter(  pmax(PROM_CM_ACTUAL, PROMLM_ANTERIOR) >= 600  ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() )
    )
kable(targets_2021, digits=3)
```



# Load information interim for this year
#TODO: REMEMBER TO CHANGE THE PATHS TO 2022 AND THE FILE NAMES
```{r}
# students22 <- read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/official/adm2021_archivo_C_demre_2021feb08_MRUN_Compartir.csv", sep=';', header=TRUE)
# bea <- read.csv('~/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/15-01-21_Preseleccionados_BEA_DEMRE_MRUN.csv', sep=';', header=TRUE)
# inscritos22 <- read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/official/Inscritos_final_febrero_MRUN_Compartir.csv", sep=';', header=TRUE)
# applications22 <- read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/Reporte_diario_postulaciones_final_mrun.csv", sep=',', header=TRUE)
students21_aux = read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/A_INSCRITOS_PUNTAJES_PDT_2021_PUB_MRUN.csv", sep=';', header=TRUE)
applications21_aux = read.csv("~/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/C_POSTULANTES_SELECCION_PDT_2021_PUB_MRUN.csv", sep=';', header=TRUE)

#TODO: ERASE THIS LINES AND REPLACE THEM WITH REAL INTERIM PATHS
students22     = students21_aux
#inscritos22    = inscritos21_aux[sample(nrow(inscritos21_aux), size = floor(nrow(inscritos21_aux)*0.7), replace = FALSE),]
applications22 = applications21_aux[sample(nrow(applications21_aux), size = floor(nrow(applications21_aux)*0.7), replace = FALSE),]
```

```{r}
applications22 %<>% dplyr::rename(mrun = MRUN)
students22 %<>% dplyr::rename(mrun = MRUN)
applications22$applied = 1
students22 <- merge(students22, applications22[,c("mrun", "applied")], by='mrun', all.x=TRUE)
```

```{r}
students22$applied[is.na(students22$applied)] <- 0
#Parssing
#TODO: CHANGE THE NAME OF THESE VARIABLES ACCORDING TO THE NEW FILES
students22 %<>% dplyr::rename(promedio_cm_actual = PROM_CM_ACTUAL, promedio_lm_anterior = PROMLM_ANTERIOR)
students22 %<>% mutate(promedio_cm_actual = as.numeric(as.character(str_replace_all(promedio_cm_actual, ",", "."))))
students22 %<>% mutate(promedio_lm_anterior = as.numeric(as.character(str_replace_all(promedio_lm_anterior, ",", "."))))
#students22$promedio_cm_actual <- as.numeric(as.character(students22$promedio_cm_actual))
##students22$promedio_lm_anterior <- as.numeric(as.character(students22$promedio_lm_anterior))
sum(is.na(students22$promedio_cm_actual))
sum(is.na(students22$promedio_lm_anterior))
hist(students22$promedio_cm_actual)
hist(students22$promedio_lm_anterior)
```



```{r}
interim_2022 = rbind(
    students22 %>% filter( pmax(promedio_cm_actual, promedio_lm_anterior) < 450 ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n()),
    students22 %>% filter( pmax(promedio_cm_actual, promedio_lm_anterior)  >= 450 & pmax(promedio_cm_actual, promedio_lm_anterior) < 600  ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n()),
    students22 %>% filter( pmax(promedio_cm_actual, promedio_lm_anterior) >= 600  ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n())
    )
kable(interim_2022, digits=3)
```

# Targets
Among students < 450
Among students >= 450 and < 600
Among students >= 450 and < 600
```{r}
average_targets = (targets_2019$pct + targets_2020$pct + targets_2021$pct)/3
low = average_targets[1]
mid = average_targets[2]
high = average_targets[3]
#low = #0.5*(0.2229+0.160355)
#mid = #0.5*(0.647234+0.4259)
#high = #0.5*(0.8788501+0.8177859)
```

```{r}
low22 <- students22 %>% filter( pmax(promedio_cm_actual, promedio_lm_anterior) < 450 ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n())
mid22 <- students22 %>% filter( pmax(promedio_cm_actual, promedio_lm_anterior)  >= 450 & pmax(promedio_cm_actual, promedio_lm_anterior) < 600  ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n())
high22 <- students22 %>% filter( pmax(promedio_cm_actual, promedio_lm_anterior) >= 600  ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n())
```

```{r}
low_to_sample = max(round(low22$n*low - low22$na), 0)
mid_to_sample = max(round(mid22$n*mid - mid22$na), 0)
high_to_sample = max(round(high22$n*high - high22$na), 0)
```

```{r}
low_to_sample
mid_to_sample
high_to_sample
```


```{r}
c(low_to_sample, mid_to_sample, high_to_sample)
sum(c(low_to_sample, mid_to_sample, high_to_sample))
```

```{r}
nrow(applications22) + sum(c(low_to_sample, mid_to_sample, high_to_sample))
```


```{r}
students22 %<>% mutate(plm_level = ifelse(pmax(promedio_cm_actual, promedio_lm_anterior) < 450, 'low', ifelse(pmax(promedio_cm_actual, promedio_lm_anterior) < 600, 'mid', 'high')) )
```

```{r}
write.csv(students22[,c("mrun", "plm_level")], "~/Dropbox/Mistakes/Code/Python/Cartillas/data/2022/plm_level.csv",  row.names = FALSE)
```

# OUTPUTS:
- Number of cases to complete by strata (region, gender, level mat-verbal)
- Clasification of students according to stratas (to know what students to sample)
    - MRUN
    - Strata (region, gender, level)
