
---
title: "Analysis + Tables + Regressions in Paper"
output:
  pdf_document:
    keep_tex:  true
    latex_engine: xelatex
  html_document: default
header-includes:
   - \usepackage{floatrow}
   - \floatsetup[figure]{capposition=top}
---

```{r echo=FALSE, message=FALSE, results='hide'}
rm(list=ls())
gc()
```

```{r echo=FALSE, message=FALSE, results='hide'}
library(rlang)
library(tidyr)
library(fastDummies)
library(reshape2)
library(corrplot)
library(stargazer)
library(stringr)
library(ggplot2)
library(rddtools)
library(parallel)
library(evd)
library(magic)
library(mvtnorm)
library(LaplacesDemon)
library(truncnorm)
library(compiler)
library(feather)
library(magrittr)
library(geosphere)
library(Hmisc)
library(plyr)
library(tidyr)
library(fastDummies)
library(reshape2)
library(corrplot)
library(stargazer)
library(stringr)
library(ggplot2)
#library(tidyverse)
library(haven)
library(MASS)
library(stringi)
library(openxlsx)
library(readxl)
library(kableExtra)
library(dplyr)
```

```{r echo=FALSE, message=FALSE, results='hide'}
my_colors <- RColorBrewer::brewer.pal(4, "Pastel1")[1:2]
myblue = '#2F5597'
```

```{r}
dropbox_dir <- "~/Dropbox/"
```

# Analysis in paper ------------------------------
```{r}
#Read All probabilities with Ratex too (fixed)
probstrue <- read.csv(paste(dropbox_dir, "Mistakes Structural/Code/Python/Cartillas/outputs/2022/probs_for_true_results_fixed_with_ratex.csv", sep=''), sep=',', header=TRUE)
probsofficial <- read.csv(paste(dropbox_dir, "Mistakes Structural/Code/Python/Cartillas/outputs/2022/probs_for_official_results_fixed_with_ratex.csv", sep=''), sep=',', header=TRUE)
probspartial <- read.csv(paste(dropbox_dir, "Mistakes Structural/Code/Python/Cartillas/outputs/2022/probs_for_partial_results_fixed_with_ratex.csv", sep=''), sep=',', header=TRUE)
#NOTE: probstrue has as pref 1 the top-true pref and pref 2 the bottom-true pref

```

```{r}
#Read data files
scores <- read.csv(file = paste(dropbox_dir, "Mistakes Structural/Code/Python/Cartillas/data/2022/puntajes_consolidado_v3.csv", sep=""), header=TRUE, sep=",")
df <- readRDS(paste(dropbox_dir,"Mistakes Structural/Code/Python/Cartillas/outputs/2022/master_file_for_analysis_of_rct.csv", sep=''))
#NOTE: probstrue has as pref 1 the top-true pref and pref 2 the bottom-true pref
probstrue %<>% dplyr::rename(codigo_carrera_top_true    = codigo_carrera_1,
                             marca_top_true             = marca_1 ,
                             puntpond_top_true          = puntpond_1 ,
                             prob_interim_top_true      = prob_interim_1 ,
                             prob_adaptive_top_true     = prob_adaptive_1 ,
                             prob_ratex_top_true        = prob_ratex_1,
                             codigo_carrera_bottom_true = codigo_carrera_2,
                             marca_bottom_true          = marca_2 ,
                             puntpond_bottom_true       = puntpond_2 ,
                             prob_interim_bottom_true   = prob_interim_2 ,
                             prob_adaptive_bottom_true  = prob_adaptive_2 ,
                             prob_ratex_bottom_true     = prob_ratex_2) %>%
                             select("MRUN",
                                    "codigo_carrera_top_true",
                                    "marca_top_true",
                                    "puntpond_top_true",
                                    "prob_interim_top_true",
                                    "prob_adaptive_top_true",
                                    "prob_ratex_top_true",
                                    "codigo_carrera_bottom_true",
                                    "marca_bottom_true",
                                    "puntpond_bottom_true",
                                    "prob_interim_bottom_true",
                                    "prob_adaptive_bottom_true",
                                    "prob_ratex_bottom_true")

survey <- readRDS(paste(dropbox_dir,"Mistakes Structural/Code/Python/Cartillas/outputs/2022/survey_processed_with_probs.rds", sep=''))
#NOTE: this file has the subjective beliefs on probabilities (you can confirm this becaise probs have round values)
# Merge survey with clean probs for toptrue and bottomtrue
survey = merge(survey, probstrue %>% select(!c("codigo_carrera_top_true", "codigo_carrera_bottom_true","marca_top_true",
                                               "puntpond_top_true", "marca_bottom_true", "puntpond_bottom_true")), by.x = "mrun", by.y = "MRUN", all.x = TRUE)

dof <- merge(df, survey, by.x="MRUN", by.y="mrun", all.x=TRUE)
dof <- merge(dof, probsofficial %>% dplyr::select(MRUN,
                                       overall_interim, overall_adaptive, overall_ratex,
                                       prob_interim_1, prob_adaptive_1, prob_ratex_1,
                                       prob_interim_2, prob_adaptive_2, prob_ratex_2,
                                       prob_interim_3, prob_adaptive_3, prob_ratex_3,
                                       prob_interim_4, prob_adaptive_4, prob_ratex_4,
                                       prob_interim_5, prob_adaptive_5, prob_ratex_5,
                                       prob_interim_6, prob_adaptive_6, prob_ratex_6,
                                       prob_interim_7, prob_adaptive_7, prob_ratex_7,
                                       prob_interim_8, prob_adaptive_8, prob_ratex_8,
                                       prob_interim_9, prob_adaptive_9, prob_ratex_9,
                                       prob_interim_10, prob_adaptive_10,  prob_ratex_10 ) %>%
               dplyr::rename(
                             overall_prob_interim_fin = overall_interim,
                             overall_prob_adaptive_fin = overall_adaptive,
                             overall_prob_ratex_fin = overall_ratex,
                             prob_interim_1_fin  = prob_interim_1, prob_adaptive_1_fin   = prob_adaptive_1,  prob_ratex_1_fin   = prob_ratex_1,
                             prob_interim_2_fin  = prob_interim_2, prob_adaptive_2_fin   = prob_adaptive_2,  prob_ratex_2_fin   = prob_ratex_2,
                             prob_interim_3_fin  = prob_interim_3, prob_adaptive_3_fin   = prob_adaptive_3,  prob_ratex_3_fin   = prob_ratex_3,
                             prob_interim_4_fin  = prob_interim_4, prob_adaptive_4_fin   = prob_adaptive_4,  prob_ratex_4_fin   = prob_ratex_4,
                             prob_interim_5_fin  = prob_interim_5, prob_adaptive_5_fin   = prob_adaptive_5,  prob_ratex_5_fin   = prob_ratex_5,
                             prob_interim_6_fin  = prob_interim_6, prob_adaptive_6_fin   = prob_adaptive_6,  prob_ratex_6_fin   = prob_ratex_6,
                             prob_interim_7_fin  = prob_interim_7, prob_adaptive_7_fin   = prob_adaptive_7,  prob_ratex_7_fin   = prob_ratex_7,
                             prob_interim_8_fin  = prob_interim_8, prob_adaptive_8_fin   = prob_adaptive_8,  prob_ratex_8_fin   = prob_ratex_8,
                             prob_interim_9_fin  = prob_interim_9, prob_adaptive_9_fin   = prob_adaptive_9,  prob_ratex_9_fin   = prob_ratex_9,
                             prob_interim_10_fin = prob_interim_10, prob_adaptive_10_fin = prob_adaptive_10, prob_ratex_10_fin  = prob_ratex_10  ),
             by="MRUN", all.x=TRUE)

#  Add probabilities for partial portfolios (before the intervention)
dof <- merge(dof, probspartial %>% dplyr::select(MRUN,
                                              overall_interim, overall_adaptive, overall_ratex,
                                              prob_interim_1, prob_adaptive_1, prob_ratex_1,
                                              prob_interim_2, prob_adaptive_2, prob_ratex_2,
                                              prob_interim_3, prob_adaptive_3, prob_ratex_3,
                                              prob_interim_4, prob_adaptive_4, prob_ratex_4,
                                              prob_interim_5, prob_adaptive_5, prob_ratex_5,
                                              prob_interim_6, prob_adaptive_6, prob_ratex_6,
                                              prob_interim_7, prob_adaptive_7, prob_ratex_7,
                                              prob_interim_8, prob_adaptive_8, prob_ratex_8,
                                              prob_interim_9, prob_adaptive_9, prob_ratex_9,
                                              prob_interim_10, prob_adaptive_10,  prob_ratex_10 ) %>%
                            dplyr::rename(overall_prob_interim_int = overall_interim,
                                          overall_prob_adaptive_int = overall_adaptive,
                                          overall_prob_ratex_int = overall_ratex,
                                          prob_interim_1_int  = prob_interim_1, prob_adaptive_1_int   = prob_adaptive_1,  prob_ratex_1_int   = prob_ratex_1,
                                          prob_interim_2_int  = prob_interim_2, prob_adaptive_2_int   = prob_adaptive_2,  prob_ratex_2_int   = prob_ratex_2,
                                          prob_interim_3_int  = prob_interim_3, prob_adaptive_3_int   = prob_adaptive_3,  prob_ratex_3_int   = prob_ratex_3,
                                          prob_interim_4_int  = prob_interim_4, prob_adaptive_4_int   = prob_adaptive_4,  prob_ratex_4_int   = prob_ratex_4,
                                          prob_interim_5_int  = prob_interim_5, prob_adaptive_5_int   = prob_adaptive_5,  prob_ratex_5_int   = prob_ratex_5,
                                          prob_interim_6_int  = prob_interim_6, prob_adaptive_6_int   = prob_adaptive_6,  prob_ratex_6_int   = prob_ratex_6,
                                          prob_interim_7_int  = prob_interim_7, prob_adaptive_7_int   = prob_adaptive_7,  prob_ratex_7_int   = prob_ratex_7,
                                          prob_interim_8_int  = prob_interim_8, prob_adaptive_8_int   = prob_adaptive_8,  prob_ratex_8_int   = prob_ratex_8,
                                          prob_interim_9_int  = prob_interim_9, prob_adaptive_9_int   = prob_adaptive_9,  prob_ratex_9_int   = prob_ratex_9,
                                          prob_interim_10_int = prob_interim_10, prob_adaptive_10_int = prob_adaptive_10, prob_ratex_10_int  = prob_ratex_10  ),
                          by="MRUN", all.x=TRUE)

dof %<>% mutate(responded_survey = ifelse(is.na(responded_survey), 0, responded_survey))

#TODO: notice that here we are using as a minimum score the value 0 (we need to change this to the
# maximum between minimum weighted score requirement and 210)
of <- read.csv(paste(dropbox_dir, "Mistakes Structural/Code/Python/Cartillas/data/2022/seleccion_20_01_22.csv", sep=''))
car <- read.csv(paste(dropbox_dir, "/Mistakes Structural/Code/Python/Cartillas/data/2022/carreras_v2.csv", sep=''), header=TRUE, sep=";")

#NOTE: Be careful here that we are identifying the columns by their order
#TODO: We need to check that this order is correct
of_l <- reshape(of[,c(1,4:53)], direction='long',
                    varying=colnames(of[,4:53]),
                    times=c('01', '02', '03', '04', '05', '06', '07', '08', '09', '10'),
                    v.names=c('cod_carrera_pref', 'estado_pref','ptje_pref', 'lugar_pref', 'pond_acad_pref'),
                    idvar='mrun')
colnames(of_l) <- c("mrun", "pref", "codigo_carrera", "marca", "orden", "puntano", "puntpond") # this is just me not knowing how to use reshape

cutoffs <- of_l %>% filter(marca == 24) %>% group_by(codigo_carrera) %>% dplyr::summarise(num_admitted = n(), min_score = pmax(min(puntpond), 210.0))
car %<>% mutate(VACANTES_REG = VACANTES_1_SEMESTRE + VACANTES_2_SEMESTRE + SOBRECUPO_1_SEMESTRE + SOBRECUPO_2_SEMESTRE)
car <- merge(car, cutoffs, by.x="CODIGO_DEMRE", by.y="codigo_carrera", all.x=TRUE)

dof <- merge(dof, car %>% dplyr::select(CODIGO_DEMRE, VACANTES_REG, num_admitted, min_score) %>%
               mutate(min_score = ifelse(num_admitted < VACANTES_REG, 210.0, min_score)) %>%
               dplyr::rename(vacants_top_true = VACANTES_REG,
                             num_admitted_top_true = num_admitted,
                             min_score_top_true = min_score), by.x="codigo_carrera_top_true", by.y="CODIGO_DEMRE", all.x=TRUE)

dof <- merge(dof, car %>% dplyr::select(CODIGO_DEMRE, VACANTES_REG, num_admitted, min_score) %>%
               mutate(min_score = ifelse(num_admitted < VACANTES_REG, 210.0, min_score)) %>%
               dplyr::rename(vacants_bottom_true = VACANTES_REG,
                             num_admitted_bottom_true = num_admitted,
                             min_score_bottom_true = min_score), by.x="codigo_carrera_bottom_true", by.y="CODIGO_DEMRE", all.x=TRUE)


dof %<>% mutate(applied_to_top_true_int = ifelse(codigo_carrera_top_true == codigo_carrera_1_int | codigo_carrera_top_true == codigo_carrera_2_int |
                                              codigo_carrera_top_true == codigo_carrera_3_int | codigo_carrera_top_true == codigo_carrera_4_int |
                                              codigo_carrera_top_true == codigo_carrera_5_int | codigo_carrera_top_true == codigo_carrera_6_int |
                                              codigo_carrera_top_true == codigo_carrera_7_int | codigo_carrera_top_true == codigo_carrera_8_int |
                                              codigo_carrera_top_true == codigo_carrera_9_int | codigo_carrera_top_true == codigo_carrera_10_int, 1, 0),
                applied_to_bottom_true_int = ifelse(codigo_carrera_bottom_true == codigo_carrera_1_int | codigo_carrera_bottom_true == codigo_carrera_2_int |
                                              codigo_carrera_bottom_true == codigo_carrera_3_int | codigo_carrera_bottom_true == codigo_carrera_4_int |
                                              codigo_carrera_bottom_true == codigo_carrera_5_int | codigo_carrera_bottom_true == codigo_carrera_6_int |
                                              codigo_carrera_bottom_true == codigo_carrera_7_int | codigo_carrera_bottom_true == codigo_carrera_8_int |
                                              codigo_carrera_bottom_true == codigo_carrera_9_int | codigo_carrera_bottom_true == codigo_carrera_10_int, 1, 0))

dof %<>% mutate(applied_to_top_true_fin = ifelse(codigo_carrera_top_true == codigo_carrera_1_fin | codigo_carrera_top_true == codigo_carrera_2_fin |
                                              codigo_carrera_top_true == codigo_carrera_3_fin | codigo_carrera_top_true == codigo_carrera_4_fin |
                                              codigo_carrera_top_true == codigo_carrera_5_fin | codigo_carrera_top_true == codigo_carrera_6_fin |
                                              codigo_carrera_top_true == codigo_carrera_7_fin | codigo_carrera_top_true == codigo_carrera_8_fin |
                                              codigo_carrera_top_true == codigo_carrera_9_fin | codigo_carrera_top_true == codigo_carrera_10_fin, 1, 0),
                applied_to_bottom_true_fin = ifelse(codigo_carrera_bottom_true == codigo_carrera_1_fin | codigo_carrera_bottom_true == codigo_carrera_2_fin |
                                              codigo_carrera_bottom_true == codigo_carrera_3_fin | codigo_carrera_bottom_true == codigo_carrera_4_fin |
                                              codigo_carrera_bottom_true == codigo_carrera_5_fin | codigo_carrera_bottom_true == codigo_carrera_6_fin |
                                              codigo_carrera_bottom_true == codigo_carrera_7_fin | codigo_carrera_bottom_true == codigo_carrera_8_fin |
                                              codigo_carrera_bottom_true == codigo_carrera_9_fin | codigo_carrera_bottom_true == codigo_carrera_10_fin, 1, 0))

dof %<>% mutate(ordering_mistake_int = ifelse(applied_to_top_true_int == 1 & codigo_carrera_top_true != codigo_carrera_1_fin, 1, 0),
                ordering_mistake_fin = ifelse(applied_to_top_true_fin == 1 & codigo_carrera_top_true != codigo_carrera_1_fin, 1, 0))


#TODO: Check this code with Nacho seems wrong to me
# dof %<>% rowwise() %>% mutate(min_prob_adaptive_int = min(prob_adaptive_1_int + (codigo_carrera_1_int == 0), prob_adaptive_2_int + (codigo_carrera_2_int == 0),
#                                                       prob_adaptive_3_int + (codigo_carrera_3_int == 0), prob_adaptive_4_int + (codigo_carrera_4_int == 0),
#                                                       prob_adaptive_5_int + (codigo_carrera_5_int == 0), prob_adaptive_6_int + (codigo_carrera_6_int == 0),
#                                                       prob_adaptive_7_int + (codigo_carrera_7_int == 0), prob_adaptive_8_int + (codigo_carrera_8_int == 0),
#                                                       prob_adaptive_9_int + (codigo_carrera_9_int == 0), prob_adaptive_10_int + (codigo_carrera_10_int == 0)))

# dof %<>% rowwise() %>% mutate(min_prob_adaptive_fin = min(prob_adaptive_1_fin + (codigo_carrera_1_fin == 0), prob_adaptive_2_fin + (codigo_carrera_2_fin == 0),
#                                                       prob_adaptive_3_fin + (codigo_carrera_3_fin == 0), prob_adaptive_4_fin + (codigo_carrera_4_fin == 0),
#                                                       prob_adaptive_5_fin + (codigo_carrera_5_fin == 0), prob_adaptive_6_fin + (codigo_carrera_6_fin == 0),
#                                                       prob_adaptive_7_fin + (codigo_carrera_7_fin == 0), prob_adaptive_8_fin + (codigo_carrera_8_fin == 0),
#                                                       prob_adaptive_9_fin + (codigo_carrera_9_fin == 0), prob_adaptive_10_fin + (codigo_carrera_10_fin == 0)))

#TODO: Becareful with the sign here, it might not be consistent with the definitions in the paper
dof %<>% mutate(bias_in_belief_ratex_top_true    = as.numeric(prob_top_true) - as.numeric(prob_ratex_top_true)*100,
                bias_in_belief_ratex_bottom_true = as.numeric(prob_bottom_true) - as.numeric(prob_ratex_bottom_true)*100)
#TODO: review this definition
dof %<>% mutate(bias_in_belief_overall_ratex =  as.numeric(prob_any_pref) - as.numeric(overall_prob_ratex_fin)*100,
                bias_in_belief_risk_ratex =  (100 - as.numeric(prob_any_pref)) - (1 - as.numeric(overall_prob_ratex_fin))*100)
hist(dof$bias_in_belief_risk_ratex)
```

```{r}
# ELIMINAR PACES HABILITADOS
paces <- read.csv(paste(dropbox_dir, "Mistakes Structural/Code/Python/Cartillas/data/2022/habilitados_pace_v2.csv", sep=''), sep=',', header=TRUE, fileEncoding = 'UTF-8-BOM') #had to add encoding option
paces %<>% mutate(habilitado = ifelse(criterio_1 == 1 & criterio_2 == 1 & criterio_3 == 1, 1, 0))
paces_ids <- paces %>% filter(habilitado == 1) %>% pull(mrun)
dof %<>% filter(!(MRUN %in% paces_ids))
```


```{r}
hist(dof$overall_prob_adaptive_int)
hist(dof$overall_prob_adaptive_fin)
```

## Tables from paper

```{r}
path_draft_tables = paste(dropbox_dir, "Mistakes Structural/Code/R/tables", sep = "")
```

```{r}
dof %<>% mutate(open_label = ifelse(open == 1, "Yes", ifelse(open == 0, "No", NA)))
dof %<>% mutate(treatment_label = ifelse(treatment == 1, "T1",
                                         ifelse(treatment == 2, "T2",
                                                ifelse(treatment == 3, "T3",
                                                       ifelse(treatment == 4, "T4", NA)))))
dof %<>% mutate(treatment_combined = treatment,
                treatment_combined = ifelse(treatment == 2 | treatment == 3, 5, treatment))
table(dof$treatment_combined)
dof = merge(dof, scores %>% select(promedio_cm_actual, promedio_cm_anterior, mrun), by.x = "MRUN", by.y = "mrun", all.x = TRUE)
dof %<>% mutate(promedio_cm_anterior = as.numeric(gsub(",", ".", as.character(promedio_cm_anterior))),
  prom_cm  = pmax(promedio_cm_actual, promedio_cm_anterior),
                    prom_cm_above_450 = ifelse(prom_cm >= 450, 1, 0))

```

## Creating some mistake variables
```{r}
dof %<>% mutate(reduced_mistakes = ifelse(changed == 1 & valid_apps_before < valid_apps_after, 1, 0),
                not_increased_mistakes = ifelse(changed == 1 & valid_apps_before <= valid_apps_after, 1, 0),
               reduced_share_mistakes = ifelse(changed == 1 & valid_apps_before/apps_before < valid_apps_after/apps_after, 1, 0),
                 not_increased_share_mistakes = ifelse(changed == 1 & valid_apps_before/apps_before <= valid_apps_after/apps_after, 1, 0)) %>%
   mutate(overall_prob_ratex_inc = ifelse(overall_prob_ratex_fin > overall_prob_ratex_int, 1, 0),
                                risk_ratex_dec = ifelse((1 - overall_prob_ratex_fin) < (1- overall_prob_ratex_int), 1, 0),                                
          risk_ratex_inc = ifelse((1 - overall_prob_ratex_fin) > (1- overall_prob_ratex_int), 1, 0),
          risk_ratex_not_inc = ifelse((1 - overall_prob_ratex_fin) <= (1- overall_prob_ratex_int), 1, 0),
                                overall_prob_ratex_inc_abs = overall_prob_ratex_fin - overall_prob_ratex_int,
                                applied_to_top_true_fin_in_top_pref = ifelse(applied_to_top_true_fin == 1 & codigo_carrera_top_true == codigo_carrera_1_fin, 1, 0),
           applied_to_top_true_int_in_top_pref = ifelse(applied_to_top_true_int == 1 & codigo_carrera_top_true == codigo_carrera_1_int, 1, 0),
                                not_applied_to_top_true_fin_in_top_pref =  ifelse(applied_to_top_true_fin_in_top_pref == 1, 0, 1),
                                not_applied_to_top_true_fin =  ifelse(applied_to_top_true_fin == 1, 0, 1))

```

               
               
### Aggregate statistics by treatment and group
```{r}
#kable(dof %>% group_by(treatment) %>% dplyr::summarise(n=n(), op = mean(open)*100, c=mean(changed)*100,  inc = mean(increased_valid)*100, dec = mean(decreased_valid)*100, as = mean(assigned_oficial)*100, ent=mean(entered)*100, lef=mean(left)*100, cs=mean(changed_status_ass)*100, cp=mean(changed_program_ass)*100), digits=3)

#kable(dof %>% group_by(treatment) %>% dplyr::summarise(n=n(), op = 100*sd(open)/sqrt(n()), c=100*sd(changed)/sqrt(n()),  inc = 100*sd(increased_valid)/sqrt(n()), dec = 100*sd(decreased_valid)/sqrt(n()), as = 100*sd(assigned_oficial)/sqrt(n()), ent=100*sd(entered)/sqrt(n()), lef=100*sd(left)/sqrt(n()), cs=100*sd(changed_status_ass)/sqrt(n()), cp=100*sd(changed_program_ass)/sqrt(n())), digits=3)

#Create Latex table by hand
table_summary_stats_by_group = dof %>% group_by(treatment_label) %>%
  dplyr::summarise(n   = n(),
                   op  = round(mean(open)*100, 3),
                   c   = round(mean(changed)*100, 3),
                   inc = round(mean(increased_valid)*100, 3),
                   dec = round(mean(decreased_valid)*100, 3),
                   as  = round(mean(assigned_oficial)*100, 3),
                   ent = round(mean(entered)*100, 3),
                   lef = round(mean(left)*100, 3),
                   cs  = round(mean(changed_status_ass)*100, 3),
                   cp  = round(mean(changed_program_ass)*100, 3))
table_summary_stats_by_group

table_summary_stats_by_group_stderr = dof %>% group_by(treatment_label) %>%
  dplyr::summarise(n   = n(),
                   op  = round(100*sd(open)/sqrt(n()), 3),
                   c   = round(100*sd(changed)/sqrt(n()), 3),
                   inc = round(100*sd(increased_valid)/sqrt(n()), 3),
                   dec = round(100*sd(decreased_valid)/sqrt(n()), 3),
                   as  = round(100*sd(assigned_oficial)/sqrt(n()), 3),
                   ent = round(100*sd(entered)/sqrt(n()), 3),
                   lef = round(100*sd(left)/sqrt(n()), 3),
                   cs  = round(100*sd(changed_status_ass)/sqrt(n()), 3),
                   cp  = round(100*sd(changed_program_ass)/sqrt(n()), 3))
table_summary_stats_by_group_stderr

#Write latex table by hand
table_latex_file = file(paste(path_draft_tables,"stats_by_treatment.tex", sep=""))
table_header = c("\\begin{table}[H]",
                 "\\caption{Summary Statistics by Group}",
                 "\\label{tab:table_treatment_stats}",
                 "\\centerline{",
                 "\\scalebox{0.7}{",
                 "\\begin{tabular}{lcccccccccc}",
                 "\\toprule",
                 "& & & \\multicolumn{3}{c}{Application} & \\multicolumn{5}{c}{Assignment} \\\\",
                 "\\cmidrule(lr){4-6}\\cmidrule(lr){7-11}")
table_columns = paste("Treatment",
                      "Total",
                      "\\makecell*[c]{Opened [\\%]}",
                      "Modified [\\%]",
                      "\\makecell*[c]{Increased [\\%]}",
                      "\\makecell*[c]{Decreased [\\%]}",
                      "Assigned [\\%]",
                      "Entered [\\%]",
                      "Left [\\%]",
                      "\\makecell*[c]{Changed  \\\\ status [\\%]}",
                      "\\makecell*[c]{Changed  \\\\ program [\\%]}",
                      sep = " & ")
table_body = paste(table_columns, "\\\\" ," \\midrule")

space = '\\\\[0pt]'
table_stats = table_summary_stats_by_group
table_sterr_stats = table_summary_stats_by_group_stderr
#Fill table body
for(i in 1:nrow(table_stats)){
  row = c()
  for(j in 1:ncol(table_stats)){
    row_stat = table_stats[i,j]
    if(j == 1){
      row = row_stat
    }
    else{
      row = paste(row, "&", row_stat)
    }
  }
  row = paste(row, space)
  table_body = c(table_body, row)
  # Paste row for standard errors
  row = c()
  for(j in 1:ncol(table_sterr_stats)){
    row_stat = table_sterr_stats[i,j]
    if(j != 1){
      if(j == 2){
        row = paste(row, "&", "")
      }else{
        row = paste(row, "&", paste("(",row_stat,")",sep=""))
      }
    }
  }
  row = paste(row, space)
  table_body = c(table_body, row)
}

table_footer = c("\\bottomrule",
                 "\\end{tabular}",
                 "}}",
                 "{\\scriptsize Note: Opened is a binary variable equal to 1 if the student opened the personalized website, 0 otherwise. Modified is a binary variable equal to 1 if the student modified its application after the personalized websites were sent, 0 otherwise. Increased (decreased) is a binary variable equal to 1 if the student increased (decreased) the number of valid applications in their list, 0 otherwise. Assigned is a binary variable equal to 1 if the student resulted assigned at the end of the process, 0 otherwise. Entered (left) is a binary variable equal to 1 if the student resulted unassigned (assigned) given their list of preferences before the intervention and (un)assigned  given their preferenes after the intervention, 0 otherwise. Changed status (program) is a binary variable equal to 1 if the student changed their status (program) of assignment considering the list of preferences submitted before and after the intervention. Standard errors reported in parenthesis.}",
                 "\\end{table}")
table_latex_code = c(table_header, table_body, table_footer)
writeLines(table_latex_code, table_latex_file)
close(table_latex_file)

```

### Aggregate statistics by group and open
```{r}
#kable(dof %>% group_by(treatment, open) %>% dplyr::summarise(n=n(), c=mean(changed)*100,  inc = mean(increased_valid)*100, dec = mean(decreased_valid)*100, ent=mean(entered)*100, lef=mean(left)*100, cs=mean(changed_status_ass)*100, cp=mean(changed_program_ass)*100), digits=3)

#kable(dof %>% group_by(treatment, open) %>% dplyr::summarise(n=n(), c=sd(changed),  inc = sd(increased_valid), dec = sd(decreased_valid), ent=sd(entered), lef=sd(left), cs=sd(changed_status_ass), cp=sd(changed_program_ass)), digits=3)

#Create Latex table by hand
table_summary_stats_by_group = dof %>% group_by(treatment_label, open_label) %>%
dplyr::summarise(n   = n(),
                 c   = round(mean(changed)*100,3),
                 inc = round(mean(increased_valid)*100,3),
                 dec = round(mean(decreased_valid)*100,3),
                 ent = round(mean(entered)*100,3),
                 lef = round(mean(left)*100,3),
                 cs  = round(mean(changed_status_ass)*100,3),
                 cp  = round(mean(changed_program_ass)*100,3))
table_summary_stats_by_group

table_summary_stats_by_group_stderr = dof %>% group_by(treatment_label, open_label) %>%
  dplyr::summarise(n   = n(),
                   c   = round(100*sd(changed)/sqrt(n()), 3),
                   inc = round(100*sd(increased_valid)/sqrt(n()), 3),
                   dec = round(100*sd(decreased_valid)/sqrt(n()), 3),
                   ent = round(100*sd(entered)/sqrt(n()), 3),
                   lef = round(100*sd(left)/sqrt(n()), 3),
                   cs  = round(100*sd(changed_status_ass)/sqrt(n()), 3),
                   cp  = round(100*sd(changed_program_ass)/sqrt(n()), 3))
table_summary_stats_by_group_stderr

#Write latex table by hand
table_latex_file = file(paste(path_draft_tables,"stats_by_treatment_and_open.tex", sep=""))
table_header = c("\\begin{table}[H]",
                 "\\caption{Summary Statistics by Group and Reception}",
                 "\\label{tab:table_treatment_abrio_stats}",
                 "\\centerline{\\scalebox{0.7}{",
                 "\\begin{tabular}{lcccccccccc}",
                 "\\toprule",
                 "  & & & \\multicolumn{3}{c}{Application} & \\multicolumn{4}{c}{Assignment} \\\\",
                 "\\cmidrule(lr){4-6}\\cmidrule(lr){7-10}")
table_columns = paste("Treatment",
                      "\\makecell*[c]{Opened}",
                      "\\(N\\)",
                      "Modified [\\%]",
                      "\\makecell*[c]{Increased [\\%]}",
                      "\\makecell*[c]{Decreased [\\%]}",
                      "Entered [\\%]",
                      "Left [\\%]",
                      "\\makecell*[c]{Changed  \\\\ status [\\%]}",
                      "\\makecell*[c]{Changed  \\\\ program [\\%]}",
                      sep = " & ")
table_body = paste(table_columns, "\\\\" ," \\midrule")

space = '\\\\[0pt]'
table_stats = table_summary_stats_by_group
table_sterr_stats = table_summary_stats_by_group_stderr
#Fill table body
for(i in 1:nrow(table_stats)){
  row = c()
  for(j in 1:ncol(table_stats)){
    row_stat = table_stats[i,j]
    if(j == 1){
      row = row_stat
    }
    else{
      row = paste(row, "&", row_stat)
    }
  }
  row = paste(row, space)
  table_body = c(table_body, row)
  # Paste row for standard errors
  row = c()
  for(j in 1:ncol(table_sterr_stats)){
    row_stat = table_sterr_stats[i,j]
    if(j != 1){
      if(j == 2 | j == 3){
        row = paste(row, "&", "")
      }else{
        row = paste(row, "&", paste("(",row_stat,")",sep=""))
      }
    }
  }
  row = paste(row, space)
  table_body = c(table_body, row)
}

table_footer = c("\\bottomrule",
                 "\\end{tabular}",
                 "}}",
                 "{\\scriptsize Note: Opened is a binary variable equal to 1 if the student opened the personalized website, 0 otherwise. Modified is a binary variable equal to 1 if the student modified its application after the personalized websites were sent, 0 otherwise. Increased (decreased) is a binary variable equal to 1 if the student increased (decreased) the number of valid applications in their list, 0 otherwise. Entered (left) is a binary variable equal to 1 if the student resulted unassigned (assigned) given their list of preferences before the intervention and (un)assigned  given their preferenes after the intervention, 0 otherwise. Changed status (program) is a binary variable equal to 1 if the student changed their status (program) of assignment considering the list of preferences submitted before and after the intervention. Standard errors reported in parenthesis.}",
                 "\\end{table}")
table_latex_code = c(table_header, table_body, table_footer)
writeLines(table_latex_code, table_latex_file)
close(table_latex_file)

```

```{r}
dof %<>% mutate(decreased_invalid = ifelse(apps_before - valid_apps_before > apps_after - valid_apps_after, 1, 0 ))

#create new variable: aggregate treatment

dof %<>% mutate(agg_treatment=ifelse(treatment==4, 1, treatment))

dof %<>% mutate(change_ratex = overall_prob_ratex_fin-overall_prob_ratex_int)

```

```{r}
# Identifying inconsistent types
dof %<>% mutate(inconsistent_type = 0)
dof %<>% mutate(inconsistent_type = ifelse(((is.na(QID87_2 ) == FALSE) | (is.na(QID87_3 ) ==FALSE)) & ((applied_to_top_true_fin == 1 & applied_to_top_true_fin_in_top_pref==0) | applied_to_top_true_fin == 0), 1, inconsistent_type))
```


```{r}
reg_changed_aggr <- glm(changed ~ factor(agg_treatment), family="binomial", data=dof %>% subset(open==1))
summary(reg_changed_aggr)
reg_changed <- glm(changed ~ factor(treatment), family="binomial", data=dof %>% subset(open==1))
summary(reg_changed)

reg_inc_aggr <- glm(increased_valid ~ factor(agg_treatment), family="binomial", data=dof %>% subset(open==1))
summary(reg_inc_aggr)
reg_inc <- glm(increased_valid ~ factor(treatment), family="binomial", data=dof %>% subset(open==1))
summary(reg_inc)

reg_dec_aggr <- glm(decreased_valid ~ factor(agg_treatment), family="binomial", data=dof %>% subset(open==1))
reg_dec_aggr <- glm(decreased_valid ~ factor(agg_treatment), family="binomial", data=dof %>% subset(open==1 & prom_cm_above_450==1))
summary(reg_dec_aggr)
reg_dec <- glm(decreased_valid ~ factor(treatment), family="binomial", data=dof %>% subset(open==1))
summary(reg_dec)

reg_st_ass_aggr <- lm(changed_status_ass ~ factor(agg_treatment), data=dof %>% subset(open==1))
summary(reg_st_ass_aggr)
reg_st_ass_aggr <- glm(changed_status_ass ~ factor(agg_treatment), family="binomial", data=dof %>% subset(open==1))
summary(reg_st_ass_aggr)
reg_st_ass <- glm(changed_status_ass ~ factor(treatment), family="binomial", data=dof %>% subset(open==1))
summary(reg_st_ass)

reg_pr_ass_aggr <- lm(changed_program_ass ~ factor(agg_treatment), data=dof %>% subset(open==1))
summary(reg_pr_ass_aggr)
reg_st_ass_aggr <- glm(changed_program_ass ~ factor(agg_treatment), family="binomial", data=dof %>% subset(open==1))
summary(reg_st_ass_aggr)
reg_pr_ass <- glm(changed_program_ass ~ factor(treatment), family="binomial", data=dof %>% subset(open==1))
summary(reg_pr_ass)

#NEW
reg_ent_aggr1 <- lm(assigned_int ~ factor(treatment), data=dof %>% subset(open==1))
summary(reg_ent_aggr1) 
reg_ent_aggr1 <- lm(assigned_fin ~ factor(agg_treatment), data=dof %>% subset(open==1 & overall_prob_ratex_int==0.00))
summary(reg_ent_aggr1) 
reg_ent_aggr1 <- lm(assigned_fin ~ factor(agg_treatment), data=dof %>% subset(open==1 & overall_prob_ratex_int==0.00 & prom_cm_above_450==1))
summary(reg_ent_aggr1) 
reg_ent_aggr1 <- lm(entered ~ factor(agg_treatment), data=dof %>% subset(open==1 & assigned_int==0))
summary(reg_ent_aggr1) 
reg_ent_aggr1 <- lm(entered ~ factor(agg_treatment), data=dof %>% subset(open==1 & assigned_int==0 & prom_cm_above_450==1))
summary(reg_ent_aggr1) 
reg_ent1 <- lm(entered ~ factor(treatment), data=dof %>% subset(open==1 & assigned_int==0))
summary(reg_ent1)
reg_ent1 <- lm(entered ~ factor(treatment), data=dof %>% subset(open==1 & assigned_int==0 & prom_cm_above_450==1))
summary(reg_ent1)
reg_ent_aggr2 <- glm(entered ~ factor(agg_treatment), family="binomial", data=dof %>% subset(open==1))
summary(reg_ent_aggr2)
reg_ent2 <- glm(entered ~ factor(treatment), family="binomial", data=dof %>% subset(open==1))
summary(reg_ent2)
reg_ent_aggr3 <- glm(entered ~ factor(agg_treatment), family="binomial", data=dof %>% subset(open==1 & assigned_int==0))
summary(reg_ent_aggr3)
reg_ent3 <- glm(entered ~ factor(treatment), family="binomial", data=dof %>% subset(open==1 & assigned_int==0))
summary(reg_ent3)
reg_ent = reg_ent3
#Overall, we find large and positive effects with respect to entering (being assigned if not assigned with interim ROL) from both T2 and T3, especially T3. The effect for T2 is significant only when using the aggregate treatments.



reg_lft_agg <- glm(left ~ factor(agg_treatment), family="binomial", data=dof %>% subset(open==1 & assigned_int==1))
summary(reg_lft_agg)
reg_lft1 <- glm(left ~ factor(treatment), family="binomial", data=dof %>% subset(open==1))
summary(reg_lft1)
reg_lft2 <- glm(left ~ factor(treatment), family="binomial", data=dof %>% subset(open==1 & assigned_int==1))
summary(reg_lft2)
reg_lft = reg_lft2 

#NEW:
reg_top_true1_mist_aggr <- lm(applied_to_top_true_fin ~ factor(agg_treatment),data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true = 0.0))
summary(reg_top_true1_mist_aggr)
reg_top_true1_mist_aggr <- glm(applied_to_top_true_fin ~ factor(treatment), family = "binomial", data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true = 0.0))
summary(reg_top_true1_mist_aggr)
reg_top_true1_mist <- lm(applied_to_top_true_fin ~ factor(treatment),data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true = 0.0))
summary(reg_top_true1_mist)
reg_top_true1_mist <- lm(applied_to_top_true_fin ~ factor(treatment),data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true < 0.01))
summary(reg_top_true1_mist)
reg_top_true1 <- lm(applied_to_top_true_fin ~ factor(treatment),data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true > 0.0))
summary(reg_top_true1)
reg_top_true1_aggr <- lm(applied_to_top_true_int ~ factor(treatment),data=dof %>% subset(open==1 & prob_ratex_top_true > 0.0))
summary(reg_top_true1_aggr)
reg_top_true1_aggr <- lm(applied_to_top_true_fin ~ factor(agg_treatment),data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true > 0.0))
summary(reg_top_true1_aggr)
reg_top_true1_aggr <- lm(applied_to_top_true_fin ~ factor(treatment),data=dof %>% subset(open==1 & applied_to_top_true_int==0 & prob_ratex_top_true > 0.0))
summary(reg_top_true1_aggr)
reg_top_true1_aggr <- lm(applied_to_top_true_fin ~ factor(treatment)+applied_to_top_true_int,data=dof %>% subset(open==1 & inconsistent_type==0 & prob_ratex_top_true > 0.0))
summary(reg_top_true1_aggr)
reg_top_true1_aggr <- lm(applied_to_top_true_fin ~ factor(treatment),data=dof %>% subset(open==1 & applied_to_top_true_int==0 & inconsistent_type==0 & prob_ratex_top_true > 0.0))
summary(reg_top_true1_aggr)
reg_top_true1_aggr <- lm(applied_to_top_true_fin_in_top_pref ~ factor(treatment),data=dof %>% subset(open==1 & prob_ratex_top_true > 0.0 & applied_to_top_true_int_in_top_pref==0))
summary(reg_top_true1_aggr)
reg_top_true1_aggr <- lm(applied_to_top_true_fin_in_top_pref ~ factor(treatment),data=dof %>% subset(open==1 & prob_ratex_top_true > 0.0 & applied_to_top_true_int_in_top_pref==0 & inconsistent_type==0))
summary(reg_top_true1_aggr)
reg_top_true1_aggr <- lm(applied_to_top_true_fin_in_top_pref ~ factor(treatment)+applied_to_top_true_int_in_top_pref,data=dof %>% subset(open==1 & inconsistent_type==0 & prob_ratex_top_true > 0.0))
summary(reg_top_true1_aggr)
reg_top_true1_aggr <- lm(applied_to_top_true_fin ~ factor(treatment),data=dof %>% subset(open==1 & applied_to_top_true_int==0 & prob_ratex_top_true > 0.0 & inconsistent_type==0))
summary(reg_top_true1_aggr)
reg_top_true1_aggr <- lm(applied_to_top_true_fin ~ factor(treatment),data=dof %>% subset(open==1))
summary(reg_top_true1_aggr)
reg_top_true <- glm(applied_to_top_true_fin ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true > 0.0))
summary(reg_top_true)
reg_top_true_aggr <- glm(applied_to_top_true_fin ~ factor(agg_treatment), family="binomial", data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true > 0.0))
summary(reg_top_true_aggr)
reg_top_true1rst_aggr <- glm(applied_to_top_true_fin_in_top_pref ~ factor(agg_treatment), family="binomial", data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true > 0.0))
summary(reg_top_true1rst_aggr)
reg_top_true1rst <- glm(applied_to_top_true_fin_in_top_pref ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true < 0.01))
summary(reg_top_true1rst_aggr)
reg_top_true <- glm(not_applied_to_top_true_fin_in_top_pref ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true > 0.0))
summary(reg_top_true)
reg_top_true <- glm(not_applied_to_top_true_fin ~ factor(treatment), family="binomial", data=dof %>% subset(open==1))
summary(reg_top_true)
reg_top_true <- glm(applied_to_top_true_fin_in_top_pref ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true = 0.0))
summary(reg_top_true)
reg_top_true <- glm(applied_to_top_true_fin_in_top_pref ~ factor(treatment), family="binomial", data=dof %>% subset(open==1 & prob_ratex_top_true > 0.0))
summary(reg_top_true)
reg_top_true <- glm(applied_to_top_true_fin_in_top_pref ~ factor(treatment), family="binomial", data=dof %>% subset(open==1 & prob_ratex_top_true > 0.0))
summary(reg_top_true)
reg_top_true1_mist_aggr <- lm(applied_to_top_true_int_in_top_pref ~ factor(treatment),data=dof %>% subset(open==1))
summary(reg_top_true1_mist_aggr)
reg_top_true1_mist_aggr <- lm(applied_to_top_true_int_in_top_pref ~ factor(treatment),data=dof %>% subset(open==1 & prob_ratex_top_true > 0.0))
summary(reg_top_true1_mist_aggr)

#NEW - Consistent:
reg_top_true1_mist_aggr <- lm(applied_to_top_true_fin ~ factor(agg_treatment),data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true = 0.0))
summary(reg_top_true1_mist_aggr)
reg_top_true1_mist <- lm(applied_to_top_true_fin ~ factor(treatment),data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true = 0.0))
summary(reg_top_true1_mist)
reg_top_true1_mist <- lm(applied_to_top_true_fin ~ factor(treatment),data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true < 0.01))
summary(reg_top_true1_mist)
reg_top_true1 <- lm(applied_to_top_true_fin ~ factor(treatment),data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true > 0.0))
summary(reg_top_true1)
reg_top_true1 <- glm(applied_to_top_true_fin ~ factor(treatment), family = "binomial", data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true > 0.0))
summary(reg_top_true1)
reg_top_true1_aggr <- lm(applied_to_top_true_fin ~ factor(agg_treatment),data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true > 0.0))
summary(reg_top_true1_aggr)
reg_top_true <- glm(applied_to_top_true_fin ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true > 0.0))
summary(reg_top_true)
reg_top_true_aggr <- glm(applied_to_top_true_fin ~ factor(agg_treatment), family="binomial", data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true > 0.0))
summary(reg_top_true_aggr)
reg_top_true1rst_aggr <- glm(applied_to_top_true_fin_in_top_pref ~ factor(agg_treatment), family="binomial", data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true > 0.0))
summary(reg_top_true1rst_aggr)
reg_top_true1rst <- glm(applied_to_top_true_fin_in_top_pref ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true < 0.01))
summary(reg_top_true1rst_aggr)
reg_top_true <- glm(not_applied_to_top_true_fin_in_top_pref ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% subset(prob_ratex_top_true > 0.0))
summary(reg_top_true)

reg_over_confidence <- glm(risk_ratex_dec ~ factor(treatment), family="binomial", data=dof %>% subset(open==1))
summary(reg_over_confidence)
reg_over_confidence <- lm(risk_ratex_dec ~ factor(treatment), data=dof %>% subset(open==1))
summary(reg_over_confidence)
#Trying other filtering, NEW:
reg_over_confidence <- glm(risk_ratex_dec ~ factor(treatment), family="binomial", data=dof %>% subset(open==1 & overall_prob_ratex_int<1.00))
summary(reg_over_confidence)
reg_over_confidence <- lm(risk_ratex_dec ~ factor(agg_treatment), data=dof %>% subset(open==1  & overall_prob_ratex_int<1.00))
summary(reg_over_confidence)
reg_over_confidence <- lm(risk_ratex_dec ~ factor(treatment), data=dof %>% subset(open==1  & overall_prob_ratex_int<1.00))
summary(reg_over_confidence)
reg_over_confidence <- lm(risk_ratex_dec ~ factor(treatment), data=dof %>% subset(open==1  & overall_prob_ratex_int>0.00 & overall_prob_ratex_int<1.00))
summary(reg_over_confidence)
reg_over_confidence_aggr <- lm(risk_ratex_dec ~ factor(agg_treatment), data=dof %>% subset(open==1  & overall_prob_ratex_int>0.00 & overall_prob_ratex_int<1.00))
summary(reg_over_confidence_aggr)
#Same but removing overall_prob_ratex_int>0.00, instead filter on score>450.
reg_over_confidence <- lm(risk_ratex_dec ~ factor(agg_treatment), data=dof %>% subset(open==1  & prom_cm_above_450==1))
summary(reg_over_confidence)
reg_over_confidence <- lm(risk_ratex_dec ~ factor(treatment), data=dof %>% subset(open==1  & prom_cm_above_450==1))
summary(reg_over_confidence)
reg_over_confidence <- glm(risk_ratex_dec ~ factor(treatment), family="binomial", data=dof %>% subset(open==1  & prom_cm_above_450==1))
summary(reg_over_confidence)
reg_over_confidence <- lm(risk_ratex_dec ~ factor(treatment), data=dof %>% subset(open==1  & prom_cm_above_450==1 & overall_prob_ratex_int<1.00))
summary(reg_over_confidence)
reg_over_confidence <- lm(overall_prob_ratex_int ~ factor(treatment), data=dof %>% subset(open==1  & prom_cm_above_450==1))
summary(reg_over_confidence)
reg_over_confidence <- lm(risk_ratex_inc ~ factor(treatment), data=dof %>% subset(open==1  & prom_cm_above_450==1 & overall_prob_ratex_int>0.00))
summary(reg_over_confidence)
reg_over_confidence <- lm(risk_ratex_dec ~ factor(agg_treatment), data=dof %>% subset(open==1  & prom_cm_above_450==1 & overall_prob_ratex_int<1.00))
summary(reg_over_confidence)
#8% of the students decrease their risk in the C group. T3 increases this share by 2.8points.

reg_over_confidence_aggr <- lm(overall_prob_ratex_int ~ factor(treatment), data=dof %>% subset(open==1))
summary(reg_over_confidence_aggr)
reg_over_confidence_aggr <- lm(change_ratex ~ factor(treatment), data=dof %>% subset(open==1  & changed==1 &  overall_prob_ratex_int==0.00))
summary(reg_over_confidence_aggr)
reg_over_confidence_aggr <- lm(change_ratex ~ factor(treatment), data=dof %>% subset(open==1  & changed==1 &  overall_prob_ratex_int<0.01))
summary(reg_over_confidence_aggr)
#use the 450 threshold
reg_over_confidence_aggr <- lm(change_ratex ~ factor(agg_treatment), data=dof %>% subset(open==1  & changed==1 &  overall_prob_ratex_int<0.01))
summary(reg_over_confidence_aggr)
#Same but removing overall_prob_ratex_int>0.00, instead filter on score>450.
reg_over_confidence_aggr <- lm(change_ratex ~ factor(treatment), data=dof %>% subset(open==1  & changed==1 &  overall_prob_ratex_int==0.00 & prom_cm_above_450==1 ))
summary(reg_over_confidence_aggr)
reg_over_confidence_aggr <- lm(change_ratex ~ factor(treatment), data=dof %>% subset(open==1  & changed==1 &  overall_prob_ratex_int<0.01 & prom_cm_above_450==1 ))
summary(reg_over_confidence_aggr)
#use the 450 threshold
reg_over_confidence_aggr <- lm(change_ratex ~ factor(treatment), data=dof %>% subset(open==1  &  overall_prob_ratex_int<0.01 & prom_cm_above_450==1 ))
summary(reg_over_confidence_aggr)
reg_over_confidence_aggr <- lm(change_ratex ~ factor(agg_treatment), data=dof %>% subset(open==1  &  overall_prob_ratex_int<0.01 & prom_cm_above_450==1 ))
summary(reg_over_confidence_aggr)
reg_over_confidence_aggr <- lm(change_ratex ~ factor(agg_treatment), data=dof %>% subset(open==1  &  overall_prob_ratex_int<0.99 & prom_cm_above_450==1 ))
summary(reg_over_confidence_aggr)
#Students with very low initial proba of being admitted significantly decreases the risk of the ROL in the final stage: students in the C group on average increases the overall probability of being admitted by 6 points in the final ROL vs interim. Compared to this baseline, students in T2 increases their overall probability of being admitted by 2.6points more, and students in T3 by 3.2 points more.
#Note that here, it is important to aggregate to get significant results.
reg_over_confidence_aggr <- lm(change_ratex ~ factor(treatment), data=dof %>% subset(open==1  &  overall_prob_ratex_int<1.00 & prom_cm_above_450==1 ))
summary(reg_over_confidence_aggr)
reg_over_confidence_aggr <- lm(change_ratex ~ factor(treatment), data=dof %>% subset(open==1 &  overall_prob_ratex_int<=0.99 & prom_cm_above_450==1 ))
summary(reg_over_confidence_aggr)
reg_over_confidence_aggr <- lm(change_ratex ~ factor(treatment), data=dof %>% subset(overall_prob_ratex_int<0.10 & prom_cm_above_450==1 ))
summary(reg_over_confidence_aggr) #we get results when not conditioning on open...
reg_over_confidence_aggr <- lm(change_ratex ~ factor(treatment), data=dof %>% subset(open==1 &  overall_prob_ratex_int<0.10 & prom_cm_above_450==1 ))
summary(reg_over_confidence_aggr)
reg_over_confidence_aggr <- lm(change_ratex ~ factor(treatment), data=dof %>% subset(open==1 &  general_message==2 & prom_cm_above_450==1 ))
summary(reg_over_confidence_aggr)
reg_over_confidence_aggr <- lm(change_ratex ~ factor(treatment), data=dof %>% subset(general_message==2 & prom_cm_above_450==1 ))
summary(reg_over_confidence_aggr) #Same: result when we do not condition on opening
reg_over_confidence_aggr <- lm(change_ratex ~ factor(agg_treatment), data=dof %>% subset(open==1 &  general_message==2 & prom_cm_above_450==1 ))
summary(reg_over_confidence_aggr)
#Very similar, and strong result, when restricting to students in general_message==2
#Again, only there when we aggregate.

#TODO: CHECK THIS!
reg_over_confidence <- glm(risk_ratex_dec ~ factor(treatment), family="binomial", data=dof %>% subset(open==1))
summary(reg_over_confidence)
reg_over_confidence <- glm(risk_ratex_inc ~ factor(treatment), family="binomial", data=dof %>% subset(open==1))
summary(reg_over_confidence)
 #NEW
 reg_over_confidence <- lm(risk_ratex_inc ~ factor(treatment), data=dof %>% subset(open==1 &          overall_prob_ratex_int>0.00))
 summary(reg_over_confidence)
  reg_over_confidence <- lm(risk_ratex_inc ~ factor(agg_treatment), data=dof %>% subset(open==1 &          overall_prob_ratex_int>0.00))
 summary(reg_over_confidence)


#Combining treatments 2 and 3 to get more power
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment_combined), data=dof %>% subset(open==1) %>% filter(changed == 1) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1))
summary(reg_over_confidence)

#Including covariates
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment) + factor(strata_region) + factor(strata_sexo) + factor(strata_score) + gets_sms, data=dof %>% subset(open==1) %>%  filter(changed == 1) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1 & strata_region != 4))
summary(reg_over_confidence)

reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment_combined) + factor(strata_region) + factor(strata_sexo) + factor(strata_score) + gets_sms, data=dof %>% subset(open==1) %>% filter(changed == 1) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1 & strata_region != 4))
summary(reg_over_confidence)


stargazer(reg_changed, reg_inc, reg_dec, reg_ent, reg_lft, reg_st_ass, reg_pr_ass, keep.stat="n",
          add.lines = list(c(2,round(exp(coef(reg_changed))[2],3), round(exp(coef(reg_inc))[2],3), round(exp(coef(reg_dec))[2],3), round(exp(coef(reg_ent))[2],3), round(exp(coef(reg_lft))[2],3),  round(exp(coef(reg_st_ass))[2],3), round(exp(coef(reg_pr_ass))[2],3)),
                           c(3,round(exp(coef(reg_changed))[3],3), round(exp(coef(reg_inc))[3],3), round(exp(coef(reg_dec))[3],3), round(exp(coef(reg_ent))[3],3), round(exp(coef(reg_lft))[3],3), round(exp(coef(reg_st_ass))[3],3), round(exp(coef(reg_pr_ass))[3],3)),
                           c(4,round(exp(coef(reg_changed))[4],3), round(exp(coef(reg_inc))[4],3), round(exp(coef(reg_dec))[4],3), round(exp(coef(reg_ent))[4],3), round(exp(coef(reg_lft))[4],3), round(exp(coef(reg_st_ass))[4],3), round(exp(coef(reg_pr_ass))[2],3))), digits=3,
                         out = paste(path_draft_tables,"regs_odds_open.tex", sep=""))

#TODO: this table has to be pasted by hand in the paper. It is easy though.
```


### Aggregate statistics by group and message type
```{r}
# kable(dof %>% group_by(treatment, open, general_message) %>% dplyr::summarise(n=n(), c=mean(changed)*100,  inc = mean(increased_valid)*100, dec = mean(decreased_valid)*100, as = mean(assigned_oficial)*100, ent=mean(entered)*100, lef=mean(left)*100, cs=mean(changed_status_ass)*100, cp=mean(changed_program_ass)*100), digits=3)

# kable(dof %>% group_by(treatment, open, general_message) %>% dplyr::summarise(n=n(), c=sd(changed),  inc = sd(increased_valid), dec = sd(decreased_valid), as = sd(assigned_oficial), ent=sd(entered), lef=sd(left), cs=sd(changed_status_ass), cp=sd(changed_program_ass)), digits=3)

#Create Latex table by hand
table_summary_stats_by_group = dof %>% group_by(treatment_label, open_label, general_message) %>%
dplyr::summarise(n   = n(),
                 c   = round(mean(changed)*100,3),
                 inc = round(mean(increased_valid)*100,3),
                 dec = round(mean(decreased_valid)*100,3),
                 as = round(mean(assigned_oficial)*100,3),
                 ent = round(mean(entered)*100,3),
                 lef = round(mean(left)*100,3),
                 cs  = round(mean(changed_status_ass)*100,3),
                 cp  = round(mean(changed_program_ass)*100,3))
table_summary_stats_by_group

table_summary_stats_by_group_stderr = dof %>% group_by(treatment_label, open_label, general_message) %>%
  dplyr::summarise(n   = n(),
                   c   = round(100*sd(changed)/sqrt(n()), 3),
                   inc = round(100*sd(increased_valid)/sqrt(n()), 3),
                   dec = round(100*sd(decreased_valid)/sqrt(n()), 3),
                   as = round(100*sd(assigned_oficial)/sqrt(n()), 3),
                   ent = round(100*sd(entered)/sqrt(n()), 3),
                   lef = round(100*sd(left)/sqrt(n()), 3),
                   cs  = round(100*sd(changed_status_ass)/sqrt(n()), 3),
                   cp  = round(100*sd(changed_program_ass)/sqrt(n()), 3))
table_summary_stats_by_group_stderr

#Write latex table by hand
table_latex_file = file(paste(path_draft_tables,"stats_by_treatment_and_open_and_message.tex", sep=""))
table_header = c("\\begin{table}[H]",
                 "\\caption{Summary Statistics by Treatment, Reception and Message Group}",
                 "\\label{tab:table_treatment_stats_by_open_and_message}",
                 "\\centerline{\\scalebox{0.6}{",
                 "\\begin{tabular}{lcccccccccccc}",
                 "\\toprule",
                 "& & & & \\multicolumn{3}{c}{Application} & \\multicolumn{5}{c}{Assignment} \\\\",
                 "\\cmidrule(lr){5-7}\\cmidrule(lr){8-12}")
table_columns = paste("Treatment",
                      "\\makecell*[c]{Open}",
                      "\\makecell*[c]{Group}",
                      "\\(N\\)",
                      "Modified [\\%]",
                      "\\makecell*[c]{Increased [\\%]}",
                      "\\makecell*[c]{Decreased [\\%]}",
                      "Assigned [\\%]",
                      "Entered [\\%]",
                      "Left [\\%]",
                      "\\makecell*[c]{Changed  \\\\ status [\\%]}",
                      "\\makecell*[c]{Changed  \\\\ program [\\%]}",
                      sep = " & ")
table_body = paste(table_columns, "\\\\" ," \\midrule")

space = '\\\\[0pt]'
table_stats = table_summary_stats_by_group
table_sterr_stats = table_summary_stats_by_group_stderr
#Fill table body
ct = 0
for(i in 1:nrow(table_stats)){
  ct = ct + 1
  row = c()
  for(j in 1:ncol(table_stats)){
    row_stat = table_stats[i,j]
    if((j == 1 | j == 2) & ct != 2){
      row_stat = ""
    }
    if(j == 1){
      row = row_stat
    }
    else{
      row = paste(row, "&", row_stat)
    }
  }
  row = paste(row, space)
  table_body = c(table_body, row)
  # Paste row for standard errors
  row = c()
  for(j in 1:ncol(table_sterr_stats)){
    row_stat = table_sterr_stats[i,j]
    if(j != 1){
      if(j == 2 | j == 3 | j == 4){
        row = paste(row, "&", "")
      }else{
        row = paste(row, "&", paste("(",row_stat,")",sep=""))
      }
    }
  }
  row = paste(row, space)
  table_body = c(table_body, row)
  #Include midrules
  if(i%%3==0){
    table_body = c(table_body, "\\midrule")
    ct = 0
  }
}

table_footer = c("\\end{tabular}",
                 "}}",
                 "{\\scriptsize Note: Opened is a binary variable equal to 1 if the student opened the personalized website, 0 otherwise. Modified is a binary variable equal to 1 if the student modified its application after the personalized websites were sent, 0 otherwise. Increased (decreased) is a binary variable equal to 1 if the student increased (decreased) the number of valid applications in their list, 0 otherwise. Assigned is a binary variable equal to 1 if the student resulted assigned at the end of the process, 0 otherwise. Entered (left) is a binary variable equal to 1 if the student resulted unassigned (assigned) given their list of preferences before the intervention and (un)assigned  given their preferenes after the intervention, 0 otherwise. Changed status (program) is a binary variable equal to 1 if the student changed their status (program) of assignment considering the list of preferences submitted before and after the intervention. Standard errors reported in parenthesis.}",
                 "\\end{table}")
table_latex_code = c(table_header, table_body, table_footer)
writeLines(table_latex_code, table_latex_file)
close(table_latex_file)
```

## Regressions and Odd-ratios among openers in Safety group
```{r}
reg_changed <- glm(changed ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 2))
summary(reg_changed)

reg_inc <- lm(increased_valid ~ factor(agg_treatment), data=dof %>% subset(open==1) %>% filter(general_message == 2))
summary(reg_inc)
reg_inc <- glm(increased_valid ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 2))
summary(reg_inc)

reg_dec <- glm(decreased_valid ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 2))
summary(reg_dec)

reg_pr_ass <- glm(changed_program_ass ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 2))
summary(reg_pr_ass)

reg_st_ass <- glm(changed_status_ass ~ factor(treatment), family="binomial", data=dof %>% subset(open==1)  %>% filter(general_message == 2))
summary(reg_st_ass)

reg_ent <- glm(entered ~ factor(treatment), family="binomial", data=dof %>% subset(open==1)  %>% filter(general_message == 2))
summary(reg_ent)
#NEW
reg_ent <- lm(entered ~ factor(agg_treatment), data=dof %>% subset(open==1 & assigned_int==0)  %>% filter(general_message == 2))
summary(reg_ent)
reg_ent <- lm(entered ~ factor(treatment), data=dof %>% subset(open==1 & assigned_int==0)  %>% filter(general_message == 2))
summary(reg_ent)
reg_ent <- glm(entered ~ factor(treatment), family="binomial", data=dof %>% subset(open==1 & assigned_int==0)  %>% filter(general_message == 2))
summary(reg_ent)
#NEW: adding score>450
reg_ent <- lm(entered ~ factor(agg_treatment), data=dof %>% subset(open==1 & assigned_int==0 & prom_cm_above_450==1)  %>% filter(general_message == 2))
summary(reg_ent)
#Strong effect on entering: + 2.8pp/3.4pp from a baseline of 6%.
reg_ent <- lm(entered ~ factor(treatment), data=dof %>% subset(open==1 & assigned_int==0 & prom_cm_above_450==1)  %>% filter(general_message == 2))
summary(reg_ent)
#Holds when not aggregating treatment
reg_ent <- glm(entered ~ factor(treatment), family="binomial", data=dof %>% subset(open==1 & assigned_int==0 & prom_cm_above_450==1)  %>% filter(general_message == 2))
summary(reg_ent)


reg_lft <- glm(left ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 2))
summary(reg_lft)

reg_top_true <- glm(not_applied_to_top_true_fin_in_top_pref ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 2) %>% 
                      subset(prob_ratex_top_true > 0.0))
summary(reg_top_true)



#TODO: CHECK THIS!
reg_over_confidence <- glm(risk_ratex_dec ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 2))
summary(reg_over_confidence)
reg_over_confidence <- glm(risk_ratex_inc ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 2))
summary(reg_over_confidence)
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment), data=dof %>% subset(open==1) %>% filter(general_message == 2))
summary(reg_over_confidence)
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment), data=dof %>% subset(open==1) %>% filter(general_message == 2) %>% filter(changed == 1))
summary(reg_over_confidence)
#NOTE: This last result would be good if we could get statistically significant results for T3
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment), data=dof %>% subset(open==1) %>% filter(general_message == 2) %>% filter(changed == 1) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1))
summary(reg_over_confidence)

#Combining treatments 2 and 3 to get more power
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment_combined), data=dof %>% subset(open==1) %>% filter(general_message == 2) %>% filter(changed == 1) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1))
summary(reg_over_confidence)
#NEW
dof %<>% mutate(treat=ifelse(agg_treatment==3,2, agg_treatment))

reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treat), data=dof %>% subset(open==1) %>% filter(general_message == 2) %>% filter(changed == 1) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1))
summary(reg_over_confidence)
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treat), data=dof %>% subset(open==1) %>% filter(general_message == 2) %>% filter(changed == 1) %>% filter(valid_apps_before > 0))
summary(reg_over_confidence)
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treat), data=dof %>% subset(open==1) %>% filter(general_message == 2) %>% filter(changed == 1))
summary(reg_over_confidence)
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treat), data=dof %>% subset(open==1) %>% filter(general_message == 2) %>% filter(valid_apps_before > 0) %>% filter(changed == 1))
summary(reg_over_confidence)
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treat), data=dof %>% subset(open==1 & general_message == 2 & valid_apps_before!=0))
summary(reg_over_confidence)
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treat), data=dof %>% subset(open==1 & general_message == 2 & changed == 1)) 
summary(reg_over_confidence)                         

#Including covariates
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment) + factor(strata_region) + factor(strata_sexo) + factor(strata_score) + gets_sms, data=dof %>% subset(open==1) %>% filter(general_message == 2) %>% filter(changed == 1) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1 & strata_region != 4))
summary(reg_over_confidence)

reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment_combined) + factor(strata_region) + factor(strata_sexo) + factor(strata_score) + gets_sms, data=dof %>% subset(open==1) %>% filter(general_message == 2) %>% filter(changed == 1) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1 & strata_region != 4))
summary(reg_over_confidence)

# Adding more controls
reg_over_confidence <- lm(overall_prob_ratex_fin ~ overall_prob_ratex_int + factor(treatment) + factor(strata_region) + factor(strata_sexo) + factor(strata_score) + gets_sms + factor(pumi), data = dof %>% subset(open==1) %>% filter(general_message == 2) %>% filter(changed == 1) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1 & strata_region != 4))
summary(reg_over_confidence)

reg_over_confidence <- lm(overall_prob_ratex_fin ~overall_prob_ratex_int + factor(treatment_combined) + factor(strata_region) + factor(strata_sexo) + factor(strata_score) + gets_sms + factor(pumi), data = dof %>% subset(open==1) %>% filter(general_message == 2) %>% filter(changed == 1) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1 & strata_region != 4))
summary(reg_over_confidence)




#NEW: 
dof %<>% mutate(overconf=ifelse(bias_in_belief_overall_ratex>0, 1,0))
dof %<>% mutate(underconf=ifelse(bias_in_belief_overall_ratex<0, 1,0))
bias_belief <- lm(overconf ~ factor(treatment), data=dof %>% subset(open==1 & general_message == 2) )
summary(bias_belief)
bias_belief <- lm(overconf ~ factor(agg_treatment), data=dof %>% subset(open==1 & general_message == 2) )
summary(bias_belief)
bias_belief <- lm(underconf ~ factor(treatment), data=dof %>% subset(open==1 & general_message == 2) )
summary(bias_belief)
bias_belief <- lm(underconf ~ factor(agg_treatment), data=dof %>% subset(open==1 & general_message == 2) )
summary(bias_belief)
bias_belief <- lm(overconf ~ factor(treatment), data=dof %>% subset(open==1 & general_message == 1) )
summary(bias_belief)
bias_belief <- lm(overconf ~ factor(agg_treatment), data=dof %>% subset(open==1 & general_message == 1) )
summary(bias_belief)
bias_belief <- lm(underconf ~ factor(treatment), data=dof %>% subset(open==1 & general_message == 1) )
summary(bias_belief)
bias_belief <- lm(underconf ~ factor(treat), data=dof %>% subset(open==1 & general_message == 1) )
summary(bias_belief)

#NEW
bias_belief <- lm(abs(bias_in_belief_overall_ratex) ~ factor(treatment), data=dof %>% subset(open==1) )
summary(bias_belief)
bias_belief <- lm(abs(bias_in_belief_overall_ratex) ~ factor(treatment), data=dof %>% subset(open==1) )
summary(bias_belief)
bias_belief <- lm(abs(bias_in_belief_overall_ratex) ~ factor(treatment), data=dof %>% subset(open==1 & general_message == 2))
summary(bias_belief)
bias_belief <- lm(abs(bias_in_belief_overall_ratex) ~ factor(treat), data=dof %>% subset(open==1 & overall_prob_ratex_int==0.00))
summary(bias_belief)
bias_belief <- lm(abs(bias_in_belief_overall_ratex) ~ factor(treat), data=dof %>% subset(open==1 & overall_prob_interim_int<0.20))
summary(bias_belief)
bias_belief <- lm(abs(bias_in_belief_overall_ratex) ~ factor(treatment), data=dof %>% subset(open==1 & overall_prob_interim_int<0.20))
summary(bias_belief)

#NEW:
dof %<>% mutate(mistake_any=ifelse( valid_apps_after < apps_after, 1,0))
any_mistake <- lm(mistake_any ~ factor(treatment), data=dof %>% subset(open==1 & valid_apps_before < apps_before))
summary(any_mistake)
any_mistake <- lm(mistake_any ~ factor(agg_treatment), data=dof %>% subset(open==1 & valid_apps_before < apps_before & prom_cm_above_450==1))
summary(any_mistake)
any_mistake <- lm(mistake_any ~ factor(treat), data=dof %>% subset(open==1 & valid_apps_before < apps_before))
summary(any_mistake)
dof %<>% mutate(know_mistake=ifelse(knows_adm_mistake=="S", 1,0))
any_mistake <- lm(know_mistake ~ factor(treat), data=dof %>% subset(open==1 & valid_apps_before < apps_before))
summary(any_mistake)



stargazer(reg_changed, reg_inc, reg_dec, reg_ent, reg_lft,  reg_st_ass, reg_pr_ass, keep.stat="n",
          add.lines = list(c(2,round(exp(coef(reg_changed))[2],3), round(exp(coef(reg_inc))[2],3), round(exp(coef(reg_dec))[2],3), round(exp(coef(reg_ent))[2],3), round(exp(coef(reg_lft))[2],3), round(exp(coef(reg_st_ass))[2],3), round(exp(coef(reg_pr_ass))[2],3)),
                           c(3,round(exp(coef(reg_changed))[3],3), round(exp(coef(reg_inc))[3],3), round(exp(coef(reg_dec))[3],3), round(exp(coef(reg_ent))[3],3), round(exp(coef(reg_lft))[3],3),  round(exp(coef(reg_st_ass))[3],3), round(exp(coef(reg_pr_ass))[3],3)),
                           c(4,round(exp(coef(reg_changed))[4],3), round(exp(coef(reg_inc))[4],3), round(exp(coef(reg_dec))[4],3), round(exp(coef(reg_ent))[4],3), round(exp(coef(reg_lft))[4],3), round(exp(coef(reg_st_ass))[4],3), round(exp(coef(reg_pr_ass))[2],3))), digits=3,
                         out = paste(path_draft_tables,"regs_odds_open_safety.tex", sep=""))

#TODO: this table has to be pasted by hand in the paper. It is easy though.
```


## Regressions and Odd-ratios among openers in Reach group
```{r}
reg_changed <- glm(changed ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 1))
summary(reg_changed)

reg_inc <- glm(increased_valid ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 1))
summary(reg_inc)

reg_dec <- glm(decreased_valid ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 1))
summary(reg_dec)

reg_pr_ass <- glm(changed_program_ass ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 1))
summary(reg_pr_ass)

reg_st_ass <- glm(changed_status_ass ~ factor(treatment), family="binomial", data=dof %>% subset(open==1)  %>% filter(general_message == 1))
summary(reg_st_ass)

reg_ent <- glm(entered ~ factor(treatment), family="binomial", data=dof %>% subset(open==1)  %>% filter(general_message == 1))
summary(reg_ent)

reg_lft <- glm(left ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 1))
summary(reg_lft)

reg_top_true <- glm(not_applied_to_top_true_fin_in_top_pref ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>%  filter(inconsistent_type != 1) %>% 
                     filter(general_message == 1) %>%
                      subset(prob_ratex_top_true > 0.00))
summary(reg_top_true)

reg_over_confidence <- glm(risk_ratex_dec ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 1))
summary(reg_over_confidence)



#TODO: CHECK THIS!
reg_over_confidence <- glm(risk_ratex_dec ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 1))
summary(reg_over_confidence)
reg_over_confidence <- glm(risk_ratex_inc ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 1))
summary(reg_over_confidence)
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment), data=dof %>% subset(open==1) %>% filter(general_message == 1))
summary(reg_over_confidence)
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment), data=dof %>% subset(open==1) %>% filter(general_message == 1) %>% filter(changed == 1))
summary(reg_over_confidence)

reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment), data=dof %>% subset(open==1) %>% filter(general_message == 1) %>% filter(changed == 1) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1))
summary(reg_over_confidence)

#Combining treatments 2 and 3 to get more power
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment_combined), data=dof %>% subset(open==1) %>% filter(general_message == 1) %>% filter(changed == 1) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1))
summary(reg_over_confidence)

#Including covariates
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment) + factor(strata_region) + factor(strata_sexo) + factor(strata_score) + gets_sms, data=dof %>% subset(open==1) %>% filter(general_message == 1) %>% filter(changed == 1) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1 & strata_region != 4))
summary(reg_over_confidence)

reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment_combined) + factor(strata_region) + factor(strata_sexo) + factor(strata_score) + gets_sms, data=dof %>% subset(open==1) %>% filter(general_message == 1) %>% filter(changed == 1) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1 & strata_region != 4))
summary(reg_over_confidence)


stargazer(reg_changed, reg_inc, reg_dec, reg_ent, reg_lft,  reg_st_ass, reg_pr_ass, keep.stat="n",
          add.lines = list(c(2,round(exp(coef(reg_changed))[2],3), round(exp(coef(reg_inc))[2],3), round(exp(coef(reg_dec))[2],3), round(exp(coef(reg_ent))[2],3), round(exp(coef(reg_lft))[2],3), round(exp(coef(reg_st_ass))[2],3), round(exp(coef(reg_pr_ass))[2],3)),
                           c(3,round(exp(coef(reg_changed))[3],3), round(exp(coef(reg_inc))[3],3), round(exp(coef(reg_dec))[3],3), round(exp(coef(reg_ent))[3],3), round(exp(coef(reg_lft))[3],3),  round(exp(coef(reg_st_ass))[3],3), round(exp(coef(reg_pr_ass))[3],3)),
                           c(4,round(exp(coef(reg_changed))[4],3), round(exp(coef(reg_inc))[4],3), round(exp(coef(reg_dec))[4],3), round(exp(coef(reg_ent))[4],3), round(exp(coef(reg_lft))[4],3), round(exp(coef(reg_st_ass))[4],3), round(exp(coef(reg_pr_ass))[2],3))), digits=3,
                         out = paste(path_draft_tables,"regs_odds_open_reach.tex", sep=""))

#TODO: this table has to be pasted by hand in the paper. It is easy though.
```

## Regressions and Odd-ratios among openers in Explore group
```{r}
reg_changed <- glm(changed ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 3))
summary(reg_changed)

reg_inc <- glm(increased_valid ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 3))
summary(reg_inc)

reg_dec <- glm(decreased_valid ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 3))
summary(reg_dec)

reg_pr_ass <- glm(changed_program_ass ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 3))
summary(reg_pr_ass)

reg_st_ass <- glm(changed_status_ass ~ factor(treatment), family="binomial", data=dof %>% subset(open==1)  %>% filter(general_message == 3))
summary(reg_st_ass)

reg_ent <- glm(entered ~ factor(treatment), family="binomial", data=dof %>% subset(open==1)  %>% filter(general_message == 3))
summary(reg_ent)

reg_lft <- glm(left ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 3) %>% filter(misfit==1 & strata_region != 4))
summary(reg_lft)

reg_top_true <- glm(not_applied_to_top_true_fin_in_top_pref ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 3) %>%
                      subset(prob_ratex_top_true > 0.0))
summary(reg_top_true)


#TODO: CHECK THIS!
#Testing
reg_top_true <- glm(not_applied_to_top_true_fin_in_top_pref ~ overall_prob_ratex_int + factor(treatment) + factor(strata_region) + factor(strata_sexo) + factor(strata_score) + gets_sms + factor(pumi), 
                    family = "binomial",
                    data = dof %>% subset(open==1) %>% filter(general_message == 3) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1 & strata_region != 4) %>% subset(prob_ratex_top_true > 0.0))
summary(reg_top_true)
# With filter of changed = 1
reg_top_true <- glm(not_applied_to_top_true_fin_in_top_pref ~ overall_prob_ratex_int + factor(treatment) + factor(strata_region) + factor(strata_sexo) + factor(strata_score) + gets_sms + factor(pumi), 
                    family = "binomial",
                    data = dof %>% subset(open==1) %>% filter(general_message == 3) %>% filter(valid_apps_before > 0) %>% filter(changed == 1) %>% filter(misfit == 1 & strata_region != 4) %>% subset(prob_ratex_top_true > 0.0))
summary(reg_top_true)
# With filter of changed = 0
reg_top_true <- glm(not_applied_to_top_true_fin_in_top_pref ~ overall_prob_ratex_int + factor(treatment) + factor(strata_region) + factor(strata_sexo) + factor(strata_score) + gets_sms + factor(pumi), 
                    family = "binomial",
                    data = dof %>% subset(open==1) %>% filter(general_message == 3) %>% filter(valid_apps_before > 0) %>% filter(changed == 0) %>% filter(misfit == 1 & strata_region != 4) %>% subset(prob_ratex_top_true > 0.0))
summary(reg_top_true)




#TODO: CHECK THIS!
reg_over_confidence <- glm(risk_ratex_dec ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 3))
summary(reg_over_confidence)


reg_adm_mistakes <- glm(not_increased_share_mistakes  ~ factor(treatment), family="binomial", 
                        data = dof  %>% 
                          filter(misfit==1 & strata_region != 4) %>% 
                          filter(valid_apps_before < apps_before) %>% 
                          subset(open==1) %>%
                          subset(changed == 1) %>% 
                          filter(general_message == 3))
summary(reg_adm_mistakes)


reg_over_confidence <- glm(risk_ratex_dec ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 3))
summary(reg_over_confidence)
reg_over_confidence <- glm(risk_ratex_inc ~ factor(treatment), family="binomial", data=dof %>% subset(open==1) %>% filter(general_message == 3))
summary(reg_over_confidence)
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment), data=dof %>% subset(open==1) %>% filter(general_message == 3))
summary(reg_over_confidence)
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment), data=dof %>% subset(open==1) %>% filter(general_message == 3) %>% filter(changed == 1))
summary(reg_over_confidence)


reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment), data=dof %>% subset(open==1) %>% filter(general_message == 3) %>% filter(changed == 1) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1))
summary(reg_over_confidence)

#Combining treatments 2 and 3 to get more power
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment_combined), data=dof %>% subset(open==1) %>% filter(general_message == 3) %>% filter(changed == 1) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1))
summary(reg_over_confidence)

#Including covariates
reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment) + factor(strata_region) + factor(strata_sexo) + factor(strata_score) + gets_sms, data=dof %>% subset(open==1) %>% filter(general_message == 3) %>% filter(changed == 1) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1 & strata_region != 4))
summary(reg_over_confidence)

reg_over_confidence <- lm(overall_prob_ratex_fin ~ factor(treatment_combined) + factor(strata_region) + factor(strata_sexo) + factor(strata_score) + gets_sms, data=dof %>% subset(open==1) %>% filter(general_message == 3) %>% filter(changed == 1) %>% filter(valid_apps_before > 0) %>% filter(misfit == 1 & strata_region != 4))
summary(reg_over_confidence)



#Testing 
dof %>% filter(open == 1) %>% group_by(general_message, treatment_label) %>% summarise(mean_prob = mean(overall_prob_ratex_fin, na.rm = TRUE),
                  n = n())


stargazer(reg_changed, reg_inc, reg_dec, reg_ent, reg_lft,  reg_st_ass, reg_pr_ass, keep.stat="n",
          add.lines = list(c(2,round(exp(coef(reg_changed))[2],3), round(exp(coef(reg_inc))[2],3), round(exp(coef(reg_dec))[2],3), round(exp(coef(reg_ent))[2],3), round(exp(coef(reg_lft))[2],3), round(exp(coef(reg_st_ass))[2],3), round(exp(coef(reg_pr_ass))[2],3)),
                           c(3,round(exp(coef(reg_changed))[3],3), round(exp(coef(reg_inc))[3],3), round(exp(coef(reg_dec))[3],3), round(exp(coef(reg_ent))[3],3), round(exp(coef(reg_lft))[3],3),  round(exp(coef(reg_st_ass))[3],3), round(exp(coef(reg_pr_ass))[3],3)),
                           c(4,round(exp(coef(reg_changed))[4],3), round(exp(coef(reg_inc))[4],3), round(exp(coef(reg_dec))[4],3), round(exp(coef(reg_ent))[4],3), round(exp(coef(reg_lft))[4],3), round(exp(coef(reg_st_ass))[4],3), round(exp(coef(reg_pr_ass))[2],3))), digits=3,
                         out = paste(path_draft_tables,"regs_odds_open_explore.tex", sep=""))

#TODO: this table has to be pasted by hand in the paper. It is easy though.
```

### Statistics by mistakers
Note: treatments 2 and 3 add the sentence "Verifica que cumples con los requisitos" if the preference is not valid.

```{r}
#Testing

#Reduction in underconfidence mistakes
reg_underconf <- glm(not_applied_to_top_true_fin_in_top_pref ~ factor(treatment),
                       family="binomial",
                       data= dof %>% subset(open==1) %>% subset(prob_ratex_top_true > 0.0))
summary(reg_underconf)
#TODO:clean definition of top-true

#Reduction in overconfidence mistakes (reduction in risk)
reg_overconf <- glm(risk_ratex_dec ~ factor(treatment),
                       family="binomial",
                       data= dof %>% subset(open==1))
summary(reg_overconf)

#Testing stuff
# Checking reduction in has bottom_true with positive prob
d_bt_aux = dof %>% subset(open==1) %>% subset(prob_ratex_bottom_true > 0 & overall_prob_ratex_fin < 1)
table(d_bt_aux$applied_to_bottom_true_fin, d_bt_aux$treatment)

#Reduction in admissibility mistakes (reduction in share of applications which are invalid)
reg_adm_mistakes <- glm(increased_valid ~ factor(treatment),
                       family="binomial",
                       data= dof %>% 
                         subset(open==1) %>% 
                         filter(valid_apps_before < apps_before))
summary(reg_adm_mistakes)
#TODO: we do not find a significant effect on admisibility mistakes perse
# but we do regarding increasing valid applications






#Look into bias for risk
hist(as.numeric(dof %>% filter(overall_prob_ratex_fin < 0.01) %>% pull(prob_any_pref)))
hist(as.numeric(dof  %>% filter(overall_prob_ratex_fin < 0.99) %>% pull(prob_any_pref)))
hist(as.numeric(dof  %>% filter(overall_prob_ratex_fin < 0.99) %>% pull(overall_prob_ratex_fin)))

#Regresion on reduction of bias in risk
reg_risk_bias <- lm(abs(bias_in_belief_overall_ratex) ~ factor(treatment)  + factor(strata_region) + factor(strata_sexo) + factor(strata_score) + factor(general_message) + gets_sms,
                       #family="binomial",
                      data= dof %>% subset(open==1) %>% mutate(bias_in_belief_risk_ratex_abs_high = ifelse(abs(bias_in_belief_risk_ratex) >= 100, 1, 0)) %>%
                      subset(overall_prob_ratex_fin < 1) %>%
                      filter(misfit==1 & strata_region != 4))
summary(reg_risk_bias)


#TODO: we need to redo this analysis subsetting students who have their
# partial portfolios contained in their final ones, and redo
# the analysis on the bias at the program level (using bias in cutoffs maybe)
# and only for programs in the survey that appear in both portfolios



#Creating table for mistakes
stargazer(reg_underconf, reg_overconf, keep.stat="n",
          add.lines = list(c(2,round(exp(coef(reg_underconf))[2],3), round(exp(coef(reg_overconf))[2],3)),
                           c(3,round(exp(coef(reg_underconf))[3],3), round(exp(coef(reg_overconf))[3],3)),
                           c(4,round(exp(coef(reg_underconf))[4],3), round(exp(coef(reg_overconf))[4],3))), digits=3,
                         out = paste(path_draft_tables,"regs_odds_open_strategic_mistakes.tex", sep=""))

#TODO: this table has to be pasted by hand in the paper. It is easy though.


```

```{r}
kable(dof %>% filter(valid_apps_before < apps_before) %>% group_by(treatment, open) %>% dplyr::summarise(n=n(), ent=mean(entered)*100, lef=mean(left)*100, cs=mean(changed_status_ass)*100, cp=mean(changed_program_ass)*100), digits=3)

kable(dof %>% filter(valid_apps_before < apps_before) %>% group_by(treatment, open) %>% dplyr::summarise(n=n(), ent=sd(entered), lef=sd(left), cs=sd(changed_status_ass), cp=sd(changed_program_ass)), digits=3)


#Create Latex table by hand
table_summary_stats_by_group = dof %>% filter(valid_apps_before < apps_before) %>% group_by(treatment_label, open_label) %>%
dplyr::summarise(n   = n(),
                 c   = round(mean(changed)*100,3),
                 inc = round(mean(increased_valid)*100,3),
                 dec = round(mean(decreased_valid)*100,3),
                 ent = round(mean(entered)*100,3),
                 lef = round(mean(left)*100,3),
                 cs  = round(mean(changed_status_ass)*100,3),
                 cp  = round(mean(changed_program_ass)*100,3))
table_summary_stats_by_group

table_summary_stats_by_group_stderr = dof %>% filter(valid_apps_before < apps_before) %>% group_by(treatment_label, open_label) %>%
  dplyr::summarise(n   = n(),
                   c   = round(100*sd(changed)/sqrt(n()), 3),
                   inc = round(100*sd(increased_valid)/sqrt(n()), 3),
                   dec = round(100*sd(decreased_valid)/sqrt(n()), 3),
                   ent = round(100*sd(entered)/sqrt(n()), 3),
                   lef = round(100*sd(left)/sqrt(n()), 3),
                   cs  = round(100*sd(changed_status_ass)/sqrt(n()), 3),
                   cp  = round(100*sd(changed_program_ass)/sqrt(n()), 3))
table_summary_stats_by_group_stderr

#Write latex table by hand
table_latex_file = file(paste(path_draft_tables,"stats_by_treatment_and_open_among_mistakers.tex", sep=""))
table_header = c("\\begin{table}[H]",
                 "\\caption{Summary Statistics by Treatment and Reception among Mistakers}",
                 "\\label{tab:table_treatment_stats_by_open_among_mistakers}",
                 "\\centerline{\\scalebox{0.7}{",
                 "\\begin{tabular}{lcccccccccc}",
                 "\\toprule",
                 "  & & & \\multicolumn{3}{c}{Application} & \\multicolumn{4}{c}{Assignment} \\\\",
                 "\\cmidrule(lr){4-6}\\cmidrule(lr){7-10}")
table_columns = paste("Treatment",
                      "\\makecell*[c]{Opened}",
                      "\\(N\\)",
                      "Modified [\\%]",
                      "\\makecell*[c]{Increased [\\%]}",
                      "\\makecell*[c]{Decreased [\\%]}",
                      "Entered [\\%]",
                      "Left [\\%]",
                      "\\makecell*[c]{Changed  \\\\ status [\\%]}",
                      "\\makecell*[c]{Changed  \\\\ program [\\%]}",
                      sep = " & ")
table_body = paste(table_columns, "\\\\" ," \\midrule")

space = '\\\\[0pt]'
table_stats = table_summary_stats_by_group
table_sterr_stats = table_summary_stats_by_group_stderr
#Fill table body
for(i in 1:nrow(table_stats)){
  row = c()
  for(j in 1:ncol(table_stats)){
    row_stat = table_stats[i,j]
    if(j == 1){
      row = row_stat
    }
    else{
      row = paste(row, "&", row_stat)
    }
  }
  row = paste(row, space)
  table_body = c(table_body, row)
  # Paste row for standard errors
  row = c()
  for(j in 1:ncol(table_sterr_stats)){
    row_stat = table_sterr_stats[i,j]
    if(j != 1){
      if(j == 2 | j == 3){
        row = paste(row, "&", "")
      }else{
        row = paste(row, "&", paste("(",row_stat,")",sep=""))
      }
    }
  }
  row = paste(row, space)
  table_body = c(table_body, row)
}

table_footer = c("\\bottomrule",
                 "\\end{tabular}",
                 "}}",
                 "{\\scriptsize Note: Opened is a binary variable equal to 1 if the student opened the personalized website, 0 otherwise. Modified is a binary variable equal to 1 if the student modified its application after the personalized websites were sent, 0 otherwise. Increased (decreased) is a binary variable equal to 1 if the student increased (decreased) the number of valid applications in their list, 0 otherwise. Entered (left) is a binary variable equal to 1 if the student resulted unassigned (assigned) given their list of preferences before the intervention and (un)assigned  given their preferenes after the intervention, 0 otherwise. Changed status (program) is a binary variable equal to 1 if the student changed their status (program) of assignment considering the list of preferences submitted before and after the intervention. Standard errors reported in parenthesis.}",
                 "\\end{table}")
table_latex_code = c(table_header, table_body, table_footer)
writeLines(table_latex_code, table_latex_file)
close(table_latex_file)



```

```{r}
# Causal effects on Admissibility Mistakers
# We can add controls to get more significant estimates
#TODO:CHECK HOW THE MISFIT VARIABLE IS DEFINED

reg_changed <- glm(changed  ~ factor(treatment), family="binomial", data = dof  %>% filter(misfit==1 & strata_region != 4) %>% filter(valid_apps_before < apps_before) %>% subset(open==1))
summary(reg_changed)

reg_inc <- glm(increased_valid  ~ factor(treatment), family="binomial", data = dof  %>% filter(misfit==1 & strata_region != 4) %>% filter(valid_apps_before < apps_before) %>% subset(open==1))
summary(reg_inc)

reg_dec <- glm(decreased_valid  ~ factor(treatment), family="binomial", data = dof  %>% filter(misfit==1 & strata_region != 4) %>% filter(valid_apps_before < apps_before) %>% subset(open==1))
summary(reg_dec)

reg_pr_ass <- glm(changed_program_ass ~ factor(treatment), family="binomial", data = dof  %>% filter(misfit==1 & strata_region != 4) %>% filter(valid_apps_before < apps_before) %>% subset(open==1))
summary(reg_pr_ass)

reg_st_ass <- glm(changed_status_ass ~ factor(treatment), family="binomial", data = dof  %>% filter(misfit==1 & strata_region != 4) %>% filter(valid_apps_before < apps_before) %>% subset(open==1))
summary(reg_st_ass)

reg_ent <- glm(entered  ~ factor(treatment), family="binomial", data = dof  %>% 
                 filter(misfit==1 & strata_region != 4) %>% 
                 filter(valid_apps_before < apps_before) %>% subset(open==1))
summary(reg_ent)

reg_lft <- glm(left  ~ factor(treatment), family="binomial", data = dof  %>% filter(misfit==1 & strata_region != 4) %>% filter(valid_apps_before < apps_before) %>% subset(open==1))
summary(reg_lft)


reg_adm_mistakes <- glm(reduced_share_mistakes  ~ factor(treatment), family="binomial", 
                        data = dof  %>% 
                          filter(misfit==1 & strata_region != 4) %>% 
                          filter(valid_apps_before < apps_before) %>% 
                          subset(open==1) %>%
                          subset(changed == 1))
summary(reg_adm_mistakes)





stargazer(reg_changed, reg_inc, reg_dec, reg_ent, reg_lft,  reg_st_ass, reg_pr_ass, keep.stat="n",
          add.lines = list(c(2,round(exp(coef(reg_changed))[2],3), round(exp(coef(reg_inc))[2],3), round(exp(coef(reg_dec))[2],3), round(exp(coef(reg_ent))[2],3), round(exp(coef(reg_lft))[2],3), round(exp(coef(reg_st_ass))[2],3), round(exp(coef(reg_pr_ass))[2],3)),
                           c(3,round(exp(coef(reg_changed))[3],3), round(exp(coef(reg_inc))[3],3), round(exp(coef(reg_dec))[3],3), round(exp(coef(reg_ent))[3],3), round(exp(coef(reg_lft))[3],3), round(exp(coef(reg_st_ass))[3],3), round(exp(coef(reg_pr_ass))[3],3)),
                           c(4,round(exp(coef(reg_changed))[4],3), round(exp(coef(reg_inc))[4],3), round(exp(coef(reg_dec))[4],3), round(exp(coef(reg_ent))[4],3), round(exp(coef(reg_lft))[4],3), round(exp(coef(reg_st_ass))[2],3), round(exp(coef(reg_pr_ass))[4],3))), digits=3,
                         out = paste(path_draft_tables,"regs_odds_open_among_adm_mistakers.tex", sep=""))

#TODO: this table has to be pasted by hand in the paper. It is easy though.
```

##Test Knowledge of weights
Creation of the variables
```{r}
#Dummies for whether the programs of the survey were in the interim list

#was top reported final in the interim list?
dof %<>% mutate(toprep_in_int= ifelse(codigo_carrera_1_fin==codigo_carrera_1_int | codigo_carrera_1_fin==codigo_carrera_2_int | codigo_carrera_1_fin==codigo_carrera_3_int
 | codigo_carrera_1_fin==codigo_carrera_4_int | codigo_carrera_1_fin==codigo_carrera_5_int | codigo_carrera_1_fin==codigo_carrera_6_int | codigo_carrera_1_fin==codigo_carrera_7_int | codigo_carrera_1_fin==codigo_carrera_8_int | codigo_carrera_1_fin==codigo_carrera_9_int | codigo_carrera_1_fin==codigo_carrera_10_int, 1, 0))

#was bottomreported true final in the interim list?
#first need to create a variable with the bottom reported:
dof %<>% mutate(bottomrep_fin= ifelse(apps_after==1, codigo_carrera_1_fin,
                                      ifelse(apps_after==2, codigo_carrera_2_fin, ifelse(apps_after==3, codigo_carrera_3_fin, ifelse(apps_after==4, codigo_carrera_4_fin, ifelse(apps_after==5,codigo_carrera_5_fin, ifelse(apps_after==6, codigo_carrera_6_fin, ifelse(apps_after==7, codigo_carrera_7_fin, ifelse(apps_after==8, codigo_carrera_8_fin, ifelse(apps_after==9, codigo_carrera_9_fin, ifelse(apps_after==10, codigo_carrera_10_fin, NA)))))))))))

dof %<>% mutate(bottomrep_in_int= ifelse(bottomrep_fin==codigo_carrera_1_int | bottomrep_fin==codigo_carrera_2_int | bottomrep_fin==codigo_carrera_3_int
 | bottomrep_fin==codigo_carrera_4_int | bottomrep_fin==codigo_carrera_5_int | bottomrep_fin==codigo_carrera_6_int | bottomrep_fin==codigo_carrera_7_int | bottomrep_fin==codigo_carrera_8_int | bottomrep_fin==codigo_carrera_9_int | bottomrep_fin==codigo_carrera_10_int, 1, 0))

#was top true in the interim list?
dof %<>% mutate(toptrue_in_int= ifelse(codigo_carrera_top_true==codigo_carrera_1_int | codigo_carrera_top_true==codigo_carrera_2_int | codigo_carrera_top_true==codigo_carrera_3_int
 | codigo_carrera_top_true==codigo_carrera_4_int | codigo_carrera_top_true==codigo_carrera_5_int | codigo_carrera_top_true==codigo_carrera_6_int | codigo_carrera_top_true==codigo_carrera_7_int | codigo_carrera_top_true==codigo_carrera_8_int | codigo_carrera_top_true==codigo_carrera_9_int | codigo_carrera_top_true==codigo_carrera_10_int, 1, 0))

#was bottom true in the interim list?
dof %<>% mutate(bottomtrue_in_int= ifelse(codigo_carrera_bottom_true==codigo_carrera_1_int | codigo_carrera_bottom_true==codigo_carrera_2_int | codigo_carrera_bottom_true==codigo_carrera_3_int
 | codigo_carrera_bottom_true==codigo_carrera_4_int | codigo_carrera_bottom_true==codigo_carrera_5_int | codigo_carrera_bottom_true==codigo_carrera_6_int | codigo_carrera_bottom_true==codigo_carrera_7_int | codigo_carrera_bottom_true==codigo_carrera_8_int | codigo_carrera_bottom_true==codigo_carrera_9_int | codigo_carrera_bottom_true==codigo_carrera_10_int, 1, 0))

#New: Requisitos de admisin, selectividad de los programas o ponderaciones
dof %<>% mutate(informed1 = ifelse((QID128_1=="Completamente informada/o" | QID128_1=="Bastante informada/o") & QID128_1!="NA", 1,0))
dof %<>% mutate(fullyinformed1 = ifelse(QID128_1=="Completamente informada/o" & QID128_1!="NA",1,0))
dof %<>% mutate(noinformed1 = ifelse(QID128_1=="No creo estar informada/o" & QID128_1!="NA",1,0))
dof %<>% mutate(informed2 = ifelse((QID128_2=="Completamente informada/o" | QID128_2=="Bastante informada/o" | QID128_2=="Medianamente Informada/o" ) & QID128_2!="NA", 1,0))
dof %<>% mutate(fullyinformed2 = ifelse(QID128_2=="Completamente informada/o" & QID128_2!="NA",1,0))
dof %<>% mutate(noinformed2 = ifelse(QID128_2=="No creo estar informada/o" & QID128_2!="NA",1,0))
dof %<>% mutate(informed3 = ifelse((QID128_3=="Completamente informada/o" | QID128_3=="Bastante informada/o") & QID128_3!="NA", 1,0))
dof %<>% mutate(fullyinformed3 = ifelse(QID128_3=="Completamente informada/o" & QID128_3!="NA",1,0))
dof %<>% mutate(noinformed3 = ifelse(QID128_3=="No creo estar informada/o" & QID128_3!="NA",1,0))
dof %<>% mutate(informed4 = ifelse((QID128_4=="Completamente informada/o" | QID128_4=="Bastante informada/o") & QID128_4!="NA", 1,0))
dof %<>% mutate(fullyinformed4 = ifelse(QID128_4=="Completamente informada/o" & QID128_4!="NA",1,0))
dof %<>% mutate(noinformed4 = ifelse(QID128_4=="No creo estar informada/o" & QID128_4!="NA",1,0))
dof %<>% mutate(informed5 = ifelse((QID128_5=="Completamente informada/o" | QID128_5=="Bastante informada/o") & QID128_5!="NA", 1,0))
dof %<>% mutate(fullyinformed5 = ifelse(QID128_5=="Completamente informada/o" & QID128_5!="NA",1,0))
dof %<>% mutate(noinformed5 = ifelse(QID128_5=="No creo estar informada/o" & QID128_5!="NA",1,0))
dof %<>% mutate(nber_answerinfo =  rowSums(!is.na(cbind(QID128_1, QID128_2, QID128_3, QID128_4, QID128_5))))
dof %<>% mutate(index_info = ifelse((QID128_1!="NA" | QID128_2!="NA" | QID128_3!="NA" | QID128_4!="NA" | QID128_5!="NA"), rowSums(cbind(informed1, informed2, informed3, informed4, informed5), na.rm = TRUE)/nber_answerinfo, NA))

dof %<>% mutate(info_est1 = ifelse((QID134_1=="Completamente informada/o" | QID134_1=="Bastante informada/o") & QID134_1!="NA", 1,0))
dof %<>% mutate(fullinfo_est1 = ifelse(QID134_2=="Completamente informada/o"& QID134_2!="NA", 1,0))
dof %<>% mutate(info_est2 = ifelse((QID134_2=="Completamente informada/o" | QID134_2=="Bastante informada/o") & QID134_2!="NA", 1,0))
dof %<>% mutate(fullinfo_est2 = ifelse(QID134_2=="Completamente informada/o"& QID134_2!="NA", 1,0))
dof %<>% mutate(info_est3 = ifelse((QID134_3=="Completamente informada/o" | QID134_3=="Bastante informada/o") & QID134_3!="NA", 1,0))
dof %<>% mutate(fullinfo_est3 = ifelse(QID134_3=="Completamente informada/o"& QID134_3!="NA", 1,0))
dof %<>% mutate(info_est4 = ifelse((QID134_4=="Completamente informada/o" | QID134_4=="Bastante informada/o") & QID134_4!="NA", 1,0))
dof %<>% mutate(fullinfo_est4 = ifelse(QID134_4=="Completamente informada/o"& QID134_4!="NA", 1,0))
dof %<>% mutate(info_est5 = ifelse((QID134_5=="Completamente informada/o" | QID134_5=="Bastante informada/o") & QID134_5!="NA", 1,0))
dof %<>% mutate(fullinfo_est5 = ifelse(QID134_5=="Completamente informada/o"& QID134_5!="NA", 1,0))


dof %<>% mutate(info_ingres1 = ifelse((QID135_1=="Completamente informada/o" | QID135_1=="Bastante informada/o") & QID135_1!="NA", 1,0))
dof %<>% mutate(fullinfo_ingres1 = ifelse(QID135_1=="Completamente informada/o"& QID135_1!="NA", 1,0))
dof %<>% mutate(info_ingres2 = ifelse((QID135_2=="Completamente informada/o" | QID135_2=="Bastante informada/o") & QID135_2!="NA", 1,0))
dof %<>% mutate(fullinfo_ingres2 = ifelse(QID135_2=="Completamente informada/o"& QID135_2!="NA", 1,0))
dof %<>% mutate(info_ingres3 = ifelse((QID135_3=="Completamente informada/o" | QID135_3=="Bastante informada/o") & QID135_3!="NA", 1,0))
dof %<>% mutate(fullinfo_ingres3 = ifelse(QID135_3=="Completamente informada/o"& QID135_3!="NA", 1,0))
dof %<>% mutate(info_ingres4 = ifelse((QID135_4=="Completamente informada/o" | QID135_4=="Bastante informada/o") & QID135_4!="NA", 1,0))
dof %<>% mutate(fullinfo_ingres4 = ifelse(QID135_4=="Completamente informada/o"& QID135_4!="NA", 1,0))
dof %<>% mutate(info_ingres5 = ifelse((QID135_5=="Completamente informada/o" | QID135_5=="Bastante informada/o") & QID135_5!="NA", 1,0))
dof %<>% mutate(fullinfo_ingres5 = ifelse(QID135_5=="Completamente informada/o"& QID135_5!="NA", 1,0))


```


Regressions:
```{r}

info_select1 <- lm(informed1 ~ factor(treatment), data=dof %>% subset(open==1 & toprep_in_int==1))
summary(info_select1)
info_select2 <- lm(informed2 ~ factor(treatment), data=dof %>% subset(open==1 & bottomrep_in_int==1))
summary(info_select2)
info_select3 <- lm(informed3 ~ factor(treatment), data=dof %>% subset(open==1 & toptrue_in_int==1)) #T3 decreases by 7 points...
summary(info_select3)
info_select5 <- lm(informed5 ~ factor(treatment), data=dof %>% subset(open==1))
summary(info_select5)
info_select1 <- lm(fullyinformed1 ~ factor(treatment), data=dof %>% subset(open==1 & toprep_in_int==1))
summary(info_select1)
info_select2 <- lm(fullyinformed2 ~ factor(treatment), data=dof %>% subset(open==1 & bottomrep_in_int==1)) ##T3 increases by 2 points
summary(info_select2)
info_select2 <- lm(fullyinformed2 ~ factor(treat), data=dof %>% subset(open==1 & bottomrep_in_int==1)) ##T3 increases by 2 points
summary(info_select2)
info_select3 <- lm(fullyinformed3 ~ factor(treatment), data=dof %>% subset(open==1 & toptrue_in_int==1))
summary(info_select3)
info_select4 <- lm(fullyinformed4 ~ factor(treatment), data=dof %>% subset(open==1 & bottomtrue_in_int==1))
summary(info_select4)
info_select5 <- lm(fullyinformed5 ~ factor(treatment), data=dof %>% subset(open==1)) ##T3 increases this by 1 point
summary(info_select5)
info_select1 <- lm(noinformed1 ~ factor(treatment), data=dof %>% subset(open==1 & toprep_in_int==1))
summary(info_select1)
info_select2 <- lm(noinformed2 ~ factor(treatment), data=dof %>% subset(open==1 & bottomrep_in_int==1))
summary(info_select2)
info_select3 <- lm(noinformed3 ~ factor(treatment), data=dof %>% subset(open==1 & toptrue_in_int==1))
summary(info_select3)
info_select4 <- lm(noinformed4 ~ factor(treatment), data=dof %>% subset(open==1 & bottomtrue_in_int==1))
summary(info_select4)
info_select5 <- lm(noinformed5 ~ factor(treatment), data=dof %>% subset(open==1))
summary(info_select5)
info_select5 <- lm(index_info ~ factor(treatment), data=dof %>% subset(open==1))
summary(info_select5)




info_select1 <- lm(info_est1 ~ factor(treatment), data=dof %>% subset(open==1 & toprep_in_int==1)) #T2 decreases by 2 points
summary(info_select1)
info_select2 <- lm(info_est2 ~ factor(treatment), data=dof %>% subset(open==1 & bottomrep_in_int==1))
summary(info_select2)
info_select3 <- lm(info_est3 ~ factor(treatment), data=dof %>% subset(open==1 & toptrue_in_int==1)) ##T3 decreases by 11points...
summary(info_select3)                                                                               ##Could that students realize how 
                                                                                                    ##uninformed they are with T3?
info_select4 <- lm(info_est4 ~ factor(treatment), data=dof %>% subset(open==1 & bottomtrue_in_int==1))
summary(info_select4)
info_select5 <- lm(info_est5 ~ factor(treatment), data=dof %>% subset(open==1))
summary(info_select5)
info_select1 <- lm(fullinfo_est1 ~ factor(treatment), data=dof %>% subset(open==1 & toprep_in_int==1))
summary(info_select1)
info_select2 <- lm(fullinfo_est2 ~ factor(treatment), data=dof %>% subset(open==1 & bottomrep_in_int==1))
summary(info_select2)
info_select3 <- lm(fullinfo_est3 ~ factor(treatment), data=dof %>% subset(open==1 & toptrue_in_int==1))
summary(info_select3)
info_select4 <- lm(fullinfo_est4 ~ factor(treatment), data=dof %>% subset(open==1 & bottomtrue_in_int==1))
summary(info_select4)
info_select5 <- lm(fullinfo_est5 ~ factor(treatment), data=dof %>% subset(open==1))
summary(info_select5)


info_select1 <- lm(info_ingres1 ~ factor(treatment), data=dof %>% subset(open==1 & toprep_in_int==1)) #T2 decreases by 3 points
summary(info_select1)
info_select2 <- lm(info_ingres2 ~ factor(treatment), data=dof %>% subset(open==1 & bottomrep_in_int==1)) #T2 decreases by 3 points
summary(info_select2)
info_select3 <- lm(info_ingres3 ~ factor(treatment), data=dof %>% subset(open==1 & toptrue_in_int==1)) #T2 decreases by 9 points
summary(info_select3)
info_select4 <- lm(info_ingres4 ~ factor(treatment), data=dof %>% subset(open==1 & bottomtrue_in_int==1))
summary(info_select4)
info_select5 <- lm(info_ingres5 ~ factor(treatment), data=dof %>% subset(open==1))
summary(info_select5)
info_select1 <- lm(fullinfo_ingres1 ~ factor(treatment), data=dof %>% subset(open==1 & toprep_in_int==1))
summary(info_select1)
info_select2 <- lm(fullinfo_ingres2 ~ factor(treatment), data=dof %>% subset(open==1 & bottomrep_in_int==1))
summary(info_select2)
info_select3 <- lm(fullinfo_ingres3 ~ factor(treatment), data=dof %>% subset(open==1 & toptrue_in_int==1))
summary(info_select3)
info_select4 <- lm(fullinfo_ingres4 ~ factor(treatment), data=dof %>% subset(open==1 & bottomtrue_in_int==1))
summary(info_select4)
info_select5 <- lm(fullinfo_ingres5 ~ factor(treatment), data=dof %>% subset(open==1))
summary(info_select5)

```
Changes in beliefs over cutoffs:
```{r}
dof <- merge(dof, car %>% dplyr::select(CODIGO_DEMRE, num_admitted, min_score, VACANTES_REG) %>%
               mutate(min_score = ifelse(num_admitted < VACANTES_REG, 210.0, min_score)) %>%
               dplyr::rename(min_score_toprep = min_score), by.x="codigo_carrera_1_fin", by.y="CODIGO_DEMRE", all.x=TRUE)

dof <- merge(dof, car %>% dplyr::select(CODIGO_DEMRE, min_score) %>%
                  dplyr::rename(min_score_toprep_test = min_score), by.x="codigo_carrera_1_fin", by.y="CODIGO_DEMRE", all.x=TRUE)

dof <- merge(dof, car %>% dplyr::select(CODIGO_DEMRE, num_admitted, min_score, VACANTES_REG) %>%
               mutate(min_score = ifelse(num_admitted < VACANTES_REG, 210.0, min_score)) %>%
               dplyr::rename(min_score_bottomrep= min_score), by.x="bottomrep_fin", by.y="CODIGO_DEMRE", all.x=TRUE)

dof <- merge(dof, car %>% dplyr::select(min_score, CODIGO_DEMRE) %>%
               dplyr::rename(min_score_bottomrep_test = min_score), by.x="bottomrep_fin", by.y="CODIGO_DEMRE", all.x=TRUE)

dof <- merge(dof, car %>% dplyr::select(CODIGO_DEMRE, num_admitted, min_score, VACANTES_REG) %>%
               dplyr::rename(min_score_top_true_test = min_score), by.x="codigo_carrera_top_true", by.y="CODIGO_DEMRE", all.x=TRUE)

dof <- merge(dof, car %>% dplyr::select(CODIGO_DEMRE, min_score) %>%
               dplyr::rename(min_score_bottom_true_test = min_score), by.x="codigo_carrera_bottom_true", by.y="CODIGO_DEMRE", all.x=TRUE)

#TODO: check whether this is the right file for the 2021 cutoffs
prev_cutoff <- read.csv(paste(dropbox_dir, "/Mistakes Structural/Data/2022/outputs/first_last_full_with_bea_2020_2021.csv", sep=''), header=TRUE, sep=",")


dof %<>% mutate(cbias_toprep = min_score_toprep_test - as.double(cutoff_top_reported))
dof %<>% mutate(cbias_bottomrep = min_score_bottomrep_test -as.double(cutoff_bottom_reported))
dof %<>% mutate(cbias_toptrue = min_score_top_true_test-as.double(cutoff_top_true))
dof %<>% mutate(cbias_bottomtrue = min_score_bottom_true_test-as.double(cutoff_bottom_true))

dof %<>% mutate(overconf_toprep = ifelse(((min_score_toprep_test - as.double(cutoff_top_reported))>0), 1,0 ))
dof %<>% mutate(overconf_bottomprep = ifelse(((min_score_bottomrep_test - as.double(cutoff_bottom_reported))>0), 1,0 ))
dof %<>% mutate(overconf_toptrue = ifelse(((min_score_top_true_test - as.double(cutoff_top_true))>0), 1,0 ))
dof %<>% mutate(overconf_bottomtrue = ifelse(((min_score_bottom_true_test - as.double(cutoff_bottom_true))>0), 1,0 ))

dof %<>% mutate(underconf_toprep = ifelse(((min_score_toprep_test - as.double(cutoff_top_reported))<0) , 1,0))
dof %<>% mutate(underconf_bottomprep = ifelse(((min_score_bottomrep_test - as.double(cutoff_bottom_reported))<0), 1,0 ))
dof %<>% mutate(underconf_toptrue = ifelse(((min_score_top_true_test - as.double(cutoff_top_true))<0), 1,0 ))
dof %<>% mutate(underconf_bottomtrue = ifelse(((min_score_bottom_true_test - as.double(cutoff_bottom_true))<0), 1,0 ))

#Put them all together, average bias by student:
dof %<>% mutate(cbias_mean=(rowSums(cbind(cbias_toprep,cbias_bottomrep,cbias_toptrue,cbias_bottomtrue), na.rm=TRUE))/(rowSums(cbind(as.double(!is.na(cutoff_top_reported)), as.double(!is.na(cutoff_bottom_reported)), as.double(!is.na(cutoff_top_true)), as.double(!is.na(cutoff_bottom_true))), na.rm=TRUE)))
dof %<>% mutate(cbias_mean = ifelse((is.na(cutoff_top_reported)==TRUE & is.na(cutoff_bottom_reported)==TRUE & is.na(cutoff_top_true)==TRUE & is.na(cutoff_bottom_true)==TRUE), NA, cbias_mean))

library(matrixStats)
dof %<>% mutate(cbias_max= rowMaxs(cbind(abs(cbias_toprep),abs(cbias_bottomrep),abs(cbias_toptrue),abs(cbias_bottomtrue)), na.rm=TRUE))
dof %<>% mutate(cbias_max = ifelse((is.na(cutoff_top_reported)==TRUE & is.na(cutoff_bottom_reported)==TRUE & is.na(cutoff_top_true)==TRUE & is.na(cutoff_bottom_true)==TRUE), NA, cbias_max))

#2021 cutoffs
dof <- merge(dof, prev_cutoff %>% dplyr::select(codigo_carrera, cutoff_reg_2021) %>%
                  dplyr::rename(cutoff2021_toprep = cutoff_reg_2021), by.x="codigo_carrera_1_fin", by.y="codigo_carrera", all.x=TRUE)
dof <- merge(dof, prev_cutoff %>% dplyr::select(codigo_carrera, cutoff_reg_2021) %>%
                  dplyr::rename(cutoff2021_bottomrep = cutoff_reg_2021), by.x="bottomrep_fin", by.y="codigo_carrera", all.x=TRUE)
dof <- merge(dof, prev_cutoff %>% dplyr::select(codigo_carrera, cutoff_reg_2021) %>%
                  dplyr::rename(cutoff2021_toptrue = cutoff_reg_2021), by.x="codigo_carrera_top_true", by.y="codigo_carrera", all.x=TRUE)
dof <- merge(dof, prev_cutoff %>% dplyr::select(codigo_carrera, cutoff_reg_2021) %>%
                  dplyr::rename(cutoff2021_bottomtrue = cutoff_reg_2021), by.x="codigo_carrera_bottom_true", by.y="codigo_carrera", all.x=TRUE)


dof %<>% mutate(c2021bias_toprep = (cutoff2021_toprep/100) - as.double(cutoff_prev_top_reported))
dof %<>% mutate(c2021bias_bottomrep = (cutoff2021_bottomrep/100) -as.double(cutoff_prev_bottom_reported))
dof %<>% mutate(c2021bias_toptrue = (cutoff2021_toptrue/100)-as.double(cutoff_prev_top_true))
dof %<>% mutate(c2021bias_bottomtrue = (cutoff2021_bottomtrue/100)-as.double(cutoff_prev_bottom_true))
dof %<>% mutate(c2021bias_mean=(rowSums(cbind(c2021bias_toprep,c2021bias_bottomrep,c2021bias_toptrue,c2021bias_bottomtrue), na.rm=TRUE))/(rowSums(cbind(as.double(!is.na(cutoff_prev_top_reported)), as.double(!is.na(cutoff_prev_bottom_reported)), as.double(!is.na(cutoff_prev_top_true)), as.double(!is.na(cutoff_prev_bottom_true))), na.rm=TRUE)))
dof %<>% mutate(c2021bias_mean = ifelse((is.na(cutoff_prev_top_reported)==TRUE & is.na(cutoff_prev_bottom_reported)==TRUE & is.na(cutoff_prev_top_true)==TRUE & is.na(cutoff_prev_bottom_true)==TRUE), NA, cbias_mean))


dof %<>% mutate(overconf_c2021_toprep = ifelse((c2021bias_toprep>0), 1,0 ))
dof %<>% mutate(overconf_c2021_bottomrep = ifelse((c2021bias_bottomrep>0), 1,0 ))
dof %<>% mutate(overconf_c2021_toptrue = ifelse((c2021bias_toptrue>0), 1,0 ))
dof %<>% mutate(overconf_c2021_bottomtrue = ifelse((c2021bias_bottomtrue>0), 1,0 ))
dof %<>% mutate(underconf_c2021_toprep = ifelse((c2021bias_toprep<0), 1,0 ))
dof %<>% mutate(underconf_c2021_bottomrep = ifelse((c2021bias_bottomrep<0), 1,0 ))
dof %<>% mutate(underconf_c2021_toptrue = ifelse((c2021bias_toptrue<0), 1,0 ))
dof %<>% mutate(underconf_c2021_bottomtrue = ifelse((c2021bias_bottomtrue<0), 1,0 ))


#beliefs w.r.t adaptive proba
dof %<>% mutate(abias_toprep= as.numeric(prob_top_reported) - prob_adaptive_1_fin*100)

dof %<>% mutate(prob_adaptive_bottomrepfin= ifelse(apps_after==1, prob_adaptive_1_fin,
                                      ifelse(apps_after==2, prob_adaptive_2_fin, ifelse(apps_after==3, prob_adaptive_3_fin, ifelse(apps_after==4, prob_adaptive_4_fin, ifelse(apps_after==5,prob_adaptive_5_fin, ifelse(apps_after==6, prob_adaptive_6_fin, ifelse(apps_after==7, prob_adaptive_7_fin, ifelse(apps_after==8, prob_adaptive_8_fin, ifelse(apps_after==9, prob_adaptive_9_fin, ifelse(apps_after==10, prob_adaptive_10_fin, NA)))))))))))
dof %<>% mutate(abias_bottomrep= as.numeric(prob_bottom_reported) - prob_adaptive_bottomrepfin*100)
dof %<>% mutate(abias_toptrue = as.numeric(prob_top_true) - prob_adaptive_top_true*100)
dof %<>% mutate(abias_bottomtrue= as.numeric(prob_bottom_true) - prob_adaptive_bottom_true*100)

#beliefs w.r.t ratex proba
dof %<>% mutate(rbias_toprep= as.numeric(prob_top_reported) - prob_ratex_1_fin*100)

dof %<>% mutate(prob_ratex_bottomrepfin= ifelse(apps_after==1, prob_ratex_1_fin,
                                      ifelse(apps_after==2, prob_ratex_2_fin, ifelse(apps_after==3, prob_ratex_3_fin, ifelse(apps_after==4, prob_ratex_4_fin, ifelse(apps_after==5,prob_ratex_5_fin, ifelse(apps_after==6, prob_ratex_6_fin, ifelse(apps_after==7, prob_ratex_7_fin, ifelse(apps_after==8, prob_ratex_8_fin, ifelse(apps_after==9, prob_ratex_9_fin, ifelse(apps_after==10, prob_ratex_10_fin, NA)))))))))))
dof %<>% mutate(rbias_bottomrep= as.numeric(prob_bottom_reported) - prob_ratex_bottomrepfin*100)
dof %<>% mutate(rbias_toptrue = as.numeric(prob_top_true) - prob_ratex_top_true*100)
dof %<>% mutate(rbias_bottomtrue= as.numeric(prob_bottom_true) - prob_ratex_bottom_true*100)
dof %<>% mutate(overconf_ratex_toprep= ifelse((as.numeric(prob_top_reported) - prob_ratex_1_fin*100)>0, 1,0))
dof %<>% mutate(overconf_ratex_bottomrep= ifelse((as.numeric(prob_bottom_reported) - prob_ratex_bottomrepfin*100)>0, 1,0))
dof %<>% mutate(overconf_ratex_toptrue= ifelse((as.numeric(prob_top_true) - prob_ratex_top_true*100)>0, 1,0))
dof %<>% mutate(overconf_ratex_bottomtrue= ifelse((as.numeric(prob_bottom_true) - prob_ratex_bottom_true*100)>0, 1,0))
```

```{r}
#regressions:
 bias_cutoff_toprep <- lm(formula = overconf_toprep ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & toprep_in_int == 1))
 summary(bias_cutoff_toprep)
 bias_cutoff_toprep <- lm(formula = overconf_bottomprep ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomrep_in_int == 1))
 summary(bias_cutoff_toprep)
 bias_cutoff_toprep <- lm(formula = overconf_toptrue ~ factor(treatment), data = dof %>% #we have an increase in the share of overconfident
                      subset(open == 1 & toptrue_in_int == 1))
 summary(bias_cutoff_toprep)
 bias_cutoff_toprep <- lm(formula = overconf_bottomtrue ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomtrue_in_int == 1))
 summary(bias_cutoff_toprep)
 
 #regressions:
 bias_cutoff_toprep <- lm(formula = underconf_toprep ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & toprep_in_int == 1))
 summary(bias_cutoff_toprep)
 bias_cutoff_toprep <- lm(formula = underconf_bottomprep ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomrep_in_int == 1))
 summary(bias_cutoff_toprep)
 bias_cutoff_toprep <- lm(formula = underconf_toptrue ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & toptrue_in_int == 1))
 summary(bias_cutoff_toprep) #...and thus a miroring decrease in the share of underconfident, but not for students in general message==2
 bias_cutoff_toprep <- lm(formula = underconf_toptrue ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & toptrue_in_int == 1 & general_message==2))
 summary(bias_cutoff_toprep)
 bias_cutoff_toprep <- lm(formula = underconf_bottomtrue ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomtrue_in_int == 1))
 summary(bias_cutoff_toprep)
 
#absolute bias in cutoffs
 bias_cutoff_bottomrep <- lm(formula = abs(cbias_toprep) ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(cbias_toprep) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & toprep_in_int==1))
 summary(bias_cutoff_bottomrep)
   dof %<>% mutate(dist_cutofftoprep = puntpond_1_fin/100 - min_score_toprep_test)
  bias_cutoff_bottomrep <- lm(formula = abs(cbias_toprep) ~ factor(treatment) + abs(dist_cutofftoprep) +factor(treatment) *abs(dist_cutofftoprep), data = dof %>% 
                      subset(open == 1 & toprep_in_int==1))
 summary(bias_cutoff_bottomrep)
bias_cutoff_bottomrep <- lm(formula = abs(cbias_toprep) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & toprep_in_int==1 & overconf_toprep==1))
 summary(bias_cutoff_bottomrep)
   bias_cutoff_bottomrep <- lm(formula = abs(cbias_toprep) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & toprep_in_int==1 & underconf_toprep==1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(cbias_bottomrep) ~ factor(treatment), data = dof %>%  #T2 and T3 brings a decrease in bias in
                                                                                                 #absolute value 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep) 
 bias_cutoff_bottomrep <- lm(formula = abs(cbias_bottomrep) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomrep_in_int == 1))
 summary(bias_cutoff_bottomrep) #T2 and T3 brings a decrease in bias in absolute value 
ggplot(data=dof %>% subset((treatment==1 | treatment==2) & bottomrep_in_int==1) , aes(x=cbias_bottomrep, group=factor(treatment), fill=factor(treatment))) +
geom_density(adjust=1.5, alpha=.4)
ggplot(data=dof %>% subset((treatment==1 | treatment==2) & bottomrep_in_int==1) , aes(x=abs(cbias_bottomrep), group=factor(treatment), fill=factor(treatment))) +
geom_density(adjust=1.5, alpha=.4)
ggplot(data=dof %>% subset((treatment==1 | treatment==3) & bottomrep_in_int==1) , aes(x=cbias_bottomrep, group=factor(treatment), fill=factor(treatment))) +
geom_density(adjust=1.5, alpha=.4)
mean(dof[dof$treatment==1 & dof$bottomrep_in_int==1,]$cbias_bottomrep, na.rm = TRUE)
mean(dof[dof$treatment==3 & dof$bottomrep_in_int==1,]$cbias_bottomrep, na.rm = TRUE)

bias_cutoff_bottomrep <- lm(formula = abs(cbias_bottomrep) ~ factor(treatment), data = dof %>%  #T2 decreases bias for overconf students
                      subset(open == 1 & bottomrep_in_int == 1 & overconf_bottomprep==1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(cbias_bottomrep) ~ factor(treatment), data = dof %>%  #T2 and T3 decreases bias for underconf
                                                                                                 #students
                      subset(open == 1 & bottomrep_in_int == 1 & underconf_bottomprep==1))
 summary(bias_cutoff_bottomrep) 
 bias_cutoff_bottomrep <- lm(formula = abs(cbias_toptrue) ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)                                                                   #T4 increases bias
 bias_cutoff_bottomrep <- lm(formula = abs(cbias_toptrue) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & toptrue_in_int == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(cbias_bottomtrue) ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(cbias_bottomtrue) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomtrue_in_int == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(cbias_mean) ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(cbias_max) ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 
 
#absolute bias in 2021 cutoffs
 bias_cutoff_bottomrep <- lm(formula = abs(c2021bias_toprep) ~ factor(treatment), data = dof %>%   #T4 increases bias
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(c2021bias_toprep) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & toprep_in_int==1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(c2021bias_bottomrep) ~ factor(treatment), data = dof %>% #T3 decreases bias, p=0.08  
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)  #T3 brings a decrease in bias in absolute value 
 bias_cutoff_bottomrep <- lm(formula = abs(c2021bias_bottomrep) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomrep_in_int == 1))
 summary(bias_cutoff_bottomrep) #T2 and T3 brings a decrease in bias in absolute value 
  bias_cutoff_bottomrep <- lm(formula = abs(c2021bias_bottomrep) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomrep_in_int == 1 & overconf_c2021_bottomrep==1))
 summary(bias_cutoff_bottomrep) 
  bias_cutoff_bottomrep <- lm(formula = abs(c2021bias_bottomrep) ~ factor(treatment), data = dof %>% #effect from uncerconf.
                      subset(open == 1 & bottomrep_in_int == 1 & underconf_c2021_bottomrep==1))
 summary(bias_cutoff_bottomrep) 
 bias_cutoff_bottomrep <- lm(formula = abs(c2021bias_toptrue) ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep) 
 bias_cutoff_bottomrep <- lm(formula = abs(c2021bias_toptrue) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & toptrue_in_int == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(c2021bias_bottomtrue) ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(c2021bias_bottomtrue) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomtrue_in_int == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(c2021bias_mean) ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 
 
 bias_cutoff_bottomrep <- lm(formula = overconf_c2021_toprep ~ factor(treatment), data = dof %>% #T3 decreases share overconf by 5points
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = overconf_c2021_toprep ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & toprep_in_int==1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = overconf_c2021_bottomrep ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep) 
 bias_cutoff_bottomrep <- lm(formula = overconf_c2021_bottomrep ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomrep_in_int == 1))
 summary(bias_cutoff_bottomrep) 
 bias_cutoff_bottomrep <- lm(formula = overconf_c2021_toptrue ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = overconf_c2021_toptrue ~ factor(treatment), data = dof %>%  #T3 increases share overconf by 9points
                      subset(open == 1 & toptrue_in_int == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = overconf_c2021_bottomtrue ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = overconf_c2021_bottomtrue ~ factor(treatment), data = dof %>% #only 28 students
                      subset(open == 1 & bottomtrue_in_int == 1))
 summary(bias_cutoff_bottomrep)
 
 bias_cutoff_bottomrep <- lm(formula = underconf_c2021_toprep ~ factor(treatment), data = dof %>%  #and thus T3 increases share underconf
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = underconf_c2021_toprep ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & toprep_in_int==1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = underconf_c2021_bottomrep ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)  #T3 brings a decrease in bias in absolute value 
 bias_cutoff_bottomrep <- lm(formula = underconf_c2021_bottomrep ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomrep_in_int == 1))
 summary(bias_cutoff_bottomrep) #T2 and T3 brings a decrease in bias in absolute value 
 bias_cutoff_bottomrep <- lm(formula = underconf_c2021_toptrue ~ factor(treatment), data = dof %>%  #T2 and T3 decrease share underconf
                      subset(open == 1))
 summary(bias_cutoff_bottomrep) #T4 increases bias
 bias_cutoff_bottomrep <- lm(formula = underconf_c2021_toptrue ~ factor(treatment), data = dof %>% #T2 decreases share underconf
                      subset(open == 1 & toptrue_in_int == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = underconf_c2021_bottomtrue ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = underconf_c2021_bottomtrue ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomtrue_in_int == 1))
 summary(bias_cutoff_bottomrep)
 
 #Adaptive bias
 bias_cutoff_bottomrep <- lm(formula = abs(abias_toprep) ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(abias_toprep) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & toprep_in_int==1))
 summary(bias_cutoff_bottomrep)
bias_cutoff_bottomrep <- lm(formula = abs(abias_bottomrep) ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(abias_bottomrep) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomrep_in_int==1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(abias_toptrue) ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(abias_toptrue) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & toptrue_in_int==1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(abias_bottomtrue) ~ factor(treatment), data = dof %>%  #decrease in the bias of bottom true from T3
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(abias_bottomtrue) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomtrue_in_int==1))
 summary(bias_cutoff_bottomrep)
 
 
 #Bias w.r.t ratex beliefs
 bias_cutoff_bottomrep <- lm(formula = abs(rbias_toprep) ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(rbias_toprep) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & toprep_in_int==1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(rbias_bottomrep) ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(rbias_bottomrep) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomrep_in_int==1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(rbias_bottomrep) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomrep_in_int==1 & overconf_ratex_bottomrep==1))
 summary(bias_cutoff_bottomrep)
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(rbias_bottomrep) ~ factor(treatment), data = dof %>% #decreases in bias
                      subset(open == 1 & bottomrep_in_int==1 & overconf_ratex_bottomrep==0))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(rbias_toptrue) ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(rbias_toptrue) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & toptrue_in_int==1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(rbias_bottomtrue) ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = abs(rbias_bottomtrue) ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomtrue_in_int==1))
 summary(bias_cutoff_bottomrep)
 
 
 
 #Overconf w.r.t ratex beliefs
 bias_cutoff_bottomrep <- lm(formula = overconf_ratex_toprep ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = overconf_ratex_toprep ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & toprep_in_int==1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = overconf_ratex_bottomrep ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = overconf_ratex_bottomrep ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomrep_in_int==1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = overconf_ratex_toptrue ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = overconf_ratex_toptrue ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & toptrue_in_int==1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = overconf_ratex_bottomtrue ~ factor(treatment), data = dof %>% 
                      subset(open == 1))
 summary(bias_cutoff_bottomrep)
 bias_cutoff_bottomrep <- lm(formula = overconf_ratex_toptrue ~ factor(treatment), data = dof %>% 
                      subset(open == 1 & bottomtrue_in_int==1))
 summary(bias_cutoff_bottomrep)
 

#beliefs proba 
bias_belief <- lm(abs(bias_in_belief_ratex_top_true) ~ factor(treatment), data=dof %>% subset(open==1 & toptrue_in_int==1) )
summary(bias_belief)
bias_belief <- lm(abs(bias_in_belief_ratex_top_true) ~ factor(treatment), data=dof %>% subset(open==1 & general_message == 2 & toptrue_in_int==1))
summary(bias_belief)
bias_belief <- lm(abs(bias_in_belief_ratex_top_true) ~ factor(treatment), data=dof %>% subset(open==1 & overall_prob_ratex_int==0.00 & toptrue_in_int==1))
summary(bias_belief)
bias_belief <- lm(abs(bias_in_belief_ratex_top_true) ~ factor(treatment), data=dof %>% subset(open==1 & prob_ratex_top_true==0.00))
summary(bias_belief)
bias_belief <- lm(abs(bias_in) ~ factor(treatment), data=dof %>% subset(open==1 & toptrue_in_int==1) )
summary(bias_belief)
bias_belief <- lm(abs(bias_in_belief_ratex_top_true) ~ factor(treatment), data=dof %>% subset(open==1 & general_message == 2 & toptrue_in_int==1))
summary(bias_belief)
bias_belief <- lm(abs(bias_in_belief_ratex_top_true) ~ factor(treatment), data=dof %>% subset(open==1 & overall_prob_ratex_int==0.00 & toptrue_in_int==1))
summary(bias_belief)
bias_belief <- lm(abs(bias_in_belief_ratex_top_true) ~ factor(treatment), data=dof %>% subset(open==1 & prob_ratex_top_true==0.00))
summary(bias_belief)
```

## IV analysis for the effect of opening the email
```{r}
library(ivpack)
```


```{r}
fs <- lm(open ~ gets_sms, data=df)
summary(fs)
stargazer(fs, out = paste(path_draft_tables,"fs.tex", sep=""))

iv_changed <- ivreg(changed ~ open | gets_sms, data=dof)
iv_inc <- ivreg(increased_valid ~ open | gets_sms, data=dof)
iv_dec <- ivreg(decreased_valid ~ open | gets_sms, data=dof)

iv_pr_ass <- ivreg(changed_program_ass ~ open | gets_sms, data=dof)
iv_st_ass <- ivreg(changed_status_ass  ~ open | gets_sms, data=dof)
iv_ent <- ivreg(entered ~ open | gets_sms, data=dof)
iv_lft <- ivreg(left ~ open | gets_sms, data=dof)

stargazer(iv_changed, iv_inc, iv_dec, iv_ent, iv_lft, iv_pr_ass, iv_st_ass, keep.stat="n", out = paste(path_draft_tables,"iv_regs.tex", sep=""))
```

```{r}
iv_changed <- ivreg(changed ~ open | gets_sms, data=dof %>% subset(treatment==3))
iv_inc <- ivreg(increased ~ open | gets_sms, data=dof %>% subset(treatment==3))
iv_dec <- ivreg(decreased ~ open | gets_sms, data=dof %>% subset(treatment==3))

iv_pr_ass <- ivreg(changed_program_ass ~ open | gets_sms, data=dof %>% subset(treatment==3))
iv_st_ass <- ivreg(changed_status_ass  ~ open | gets_sms, data=dof %>% subset(treatment==3))
iv_ent <- ivreg(entered ~ open | gets_sms, data=dof %>% subset(treatment==3))
iv_lft <- ivreg(left ~ open | gets_sms, data=dof %>% subset(treatment==3))

stargazer(iv_changed, iv_inc, iv_dec, iv_ent, iv_lft, iv_pr_ass, iv_st_ass, keep.stat="n", out = paste(path_draft_tables,"iv_regs_subset.tex", sep=""))
```



## Robustness checks
## Balance in assignment to treatments

```{r}
#TODO: Check if this is updated in the text
library(nnet)
m <- multinom(factor(treatment) ~ factor(strata_region) + factor(strata_sexo) + factor(strata_score) + factor(general_message) + gets_sms + open_cartilla, data = ms %>% filter(strata_region != 4))

mf <- multinom(factor(treatment) ~ factor(strata_region) + factor(strata_sexo) + factor(strata_score) + factor(general_message) + gets_sms + open_cartilla, data = ms %>% filter(misfit==1 & strata_region != 4))

summary(m)

stargazer(m, mf, out = paste(path_draft_tables,"regs_balance.tex", sep=""))
```

```{r}
#TODO:CHECK HOW THE MISFIT VARIABLE IS DEFINED
ms %>% filter(misfit == 1) %>% nrow()
```


Excluding misfits
```{r}
#TODO:CHECK HOW THE MISFIT VARIABLE IS DEFINED
m <- polr(factor(treatment) ~ factor(strata_region) + factor(strata_sexo) + factor(strata_score) + factor(general_message) + gets_sms + open_cartilla, data = ms %>% filter(misfit == 0), Hess=TRUE)
## store table
(ctable <- coef(summary(m)))

p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

## combined table
(ctable <- cbind(ctable, "p value" = p))
```

 