---
title: "anais issue"
output: html_document
---
```{r echo=FALSE, message=FALSE, results='hide'}
rm(list=ls())
gc()
```

```{r echo=FALSE, message=FALSE, results='hide'}
library(plyr)
library(dplyr)
library(tidyr)
library(fastDummies)
library(reshape2)
library(corrplot)
library(stargazer)
library(stringr)
library(ggplot2)
#library(rddtools)
library(parallel)
library(evd)  # \342\200\230~/R/x86_64-redhat-linux-gnu-library/3.5\342\200\231 (personal library in Hawk)
library(magic)
library(mvtnorm)
library(LaplacesDemon)
library(truncnorm)
library(compiler)
library(feather)
library(magrittr)
library(geosphere)
library(Hmisc)
library(plyr)
library(dplyr)
library(tidyr)
library(fastDummies)
library(reshape2)
library(corrplot)
library(stargazer)
library(stringr)
library(ggplot2)
```

# Load files
```{r}
df <- read.csv(file = "~/Dropbox/Mistakes/Code/R/recommendation/outputs/df_merge_recommendations.csv")
```

```{r}
load("/Users/iriosu/Dropbox/Mistakes Structural/Data/intermediate_data/appFinal_before_after.rds")
```

# First, check consistrency between file of recommendations, general messages and Strata_2
```{r}
aba <- merge(df, appFinal_before_after, by.x="mrun", by.y="MRUN")
```

```{r}
aba %>% filter(general_message == Strata_2) %>% group_by(general_message, Strata_2) %>% tally()
```

```{r}
# general message 1
aba %>% filter(prob_1 == 1) %>% group_by(Strata_2) %>% tally()
# general message 2
aba %>% filter(prob_1 < 1 & overall_prob >= 0.7 & overall_prob < 1 & pace == 0) %>% group_by(Strata_2) %>% tally()
# general message 3
aba %>% filter(prob_1 < 1 & overall_prob < 0.7 & pace == 0) %>% group_by(Strata_2) %>% tally()
```

# Check consistency of files used in Anais code (this is copy paste from analysis_warnings.R, line 1892)
```{r}
risk_initial <- read.csv('~/Dropbox/Mistakes Structural/Data/2021/applications_and_probs_for_stratas.csv', sep=';', header=TRUE)
risk_initial %<>% select(MRUN, overall_prob)
risk_initial %<>% dplyr::rename(overall_prob_initial=overall_prob)

    #Load Final Risk Database
risk_final <- read.csv('~/Dropbox/Mistakes Structural/Data/2021/bootstrap_final_admission_probabilities/applications_and_probs_last.csv', sep=';', header=TRUE)
risk_final %<>% select(MRUN, overall_prob)
risk_final %<>% dplyr::rename(overall_prob_final=overall_prob)

    #Merge both datasets
risk = merge(risk_final, risk_initial, by="MRUN", all.x = TRUE)
remove(risk_initial, risk_final)
```

```{r}
abar <- merge(appFinal_before_after, risk, by="MRUN", all.x=TRUE)
```

Add columns general_message, pace and prob_1 (admission prob in top preference initial)
```{r}
abar <- merge(abar, aba %>% dplyr::select(mrun, general_message, pace, prob_1), by.x = "MRUN", by.y="mrun")
```


Check conditions for messages
```{r}
# general message 1
abar %>% filter(prob_1 == 1) %>% group_by(Strata_2) %>% tally()
# general message 2
abar %>% filter(prob_1 < 1 & overall_prob_initial >= 0.7 & overall_prob_initial < 1 & pace == 0) %>% group_by(Strata_2) %>% tally()
# general message 3
abar %>% filter(prob_1 < 1 & overall_prob_initial < 0.7 & pace == 0) %>% group_by(Strata_2) %>% tally()
```
As you can see from here, Strata_2 is correct. The NAs are due to Cris removing them.

```{r}
#Compute the risk and the change in risk
abar %<>% mutate(risk_initial = 1-overall_prob_initial)
abar %<>% mutate(risk_final = 1-overall_prob_final)
abar %<>% mutate(change_risk = risk_final-risk_initial)
abar %<>% mutate(reduced_risk = ifelse(change_risk<0, 1, 0))
abar %<>% mutate(increased_risk = ifelse(change_risk>0, 1, 0))
```


These are the tables Anais was generating.
```{r}
table(abar %>% subset(risk_initial>=0.70) %>% select(Strata_2_label), useNA="always")                      #We have 9476 students in the Safety strata, 29 in Explore
table(abar %>% subset(risk_initial>=0.30 & risk_initial<0.70) %>% select(Strata_2_label), useNA="always")  #Pb: 563 students in the safety strata
table(abar %>% subset(risk_initial<0.01) %>% select(Strata_2_label), useNA="always")                       #Pb: 34,661 students in explore, 668 "safety and reach" and 11,398 NA
```
If you want to correctly write the conditions in terms of risk, these should be:
- General message 1: risk_initial == 0 and prob_1 == 1
- General message 2: prob_1 < 1 and risk_initial < 0.3 and risk_initial > 0 and pace == 0
- General message 3: prob_1 < 1 and risk_initial >= 0.3 and pace == 0

```{r}
table(abar %>% filter(prob_1 == 1) %>% select(Strata_2), useNA="always")                      #We have 9476 students in the Safety strata, 29 in Explore
table(abar %>% filter(risk_initial <= 0.3 & risk_initial > 0 & prob_1 < 1 & pace == 0) %>% select(Strata_2), useNA="always")  #Pb: 563 students in the safety strata
table(abar %>% filter(risk_initial > 0.3 & prob_1 < 1 & pace == 0) %>% select(Strata_2), useNA="always") #Pb: 34,661 students in explore, 668 "safety and reach" and 11,398 NA
```

```{r}
abar %>% filter(risk_initial > 0.3 & prob_1 < 1 & pace == 0) %>% filter(Strata_2 == 2) %>% dplyr::select(overall_prob_initial, risk_initial)
```


```{r}
# general message 1
abar %>% filter(prob_1 == 1) %>% group_by(Strata_2) %>% tally()
# general message 2
abar %>% filter(prob_1 < 1 & overall_prob_initial >= 0.7 & overall_prob_initial < 1 & pace == 0) %>% group_by(Strata_2) %>% tally()
# general message 3
abar %>% filter(prob_1 < 1 & overall_prob_initial < 0.7 & pace == 0) %>% group_by(Strata_2) %>% tally()
```



