---
title: "Analysis"
output:
  pdf_document:
    keep_tex:  true
    latex_engine: xelatex
  html_document: default
---

```{r echo=FALSE, message=FALSE, results='hide'}
library(plyr)
library(dplyr)
library(tidyr)
library(fastDummies)
library(reshape2)
library(corrplot)
library(stargazer)
library(stringr)
library(ggplot2)
library(rddtools)
library(parallel)
library(evd)  # \342\200\230~/R/x86_64-redhat-linux-gnu-library/3.5\342\200\231 (personal library in Hawk)
library(magic)
library(mvtnorm)
library(LaplacesDemon)
library(truncnorm)
library(compiler)
library(feather)
library(magrittr)
library(geosphere)
library(Hmisc)
library(plyr)
library(dplyr)
library(tidyr)
library(fastDummies)
library(reshape2)
library(corrplot)
library(stargazer)
library(stringr)
library(ggplot2)
library(knitr) 
library(kableExtra)
```

```{r}
dropbox_dir = "~/Dropbox/"

students19 <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2019/A_INSCRITOS_PUNTAJES_PSU_2019_PUB_MRUN.csv", sep=';', header=TRUE)
applications19 <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2019/C_POSTULANTES_SELECCION_PSU_2019_PUB_MRUN.csv", sep=';', header=TRUE)

students20 <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2020/A_INSCRITOS_PUNTAJES_PSU_2020_PUB_MRUN.csv", sep=';', header=TRUE)
applications20 <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2020/C_POSTULANTES_SELECCION_PSU_2020_PUB_MRUN.csv", sep=';', header=TRUE)
```


```{r}
applications19$applied = 1
applications20$applied = 1
applications19 %<>% mutate(assigned = (ESTADO_PREF_01 == 24) + (ESTADO_PREF_02 == 24) + (ESTADO_PREF_03 == 24) + (ESTADO_PREF_04 == 24) + (ESTADO_PREF_05 == 24) + 
                                      (ESTADO_PREF_06 == 24) + (ESTADO_PREF_07 == 24) + (ESTADO_PREF_08 == 24) + (ESTADO_PREF_09 == 24) + (ESTADO_PREF_10 == 24) )
applications20 %<>% mutate(assigned = (ESTADO_PREF_01 == 24) + (ESTADO_PREF_02 == 24) + (ESTADO_PREF_03 == 24) + (ESTADO_PREF_04 == 24) + (ESTADO_PREF_05 == 24) + 
                                      (ESTADO_PREF_06 == 24) + (ESTADO_PREF_07 == 24) + (ESTADO_PREF_08 == 24) + (ESTADO_PREF_09 == 24) + (ESTADO_PREF_10 == 24) )
```


```{r}
students19 <- merge(students19, applications19[,c("MRUN", "applied", "assigned")], by='MRUN', all.x=TRUE)
students19$applied[is.na(students19$applied)] <- 0
students19$assigned[is.na(students19$assigned)] <- 0
students20 <- merge(students20, applications20[,c("MRUN", "applied", "assigned")], by='MRUN', all.x=TRUE)
students20$applied[is.na(students20$applied)] <- 0
students20$assigned[is.na(students20$assigned)] <- 0
```

```{r}
students19 %>% group_by(assigned) %>% tally()
students20 %>% group_by(assigned) %>% tally()
124451/(124451+181601)
116047/(116047+192488)
```


```{r}
students19$PROMLM_ACTUAL <- as.numeric(students19$PROMLM_ACTUAL)
students19$PROMLM_ANTERIOR <- as.numeric(students19$PROMLM_ANTERIOR)
students20$PROMLM_ACTUAL <- as.numeric(students20$PROMLM_ACTUAL)
students20$PROMLM_ANTERIOR <- as.numeric(students20$PROMLM_ANTERIOR)
```

```{r}
kable(
  rbind(students19 %>% filter(  pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) < 450 ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() ),
        students19 %>% filter(  pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) >= 450 & pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) < 600 ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() ),
        students19 %>% filter(  pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) >= 600  ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() )
    ), digits=3
)

```

```{r}
kable(
  rbind(students20 %>% filter(  pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) < 450 ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() ),
        students20 %>% filter(  pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) >= 450 & pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) < 600 ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() ),
        students20 %>% filter(  pmax(PROMLM_ACTUAL, PROMLM_ANTERIOR) >= 600  ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n() )
    ), digits=3
)
```

```{r}
students21 <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/official/adm2021_archivo_C_demre_2021feb08_MRUN_Compartir.csv", sep=';', header=TRUE)
bea <- read.csv('/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/15-01-21_Preseleccionados_BEA_DEMRE_MRUN.csv', sep=';', header=TRUE)
inscritos21 <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/official/Inscritos_final_febrero_MRUN_Compartir.csv", sep=';', header=TRUE)
applications21 <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/Reporte_diario_postulaciones_final_mrun.csv", sep=',', header=TRUE)
```

```{r}
applications21$applied = 1
students21 <- merge(students21, applications21[,c("mrun", "applied")], by='mrun', all.x=TRUE)
```

```{r}
students21$applied[is.na(students21$applied)] <- 0

students21$promedio_cm_actual <- as.numeric(students21$promedio_cm_actual)
students21$promedio_lm_anterior <- as.numeric(students21$promedio_lm_anterior)
```



```{r}
kable(
  rbind(
    students21 %>% filter( pmax(promedio_cm_actual, promedio_lm_anterior) < 450 ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n()),
    students21 %>% filter( pmax(promedio_cm_actual, promedio_lm_anterior)  >= 450 & pmax(promedio_cm_actual, promedio_lm_anterior) < 600  ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n()),
    students21 %>% filter( pmax(promedio_cm_actual, promedio_lm_anterior) >= 600  ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n())   
  ), digits=3
)
```

# Targets
Among students < 450: 19.16%
Among students >= 450 and < 600: 53.65%
Among students >= 450 and < 600: 84.83%
```{r}
low  = 0.5*(0.2229+0.160355) 
mid = 0.5*(0.647234+0.4259) 
high = 0.5*(0.8788501+0.8177859) 
```

```{r}
c(low, mid, high)
```


```{r}
low21 <- students21 %>% filter( pmax(promedio_cm_actual, promedio_lm_anterior) < 450 ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n())
mid21 <- students21 %>% filter( pmax(promedio_cm_actual, promedio_lm_anterior)  >= 450 & pmax(promedio_cm_actual, promedio_lm_anterior) < 600  ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n())
high21 <- students21 %>% filter( pmax(promedio_cm_actual, promedio_lm_anterior) >= 600  ) %>% summarise(n=n(), na=sum(applied), pct=sum(applied)/n())
```

```{r}
low_to_sample = round(low21$n*low - low21$na)
mid_to_sample = round(mid21$n*mid - mid21$na)
high_to_sample = round(high21$n*high - high21$na)
```

```{r}
low_to_sample
mid_to_sample
high_to_sample
```


```{r}
c(low_to_sample, mid_to_sample, high_to_sample)
sum(c(low_to_sample, mid_to_sample, high_to_sample))
```

```{r}
nrow(applications21) + sum(c(low_to_sample, mid_to_sample, high_to_sample))
```


```{r}
students21 %<>% mutate(plm_level = ifelse(pmax(promedio_cm_actual, promedio_lm_anterior) < 450, 'low', ifelse(pmax(promedio_cm_actual, promedio_lm_anterior) < 600, 'mid', 'high')) )
```

```{r}
write.csv(students21[,c("mrun", "plm_level")], "/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/plm_level.csv",  row.names = FALSE)
```






```{r}
bies <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/ACCESO_BIES.csv", header=TRUE, sep=';')
```


```{r}
colnames(bies)
```

```{r}
bies %>% filter(grepl('MAYOR',NOMBRE_INSTITUCION))
```



```{r}
bcu <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/ACCESO_BCU-8184.ETAPA2.csv", header=TRUE, sep=';')
```

```{r}
colnames(bcu)
```

```{r}
bcu %>% filter(grepl('MAYOR', NOMBRE_INSTITUCION))
```

```{r}
mx <- merge(bcu, bies[,c('COD_IES', 'GRATUIDAD')], by="COD_IES")
```

```{r}
colnames(mx)
```

```{r}
mx %>% filter(GRATUIDAD.x != GRATUIDAD.y)
```



```{r}
# as.list(str_split(bcu$ANIOS_ACREDITACION_INS, '_'))
bcu$acreditacion <- str_split_fixed(bcu$ANIOS_ACREDITACION_INS, "_", 2)[,2]
bcu$acreditacion <- ifelse(bcu$acreditacion == "", NA, as.numeric(bcu$acreditacion))
```

```{r}
ac <- bcu %>% group_by(COD_IES) %>% summarise(ac.mx = max(acreditacion, na.rm=TRUE), ac.mn = min(acreditacion, na.rm=TRUE))
```

```{r}
ac
```

```{r}
bcu %>% filter(COD_IES == 84) %>% dplyr::select(ANIOS_ACREDITACION_INS)
```









```{r}
nrow(students19) # Inscritos: 306052 - 308535 - 268841
nrow(applications19) # Applications: 154366 - 146465 - 60k
nrow(car19) # Carreras: 1806 - 1826 - 1910
nrow(students)
nrow(applications) 
nrow(car20) 
```

# Inscritos: 306052 - 308535 - 268841
# Applications: 154366 - 146465 - 60k
# Carreras: 1806 - 1826 - 1910
# Rinde lenguaje proceso actual: 280760 - 294898 - 234007

```{r}
students19 %>% filter(!is.na(MATE_ACTUAL)) %>% nrow()
students21 %>% filter(!is.na(clec_actual)) %>% nrow()
```

```{r}
234007/294898
```

```{r}
colnames(students21)
```


```{r}
car19 <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2019/carreras.csv", sep=';', header=TRUE)
car20 <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2020/carreras.csv", sep=';', header=TRUE)
car21 <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/carreras.csv", sep=';', header=TRUE)
```


```{r}
car19 %>% filter(CODIGO == 11037)
```

```{r}
flf <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/outputs/first_last_full_2019_2020.csv", header=TRUE, sep=';')
```

```{r}
flf %>% group_by(full_2019) %>% summarise(n())
flf %>% group_by(full_2020) %>% summarise(n())
1117/(1117+944)
1166/(1166+895)
```




```{r}
df <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/official/bases2021-feb2/ACCESO_BCU-8184.ETAPA2.csv", sep=";", header=TRUE)
```

```{r}
colnames(df)
```

```{r}
cols <- c("DURACION_ESTUDIOS", "DURACION_TITULACION", "DURACION_TOTAL", "DURACION_FORMAL_PROGRAMA")
```

```{r}
df %>% filter(DURACION_FORMAL_PROGRAMA != DURACION_TOTAL) %>% dplyr::select(cols)
```


```{r}
of <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/official/bases2021-feb2/ACCESO_OFERTA_CENTRALIZADA - 8691.V3.csv", sep=';', header=TRUE)
```

```{r}
of %>% filter(CODIGO_DEMRE == 11081)
```

```{r}
of <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2020/carreras.csv", sep=';', header=TRUE)
```

```{r}
of %>% filter(CODIGO == 11081)
```

```{r}
app20 <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2020/C_POSTULANTES_SELECCION_PSU_2020_PUB_MRUN.csv", sep=';', header=TRUE)
```

```{r}
colnames(app20)
```


```{r}
app20 %>% filter(MRUN == 1238149)
```


```{r}
punt <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/official/adm2021_archivo_C_demre_2021feb08_MRUN_Compartir.csv", sep=';', header=TRUE)
```

```{r}
ins <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/Inscritos_final_febrero_MRUN.csv", sep=';', header=TRUE)
```

```{r}
colnames(ins)
```


```{r}
mr <- merge(ins, punt, by='mrun')
```



```{r}
car21 <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/carreras.csv", sep=';', header=TRUE)
```

```{r}
car21 %>% nrow()
```

```{r}
applications21
```

```{r}
applications21 %>% filter(car_codigo_1prefer == 11045) %>% summarise(n=n()/nrow(applications21))
```
```{r}
colnames(applications21)
```

```{r}
applications19$PTJE_PREF_01 <- as.numeric(gsub(',', '.', applications19$PTJE_PREF_01))
applications20$PTJE_PREF_01 <- as.numeric(gsub(',', '.', applications20$PTJE_PREF_01))
```

```{r}
applications19 %>% filter(COD_CARRERA_PREF_01 == 11045 & PTJE_PREF_01 > 0) %>% summarise(n=n()/nrow(applications19), pp=mean(PTJE_PREF_01, na.rm=TRUE))
applications20 %>% filter(COD_CARRERA_PREF_01 == 11045 & PTJE_PREF_01 > 0) %>% summarise(n=n()/nrow(applications20), pp=mean(PTJE_PREF_01, na.rm=TRUE))
applications21 %>% filter(car_codigo_1prefer == 11045 & puntaje_carr1 > 0) %>% summarise(n=n()/nrow(applications21), pp=mean(puntaje_carr1))
```


```{r}
aux <- applications21 %>% filter( substr(car_codigo_1prefer,1, 2) == '53' | 
                                    substr(car_codigo_2prefer,1, 2) == '53' |
                                    substr(car_codigo_3prefer,1, 2) == '53' |
                                    substr(car_codigo_4prefer,1, 2) == '53' |
                                    substr(car_codigo_5prefer,1, 2) == '53' |
                                    substr(car_codigo_6prefer,1, 2) == '53' |
                                    substr(car_codigo_7prefer,1, 2) == '53' |
                                    substr(car_codigo_8prefer,1, 2) == '53' |
                                    substr(car_codigo_9prefer,1, 2) == '53' |
                                    substr(car_codigo_10prefer,1, 2) == '53')
```


```{r}
write.csv(aux[,c('mrun')],"/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/postulantes_UBO.csv", row.names=FALSE)
```


```{r}
dropbox_dir = "~/Dropbox/"
```


```{r}
d_2020 <- read.csv("/Users/iriosu/Downloads/ArchivosABCDRemappedAEncuestas-2/2020/D_202011302111.csv", header=TRUE, sep=';')
c_2020 <- read.csv("/Users/iriosu/Downloads/ArchivosABCDRemappedAEncuestas-2/2020/C_202011302111.csv", header=TRUE, sep=';')
```







# --------------------------------------------
# Merging with new data from GIORGIO - 2020
# --------------------------------------------

```{r}
survey_2020 <- read.csv(paste(dropbox_dir, "Mistakes in college admissions/data/clean/survey-responses-2020.csv", sep=''), header=TRUE)
```

```{r}
survey_2020$ID <- str_replace(survey_2020$recipientemail, '@email.com', '')
survey_2020$ID <- str_replace(survey_2020$ID, '"', '')
```

```{r}
load("/Users/iriosu/Downloads/abcd-anonimizados/2020/A_202105150226.rdata")
load("/Users/iriosu/Downloads/abcd-anonimizados/2020/B_202105150226.rdata")
load("/Users/iriosu/Downloads/abcd-anonimizados/2020/C_202105150226.rdata")
load("/Users/iriosu/Downloads/abcd-anonimizados/2020/D_202105150226.rdata")
```

```{r}
bcd_2020 <- merge(b_2020, c_2020 %>% dplyr::select(-intersect(colnames(b_2020), colnames(c_2020))[2:12]) , by="ID")
```

```{r}
bcd_2020 <- merge(bcd_2020, d_2020 %>% dplyr::select(-intersect(colnames(bcd_2020), colnames(d_2020))[2:3]) , by="ID")
```

```{r}
bcd_2020 <- merge(bcd_2020, survey_2020, by="ID")
```

```{r}
saveRDS(bcd_2020, "/Users/iriosu/Dropbox/Mistakes/Data/intermediate_data/bcd_and_survey_2020_20210517.rds")
```


# --------------------------------------------
# Merging data MINEDUC - DEMRE 2021
# --------------------------------------------

```{r}
apps_survey_21 <- read.csv("/Users/iriosu/Dropbox/Mistakes in college admissions/data/raw/implementation/survey-2021/postulaciones_202102240455puntajes.csv", header=TRUE, sep=';')
apps_21 <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/210217 Reporte Postulaciones MRUN v2 CB.csv", header=TRUE, sep=',')
```

```{r}
last_app_21 <- apps_21 %>% group_by(MRUN) %>% mutate(last_folio = max(FOLIO_POSTULACION)) %>% filter(FOLIO_POSTULACION == last_folio) %>% as.data.frame()
```

```{r}
last_app_21
```

```{r}
apps_survey_21
```

```{r}
apps_survey_21$PUNTAJE_CARR1 <- round(as.numeric(as.character(apps_survey_21$PUNTAJE_CARR1)), digits=2)
apps_survey_21$PUNTAJE_CARR2 <- round(as.numeric(as.character(apps_survey_21$PUNTAJE_CARR2)), digits=2)
apps_survey_21$PUNTAJE_CARR3 <- round(as.numeric(as.character(apps_survey_21$PUNTAJE_CARR3)), digits=2)
apps_survey_21$PUNTAJE_CARR4 <- round(as.numeric(as.character(apps_survey_21$PUNTAJE_CARR4)), digits=2)
apps_survey_21$PUNTAJE_CARR5 <- round(as.numeric(as.character(apps_survey_21$PUNTAJE_CARR5)), digits=2)
apps_survey_21$PUNTAJE_CARR6 <- round(as.numeric(as.character(apps_survey_21$PUNTAJE_CARR6)), digits=2)
apps_survey_21$PUNTAJE_CARR7 <- round(as.numeric(as.character(apps_survey_21$PUNTAJE_CARR7)), digits=2)
apps_survey_21$PUNTAJE_CARR8 <- round(as.numeric(as.character(apps_survey_21$PUNTAJE_CARR8)), digits=2)
apps_survey_21$PUNTAJE_CARR9 <- round(as.numeric(as.character(apps_survey_21$PUNTAJE_CARR9)), digits=2)
apps_survey_21$PUNTAJE_CARR10 <- round(as.numeric(as.character(apps_survey_21$PUNTAJE_CARR10)), digits=2)
```

```{r}
last_app_21[is.na(last_app_21)] <- -1
apps_survey_21[is.na(apps_survey_21)] <- -1
```



```{r}
mg <- merge(last_app_21, apps_survey_21, by=c("CAR_CODIGO_1PREFER", "CAR_CODIGO_2PREFER", "CAR_CODIGO_3PREFER", "CAR_CODIGO_4PREFER", "CAR_CODIGO_5PREFER", "CAR_CODIGO_6PREFER", "CAR_CODIGO_7PREFER", "CAR_CODIGO_8PREFER", "CAR_CODIGO_9PREFER", "CAR_CODIGO_10PREFER", "PUNTAJE_CARR1", "PUNTAJE_CARR2", "PUNTAJE_CARR3", "PUNTAJE_CARR4", "PUNTAJE_CARR5", "PUNTAJE_CARR6", "PUNTAJE_CARR7", "PUNTAJE_CARR8", "PUNTAJE_CARR9", "PUNTAJE_CARR10"))
```

```{r}
mg %<>% group_by(ID) %>% mutate(nrep=n()) %>% ungroup
```

```{r}
mg %>% filter(nrep > 1) %>% summarise(max(PUNTAJE_CARR1))
```






# ----------------------------------
# Extra Analysis
# ----------------------------------

```{r}
d_2021 <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/Reporte_diario_postulaciones_final_mrun.csv", sep=",", header=TRUE)
```


```{r}
c_2021 <- read.csv("/Users/iriosu/Dropbox/Mistakes/Code/Python/Cartillas/data/2021/adm2021_archivo_C_demre_2021feb08_MRUN_Compartir.csv", sep=";", header=TRUE)
```

```{r}
id = 5157446
c_2021 %>% filter(mrun == id)
d_2021 %>% filter(mrun == id)
```

```{r}
c_2021$promedio_cm_actual <- as.numeric(as.character(c_2021$promedio_cm_actual))
c_2021$promedio_lm_anterior <- as.numeric(as.character(c_2021$promedio_lm_anterior))
```


```{r}
aux <- c_2021 %>% filter(promedio_cm_actual < 450 & promedio_lm_anterior < 450 & pace != "PACE" & promedio_cm_actual > 0 & (hcso_actual > 0 | cien_actual > 0))
```

```{r}
aux <- merge(aux, d_2021)
```

```{r}
aux
```


