---
title: "Analysis Strategic Mistakes"
output:
  pdf_document:
    keep_tex:  true
    latex_engine: xelatex
  html_document: default
---

```{r echo=FALSE, message=FALSE, results='hide'}
library(plyr)
library(dplyr)
library(tidyr)
library(fastDummies)
library(reshape2)
library(corrplot)
library(stargazer)
library(stringr)
library(ggplot2)
library(rddtools)
library(parallel)
library(evd)  # \342\200\230~/R/x86_64-redhat-linux-gnu-library/3.5\342\200\231 (personal library in Hawk)
library(magic)
library(mvtnorm)
library(LaplacesDemon)
library(truncnorm)
library(compiler)
library(feather)
library(magrittr)
library(geosphere)
library(Hmisc)
library(plyr)
library(dplyr)
library(tidyr)
library(fastDummies)
library(reshape2)
library(corrplot)
library(stargazer)
library(stringr)
library(ggplot2)
```

```{r}
dropbox_dir = "~/Dropbox/"
```


# Load data and Pre-processing
The data I'm loading here is in long format (one row per student/application), and it includes all students who applied to at least one program (even if they have only invalid applications)

```{r echo=FALSE, message=FALSE, results='hide'}
dfs_2019 <- readRDS(paste(dropbox_dir, "Mistakes/Data/intermediate_data/bcd_and_survey_2019.rds", sep=''))

car19 <- read.csv(file = paste(dropbox_dir, "/Dropout_matching/Intermediate_data/data-giorgio/oferta2019_201812021829.csv", sep = "") , header=TRUE, sep=';')

cols_w = c("ID", "LENG_ACTUAL", "LENG_ANTERIOR", "MATE_ACTUAL", "MATE_ANTERIOR", "CIEN_ACTUAL", "CIEN_ANTERIOR", "HCSO_ACTUAL","HCSO_ANTERIOR", "PTJE_RANKING", "PTJE_NEM", "assigned_2019", "PROMEDIO_LM_ACTUAL", "PROMEDIO_LM_ANTERIOR")
cols_l <- c('COD_CARRERA_PREF_01', 'ESTADO_PREF_01','PTJE_PREF_01', 'LUGAR_PREF_01', 'POND_ACAD_PREF_01',
          'COD_CARRERA_PREF_02', 'ESTADO_PREF_02','PTJE_PREF_02', 'LUGAR_PREF_02', 'POND_ACAD_PREF_02',
          'COD_CARRERA_PREF_03', 'ESTADO_PREF_03','PTJE_PREF_03', 'LUGAR_PREF_03', 'POND_ACAD_PREF_03',
          'COD_CARRERA_PREF_04', 'ESTADO_PREF_04','PTJE_PREF_04', 'LUGAR_PREF_04', 'POND_ACAD_PREF_04',
          'COD_CARRERA_PREF_05', 'ESTADO_PREF_05','PTJE_PREF_05', 'LUGAR_PREF_05', 'POND_ACAD_PREF_05',
          'COD_CARRERA_PREF_06', 'ESTADO_PREF_06','PTJE_PREF_06', 'LUGAR_PREF_06', 'POND_ACAD_PREF_06',
          'COD_CARRERA_PREF_07', 'ESTADO_PREF_07','PTJE_PREF_07', 'LUGAR_PREF_07', 'POND_ACAD_PREF_07',
          'COD_CARRERA_PREF_08', 'ESTADO_PREF_08','PTJE_PREF_08', 'LUGAR_PREF_08', 'POND_ACAD_PREF_08',
          'COD_CARRERA_PREF_09', 'ESTADO_PREF_09','PTJE_PREF_09', 'LUGAR_PREF_09', 'POND_ACAD_PREF_09',
          'COD_CARRERA_PREF_10', 'ESTADO_PREF_10','PTJE_PREF_10', 'LUGAR_PREF_10', 'POND_ACAD_PREF_10')

d_2019_l <- reshape(dfs_2019[,c(cols_w, cols_l)], direction='long', 
                    varying=colnames(dfs_2019[,cols_l]), 
                    times=c('01', '02', '03', '04', '05', '06', '07', '08', '09', '10'),
                    v.names=c('COD_CARRERA_PREF', 'ESTADO_PREF','PTJE_PREF', 'LUGAR_PREF', 'POND_ACAD_PREF'),
                    idvar='ID')
colnames(d_2019_l) <- c(cols_w, "pref", "codigo_carrera", "marca", "orden", "puntano", "puntpond") # this is just me not knowing how to use reshape

rdat <- merge(d_2019_l, car19, by.x="codigo_carrera", by.y="CODIGO")

rdat %<>% mutate(psu_actual = LENG_ACTUAL*PCT_LENG + MATE_ACTUAL*PCT_MATE + 
                                      ifelse(ifelse(!is.na(CIEN_ACTUAL) & !is.na(PCT_CIEN), CIEN_ACTUAL*PCT_CIEN, 0) > ifelse(!is.na(HCSO_ACTUAL) & !is.na(PCT_HCSO), HCSO_ACTUAL*PCT_HCSO, 0), ifelse(!is.na(CIEN_ACTUAL) & !is.na(PCT_CIEN), CIEN_ACTUAL*PCT_CIEN, 0), ifelse(!is.na(HCSO_ACTUAL) & !is.na(PCT_HCSO), HCSO_ACTUAL*PCT_HCSO, 0)), 
                psu_anterior = LENG_ANTERIOR*PCT_LENG + MATE_ANTERIOR*PCT_MATE + 
                                      ifelse(ifelse(!is.na(CIEN_ANTERIOR) & !is.na(PCT_CIEN), CIEN_ANTERIOR*PCT_CIEN, 0) > ifelse(!is.na(HCSO_ANTERIOR) & !is.na(PCT_HCSO), HCSO_ANTERIOR*PCT_HCSO, 0), ifelse(!is.na(CIEN_ANTERIOR) & !is.na(PCT_CIEN), CIEN_ANTERIOR*PCT_CIEN, 0), ifelse(!is.na(HCSO_ANTERIOR) & !is.na(PCT_HCSO), HCSO_ANTERIOR*PCT_HCSO, 0)))

rdat %<>% mutate(anterior_best = ifelse(!is.na(psu_anterior), ifelse(psu_anterior > psu_actual, 1, 0), 0))

rdat %<>%  mutate(pp = ifelse(PTJE_NEM == 0, 
                                  ifelse(anterior_best == 0, psu_actual/(100-PCT_NOTAS-PCT_RANKING),
                                         psu_anterior/(100-PCT_NOTAS-PCT_RANKING)),
                                        (PTJE_RANKING*PCT_RANKING + PTJE_NEM*PCT_NOTAS)/100 + ifelse(anterior_best == 0,
                                                                                                     psu_actual/(100),
                                                                                                     psu_anterior/(100))),
                  plm = ifelse(anterior_best == 0, 0.5*(LENG_ACTUAL + MATE_ACTUAL) , 0.5*(LENG_ANTERIOR + MATE_ANTERIOR)))

rdat %<>% group_by(ID) %>% mutate(num_apps = n(), num_apps_invalid = sum(marca < 24 | marca > 26), 
                                  is_valid = ifelse(marca >= 24 & marca <= 26, 1, 0), 
                                  num_apps_w_min_pp_geq_600 = sum(PTJE_PONDERADO_MINIMO >= 600))

rdat %<>% mutate(all_mistakes = ifelse(num_apps_invalid == num_apps, 1, 0), 
                 some_mistakes = ifelse(num_apps_invalid > 0 & num_apps_invalid < num_apps, 1, 0),
                 distance_to_min_lm = round(plm-PROM_MIN_LENG_MATE,0), 
                 distance_to_min_pond = round(pp-PTJE_PONDERADO_MINIMO,0),
                 distance_to_min_lm_1 = round((plm-PROM_MIN_LENG_MATE)/0.5)*0.5, 
                 distance_to_min_pond_1 = round((pp-PTJE_PONDERADO_MINIMO)/0.5)*0.5)

pref_assigned <- rdat %>% filter(marca == 24) %>% dplyr::select(ID, codigo_carrera, pref)

colnames(pref_assigned) <- c("ID", "carrera_assigned", "pref_assigned")
pref_assigned$pref_assigned <- as.numeric(pref_assigned$pref_assigned)

rdat <- merge(rdat, pref_assigned, by="ID", all.x=TRUE)
rdat$carrera_assigned[is.na(rdat$carrera_assigned)] <- 0
rdat$pref_assigned[is.na(rdat$pref_assigned)] <- 0

rm(pref_assigned)

rdat %<>% mutate(marca_rel = ifelse(pref_assigned < as.numeric(pref) & pref_assigned > 0, 26, marca))
cutoffs <- rdat %>% filter(marca == 24) %>% group_by(codigo_carrera) %>% summarise(cutoff = min(puntpond))
rdat <- merge(rdat, cutoffs, by="codigo_carrera", all.x=TRUE)

rdat %<>% mutate(distance_to_cutoff = round(pp-cutoff,0), 
                 distance_to_cutoff_1 = round((pp-cutoff)/0.5)*0.5)
```


# Strategic mistake 1: not applying to more desired program

```{r}
dfs_2019 %>% filter(!is.na(mp_carr)) %>% group_by(applied_to_mp, rand_money, distance_mp >= 0) %>% tally()
```

```{r}
colnames(survey_2020)
```




# Strategic mistake 2: applying to programs out of reach

```{r}
cutoffs <- readRDS(paste(dropbox_dir, "Mistakes/Data/intermediate_data/panel_cutoffs_2004_2020.rds", sep=''))
```

```{r}
colnames(cutoffs[,2:length(colnames(cutoffs))])
```


```{r}
cl <- reshape(cutoffs, direction='long', 
                    varying=colnames(cutoffs[,2:length(colnames(cutoffs))]), 
                    times=c('2004', '2005', '2006', '2007', '2008', '2009', '2010', '2011', '2012', '2013', '2014', '2015', '2016', '2017', '2018', '2019', '2020'),
                    v.names=c('cutoff'),
                    idvar='codigo_carrera')

colnames(cl) <- c("codigo_carrera", "year", "cutoff")
```

```{r}
sbp <- cl %>% filter(!is.na(cutoff)) %>% group_by(codigo_carrera) %>% summarise(n=n(), avg = mean(cutoff, na.rm=TRUE), sd = sd(cutoff))
```

```{r}
sbp %>% filter(n >= 3) %>% summarise(avg_sd = mean(sd))

ggplot(sbp %>% filter(n > 3), aes(x=sd)) + 
  geom_histogram(position = "identity", alpha=0.5) +
  scale_y_continuous(expand = c(0, 0)) + 
  labs(x = "Std. Score", y="Count") +
  # scale_fill_discrete(name = "Dose", labels = c("[0,450]", "(450,500]", "(500,550]", "(600,650]", "(650,700]", "(700,850]")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.title = element_blank())
```

```{r}
rdat %<>% group_by(ID) %>% mutate(num_strategic_mistakes = sum(distance_to_cutoff < -50 & is_valid == 1)) %>% ungroup %>% as.data.frame()
```

```{r}
rdat %>% filter(distance_to_cutoff < -50) %>% tally()
rdat %>% filter(distance_to_cutoff < -50 & is_valid == 1) %>% tally()
```

```{r}
rdat %>% filter(pref == "01") %>% summarise(sum(num_apps == num_strategic_mistakes,na.rm=TRUE))
rdat %>% filter(pref == "01") %>% summarise(sum(num_strategic_mistakes > 1 & assigned_2019 == 0,na.rm=TRUE))
```

## RDD analysis: effect of being below cutoff on overall assignment

```{r}
dfg <- rdat %>% filter(!is.na(codigo_carrera) & abs(distance_to_cutoff) <= 10) %>% group_by(distance_to_cutoff) %>% summarise(prob_assigned = mean(assigned_2019))

rde <- rdd_data(dfg$prob_assigned, dfg$distance_to_cutoff, cutpoint = 0)
rdd_assigned <- rdd_reg_lm(rdd_object = rde, slope = "same", order=2)
summary(rdd_assigned)

plot(rdd_assigned,
     cex = 0.75, 
     col = "steelblue", 
     xlab = "Distance to cutoff", 
     ylab = "Probability of Assignment")
```

Remark:in previous plot, on the right of the cutoff it is not equal to 1 because of application mistakes.

```{r}
dfg <- rdat %>% filter(!is.na(codigo_carrera) & abs(distance_to_cutoff) <= 10 & pref == "01") %>% group_by(distance_to_cutoff) %>% summarise(prob_assigned = mean(assigned_2019))

rde <- rdd_data(dfg$prob_assigned, dfg$distance_to_cutoff, cutpoint = 0)
rdd_assigned <- rdd_reg_lm(rdd_object = rde, slope = "same", order=2)
summary(rdd_assigned)

plot(rdd_assigned,
     cex = 0.75, 
     col = "steelblue", 
     xlab = "Distance to cutoff", 
     ylab = "Probability of Assignment")
```


```{r}
dfg <- rdat %>% filter(!is.na(codigo_carrera) & abs(distance_to_cutoff) <= 10 & pref == "01" & num_apps > 1 ) %>% group_by(distance_to_cutoff) %>% summarise(prob_assigned = mean(assigned_2019))

rde <- rdd_data(dfg$prob_assigned, dfg$distance_to_cutoff, cutpoint = 0)
rdd_assigned <- rdd_reg_lm(rdd_object = rde, slope = "same", order=2)
summary(rdd_assigned)

plot(rdd_assigned,
     cex = 0.75, 
     col = "steelblue", 
     xlab = "Distance to cutoff", 
     ylab = "Probability of Assignment")
```





## Analyzing beliefs

```{r}
dfs_2019 %>% filter(cutoff_mp > 0 &  mp_cutoff_belief > 0 & !is.na(mp_carr)) %>% group_by(applied_to_mp, distance_mp >= 0) %>% summarise(avg = mean(mp_cutoff_belief-cutoff_mp, na.rm=TRUE), sd = sd(mp_cutoff_belief-cutoff_mp, na.rm=TRUE)) 
```

```{r}
ggplot(dfs_2019 %>% filter(distance_mp >= 0 & applied_to_mp == 0 & cutoff_mp > 0 &  mp_cutoff_belief > 0 & !is.na(mp_carr)), aes(x=mp_cutoff_belief)) + 
  geom_histogram(position = "identity", alpha=0.5) +
  scale_y_continuous(expand = c(0, 0)) + 
  labs(x = "Belief", y="Count") +
  # scale_fill_discrete(name = "Dose", labels = c("[0,450]", "(450,500]", "(500,550]", "(600,650]", "(650,700]", "(700,850]")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.title = element_blank())

ggplot(dfs_2019 %>% filter(distance_mp >= 0 & applied_to_mp == 0 & cutoff_mp > 0 & mp_cutoff_belief > 0 & !is.na(mp_carr)), aes(x=mp_cutoff_belief-cutoff_mp)) + 
  geom_histogram(position = "identity", alpha=0.5) +
  scale_y_continuous(expand = c(0, 0)) + 
  labs(x = "Belief - Cutoff", y="Count") +
  # scale_fill_discrete(name = "Dose", labels = c("[0,450]", "(450,500]", "(500,550]", "(600,650]", "(650,700]", "(700,850]")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.title = element_blank())

ggplot(dfs_2019 %>% filter(distance_mp >= 0 & cutoff_mp > 0 & mp_cutoff_belief > 0 & !is.na(mp_carr)), aes(x=mp_cutoff_belief-cutoff_mp, fill=as.factor(applied_to_mp))) + 
  geom_histogram(position = "identity", alpha=0.5) +
  scale_y_continuous(expand = c(0, 0)) + 
  labs(x = "Std. Score", y="Count") +
  # scale_fill_discrete(name = "Dose", labels = c("[0,450]", "(450,500]", "(500,550]", "(600,650]", "(650,700]", "(700,850]")) +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(),
        legend.title = element_blank())
```

```{r}
dfs_2019 %>% filter(mp_cutoff_belief-cutoff_mp > 300) %>% dplyr::select(mp_carr, mp_cutoff_belief,cutoff_mp)
```



```{r}
colnames(dfs_2019)
```

